---
title: "Exploratory Data Analysis Report"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: readable
    toc: true
    toc_float: true
params:
  cleaning_stats_agg: NA
  cleaning_stats_subj: NA
  stim_pref_agg: NA
  stim_pref_subj: NA
  stim_pref_test: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(knitr)
library(kableExtra)
library(dplyr)
library(ggplot2)
library(scales)
library(htmltools)
library(plotly)
```

# 1. Data Cleaning Statistics

This section summarizes data quality, including missed trials and trials with unrealistically fast reaction times (e.g., < 200ms).

## 1.1 Aggregate Statistics

```{r cleaning-agg}
if (!is.null(params$cleaning_stats_agg)) {
  params$cleaning_stats_agg %>%
    kable(digits = 2, caption = "Table 1.1: Aggregate Data Cleaning Statistics") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
} else {
  print("No aggregate statistics provided.")
}
```

## 1.2 Subject-Level Statistics

```{r cleaning-subj}
if (!is.null(params$cleaning_stats_subj)) {
  params$cleaning_stats_subj %>%
    dplyr::rename(
      "Subject ID" = participant_id,
      "Total Trials" = total_main_trials,
      "Missed" = n_missed_choice,
      "Fast RT" = n_fast_rt,
      "Valid Trials" = n_valid_trials,
      "Invalid Trials" = n_invalid_trials,
      "Valid (%)" = percent_valid_trials
    ) %>%
    kable(digits = 2, caption = "Table 1.2: Subject-Level Data Cleaning Summary") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE) %>%
    scroll_box(height = "500px")
} else {
  print("No subject-level statistics provided.")
}
```

# 2. Stimulus Preference

This section summarizes whether participants preferred one stimulus (0 vs 1) overall. Missed trials are excluded.

## 2.1 Aggregate

```{r stim-pref-agg-table}
if (!is.null(params$stim_pref_agg)) {
  params$stim_pref_agg %>%
    kable(
      digits = 3,
      caption = "Table 2.1: Aggregate Stimulus Preference (Overall Choice Proportions)"
    ) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
} else {
  print("No aggregate stimulus preference provided.")
}
```

```{r stim-pref-agg-plot}
if (!is.null(params$stim_pref_agg)) {
  agg <- params$stim_pref_agg
  plot_df <- tibble::tibble(
    stimulus = c("Stimulus 0", "Stimulus 1"),
    proportion = c(agg$`Prop Choice Stimulus 0`, agg$`Prop Choice Stimulus 1`)
  )

  p <- ggplot(plot_df, aes(x = stimulus, y = proportion, fill = stimulus)) +
    geom_col(alpha = 0.85, width = 0.7) +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1), limits = c(0, 1)) +
    scale_fill_manual(values = c("Stimulus 0" = "dodgerblue", "Stimulus 1" = "firebrick")) +
    labs(
      title = "Overall Proportion of Choices",
      x = "Choice",
      y = "Proportion"
    ) +
    theme_minimal(base_size = 12) +
    theme(legend.position = "none", plot.title = element_text(face = "bold"))

  print(p)
}
```

## 2.2 Subject-Level

```{r stim-pref-subj-table}
if (!is.null(params$stim_pref_subj)) {
  params$stim_pref_subj %>%
    dplyr::rename(
      "Subject ID" = participant_id,
      "Valid Trials" = n_valid_trials,
      "N Choice 0" = n_choice_0,
      "N Choice 1" = n_choice_1,
      "Prop Choice 0" = prop_choice_0,
      "Prop Choice 1" = prop_choice_1
    ) %>%
    kable(digits = 3, caption = "Table 2.2: Subject-Level Stimulus Preference") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE) %>%
    scroll_box(height = "500px")
} else {
  print("No subject-level stimulus preference provided.")
}
```

```{r stim-pref-subj-plot, results='asis'}
if (!is.null(params$stim_pref_subj)) {
  subj <- params$stim_pref_subj

  .make_pref_plotly <- function(df, prop_col, stim_label, fill_col, choice_val) {
    #####
    # Create a subject-level preference histogram plot (counts) as Plotly widget
    #
    # Parameters
    # ----
    # df : tibble
    #     Subject-level preference data frame
    # prop_col : character
    #     Column name containing preference proportion (e.g., "prop_choice_0")
    # stim_label : character
    #     Label used in the plot title (e.g., "Stimulus 0")
    # fill_col : character
    #     Fill color used for the histogram
    # choice_val : integer
    #     Choice value used in axis label (0 or 1)
    #
    # Returns
    # ----
    # plotly htmlwidget
    #     Histogram widget with MathJax-rendered axis titles
    #####
    x <- df[[prop_col]]
    m <- mean(x, na.rm = TRUE)
    mean_txt <- paste0("Mean: ", scales::percent(m, accuracy = 0.1))

    plotly::plot_ly(
      x = x,
      type = "histogram",
      xbins = list(start = 0.25, end = 0.75, size = 0.05),
      marker = list(color = fill_col, line = list(color = "black", width = 1)),
      opacity = 0.85,
      hovertemplate = "p=%{x:.0%}<br>N=%{y}<extra></extra>"
    ) %>%
      plotly::layout(
        title = list(text = paste0("Subject-Level Preference for ", stim_label), font = list(size = 20)),
        bargap = 0.05,
        xaxis = list(
          title = paste0("$p(\\\\mathrm{choice}=", choice_val, ")$"),
          tickformat = ".0%",
          range = c(0.25, 0.75),
          tickvals = seq(0.25, 0.75, by = 0.10)
        ),
        yaxis = list(
          title = "$N$",
          rangemode = "tozero"
        ),
        font = list(size = 16),
        margin = list(l = 70, r = 20, t = 60, b = 70),
        shapes = list(
          list(
            type = "line",
            x0 = 0.5, x1 = 0.5,
            y0 = 0, y1 = 1, yref = "paper",
            line = list(color = "rgba(60,60,60,0.85)", dash = "dot", width = 2)
          ),
          list(
            type = "line",
            x0 = m, x1 = m,
            y0 = 0, y1 = 1, yref = "paper",
            line = list(color = "rgba(20,20,20,0.95)", dash = "dash", width = 2)
          )
        ),
        annotations = list(
          list(
            x = min(0.74, m + 0.01),
            y = 1,
            yref = "paper",
            xref = "x",
            text = mean_txt,
            showarrow = FALSE,
            xanchor = "left",
            yanchor = "top",
            font = list(color = "rgba(20,20,20,0.95)", size = 16)
          )
        )
      ) %>%
      plotly::config(displayModeBar = FALSE)
  }

  p0 <- .make_pref_plotly(subj, "prop_choice_0", "Stimulus 0", "dodgerblue", choice_val = 0)
  p1 <- .make_pref_plotly(subj, "prop_choice_1", "Stimulus 1", "firebrick", choice_val = 1)

  carousel_id <- paste0("stim-pref-carousel-", as.integer(stats::runif(1, 1, 1e9)))

  htmltools::browsable(
    htmltools::tagList(
      htmltools::tags$style(htmltools::HTML("
        .eda-carousel { max-width: 980px; margin: 8px 0 6px 0; }
        .eda-carousel .row { display: flex; align-items: center; gap: 14px; }
        .eda-carousel .viewport { flex: 1 1 auto; min-width: 0; }
        .eda-carousel .slide { display: none; }
        .eda-carousel .slide.active { display: block; }
        .eda-carousel .html-widget { width: 100% !important; }
        .eda-carousel button.nav {
          width: 44px; height: 44px; border-radius: 22px;
          border: 1px solid rgba(0,0,0,0.25);
          background: rgba(255,255,255,0.85);
          color: rgba(0,0,0,0.75);
          font-size: 26px; line-height: 40px;
          cursor: pointer;
          box-shadow: 0 2px 8px rgba(0,0,0,0.12);
          user-select: none;
          flex: 0 0 auto;
        }
        .eda-carousel button.nav:hover { background: rgba(255,255,255,0.95); }
        .eda-carousel .caption { text-align: center; margin-top: 8px; color: rgba(0,0,0,0.65); font-size: 14px; }
      ")),
      htmltools::tags$div(
        id = carousel_id,
        class = "eda-carousel",
        `data-idx` = "0",
        htmltools::tags$div(
          class = "row",
          htmltools::tags$button(
            class = "nav prev",
            type = "button",
            onclick = sprintf("edaCarouselStep('%s', -1)", carousel_id),
            htmltools::HTML("&#10094;")
          ),
          htmltools::tags$div(
            class = "viewport",
            htmltools::tags$div(class = "slide active", htmltools::as.tags(p0)),
            htmltools::tags$div(class = "slide", htmltools::as.tags(p1))
          ),
          htmltools::tags$button(
            class = "nav next",
            type = "button",
            onclick = sprintf("edaCarouselStep('%s', 1)", carousel_id),
            htmltools::HTML("&#10095;")
          )
        ),
        htmltools::tags$div(class = "caption", "Use arrows to switch: Stimulus 0 ↔ Stimulus 1")
      ),
      htmltools::tags$script(htmltools::HTML("
        function edaCarouselShow(id, idx) {
          const el = document.getElementById(id);
          if (!el) return;
          const slides = el.querySelectorAll('.slide');
          const n = slides.length;
          const i = ((idx % n) + n) % n;
          slides.forEach((s, k) => s.classList.toggle('active', k === i));
          el.setAttribute('data-idx', String(i));
          // If Plotly widgets are inside, trigger a resize after showing
          setTimeout(function () {
            try { window.dispatchEvent(new Event('resize')); } catch (e) {}
            try {
              if (window.Plotly) {
                const widgets = el.querySelectorAll('.slide.active .html-widget');
                widgets.forEach(function (w) {
                  try { Plotly.Plots.resize(w); } catch (e) {}
                });
              }
            } catch (e) {}
          }, 60);
        }
        function edaCarouselStep(id, delta) {
          const el = document.getElementById(id);
          if (!el) return;
          const cur = parseInt(el.getAttribute('data-idx') || '0', 10);
          edaCarouselShow(id, cur + delta);
        }
      "))
    )
  )
}
```

## 2.3 Significance Test (Difference in Proportions)

We test whether participants’ stimulus 1 choice proportion differs from chance (0.5) using a one-sample t-test on subject-level proportions.

```{r stim-pref-test}
if (!is.null(params$stim_pref_test)) {
  params$stim_pref_test %>%
    dplyr::transmute(
      `\\(\\mathbf{N}\\)` = n,
      `\\(\\mathbf{\\mu_0}\\)` = mu,
      `\\(\\mathbf{\\bar{p}}\\)` = mean_prop_choice_1,
      `\\(\\mathbf{SD}\\)` = sd_prop_choice_1,
      `\\(\\mathbf{\\Delta}\\)` = mean_diff_from_mu,
      `\\(\\mathbf{t}\\)` = t,
      `\\(\\mathbf{df}\\)` = df,
      `\\(\\mathbf{p}\\)` = p_value,
      `\\(\\mathbf{CI}_{95\\%}^{low}\\)` = conf_low,
      `\\(\\mathbf{CI}_{95\\%}^{high}\\)` = conf_high
    ) %>%
    kable(
      digits = 4,
      escape = FALSE,
      caption = "Table 2.3: One-sample t-test of Subject-Level Preference for Stimulus 1 vs Chance (0.5)"
    ) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE) %>%
    row_spec(0, bold = FALSE)
} else {
  print("No stimulus preference test results provided.")
}
```
