---
title: "Exploratory Data Analysis Report"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: readable
    toc: true
    toc_float: true
params:
  cleaning_stats_agg: NA
  cleaning_stats_subj: NA
  stim_pref_agg: NA
  stim_pref_subj: NA
  stim_pref_test: NA
  rt_summary_agg: NA
  rt_summary_subj: NA
  rt_over_bins: NA
  rt_by_condition_summary: NA
  rt_by_condition_data: NA
  accuracy_agg: NA
  accuracy_subj: NA
  accuracy_test: NA
  accuracy_over_bins: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(knitr)
library(kableExtra)
library(dplyr)
library(ggplot2)
library(scales)
library(htmltools)
```

# 1. Data Cleaning Statistics

This section summarizes data quality, including missed trials and trials with unrealistically fast reaction times (e.g., < 200ms).

## 1.1 Aggregate Statistics

```{r cleaning-agg}
if (!is.null(params$cleaning_stats_agg)) {
  params$cleaning_stats_agg %>%
    kable(digits = 2, caption = "Table 1.1: Aggregate Data Cleaning Statistics") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
} else {
  print("No aggregate statistics provided.")
}
```

## 1.2 Subject-Level Statistics

```{r cleaning-subj}
if (!is.null(params$cleaning_stats_subj)) {
  params$cleaning_stats_subj %>%
    dplyr::rename(
      "Subject ID" = participant_id,
      "Total Trials" = total_main_trials,
      "Missed" = n_missed_choice,
      "Fast RT" = n_fast_rt,
      "Valid Trials" = n_valid_trials,
      "Invalid Trials" = n_invalid_trials,
      "Valid (%)" = percent_valid_trials
    ) %>%
    kable(digits = 2, caption = "Table 1.2: Subject-Level Data Cleaning Summary") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE) %>%
    scroll_box(height = "500px")
} else {
  print("No subject-level statistics provided.")
}
```

# 2. Stimulus Preference

This section summarizes whether participants preferred one stimulus (0 vs 1) overall. Missed trials are excluded.

## 2.1 Aggregate

```{r stim-pref-agg-table}
if (!is.null(params$stim_pref_agg)) {
  params$stim_pref_agg %>%
    kable(
      digits = 3,
      caption = "Table 2.1: Aggregate Stimulus Preference (Overall Choice Proportions)"
    ) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
} else {
  print("No aggregate stimulus preference provided.")
}
```

```{r stim-pref-agg-plot}
if (!is.null(params$stim_pref_agg)) {
  agg <- params$stim_pref_agg
  plot_df <- tibble::tibble(
    stimulus = c("Stimulus 0", "Stimulus 1"),
    proportion = c(agg$`Prop Choice Stimulus 0`, agg$`Prop Choice Stimulus 1`)
  )

  p <- ggplot(plot_df, aes(x = stimulus, y = proportion, fill = stimulus)) +
    geom_col(alpha = 0.85, width = 0.7) +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1), limits = c(0, 1)) +
    scale_fill_manual(values = c("Stimulus 0" = "dodgerblue", "Stimulus 1" = "firebrick")) +
    labs(
      title = "Overall Proportion of Choices",
      x = "Choice",
      y = "Proportion"
    ) +
    theme_minimal(base_size = 12) +
    theme(legend.position = "none", plot.title = element_text(face = "bold"))

  print(p)
}
```

## 2.2 Subject-Level

```{r stim-pref-subj-table}
if (!is.null(params$stim_pref_subj)) {
  params$stim_pref_subj %>%
    dplyr::rename(
      "Subject ID" = participant_id,
      "Valid Trials" = n_valid_trials,
      "N Choice 0" = n_choice_0,
      "N Choice 1" = n_choice_1,
      "Prop Choice 0" = prop_choice_0,
      "Prop Choice 1" = prop_choice_1
    ) %>%
    kable(digits = 3, caption = "Table 2.2: Subject-Level Stimulus Preference") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE) %>%
    scroll_box(height = "500px")
} else {
  print("No subject-level stimulus preference provided.")
}
```

```{r stim-pref-subj-plot, results='asis'}
if (!is.null(params$stim_pref_subj)) {
  subj <- params$stim_pref_subj

  .make_pref_plot <- function(df, prop_col, stim_label, fill_col) {
    #####
    # Create a subject-level preference histogram plot (counts)
    #
    # Parameters
    # ----
    # df : tibble
    #     Subject-level preference data frame
    # prop_col : character
    #     Column name containing preference proportion (e.g., "prop_choice_0")
    # stim_label : character
    #     Label used in the plot title (e.g., "Stimulus 0")
    # fill_col : character
    #     Fill color used for the histogram
    #
    # Returns
    # ----
    # ggplot
    #     Histogram plot with participant counts on y-axis
    #####
    x <- df[[prop_col]]
    m <- mean(x, na.rm = TRUE)

    ggplot(df, aes(x = .data[[prop_col]])) +
      geom_histogram(
        aes(y = after_stat(count)),
        binwidth = 0.05,
        fill = fill_col,
        color = "black",
        alpha = 0.85,
        boundary = 0
      ) +
      geom_vline(xintercept = 0.5, linetype = "dotted", color = "grey30", linewidth = 0.9) +
      geom_vline(xintercept = m, color = "grey10", linetype = "dashed", linewidth = 1.1) +
      annotate(
        "text",
        x = min(0.74, m + 0.01),
        y = Inf,
        label = paste0("Mean: ", scales::percent(m, accuracy = 0.1)),
        hjust = 0,
        vjust = 1.6,
        color = "grey10",
        size = 6
      ) +
      scale_x_continuous(
        labels = scales::percent_format(accuracy = 1),
        limits = c(0.25, 0.75),
        breaks = seq(0.25, 0.75, by = 0.10)
      ) +
      labs(
        title = paste0("Subject-Level Preference for ", stim_label),
        x = if (prop_col == "prop_choice_0") expression(italic(p)(choice == 0)) else expression(italic(p)(choice == 1)),
        y = expression(italic(N))
      ) +
      theme_minimal(base_size = 18) +
      theme(
        plot.title = element_text(face = "bold", size = 20),
        axis.title.x = element_text(size = 18),
        axis.title.y = element_text(size = 18),
        axis.text.x = element_text(size = 16),
        axis.text.y = element_text(size = 16)
      )
  }

  p0 <- .make_pref_plot(subj, "prop_choice_0", "Stimulus 0", "dodgerblue")
  p1 <- .make_pref_plot(subj, "prop_choice_1", "Stimulus 1", "firebrick")

  # Render as a simple carousel (robust in HTML via embedded image URIs)
  tmp0 <- tempfile(fileext = ".png")
  tmp1 <- tempfile(fileext = ".png")
  ggsave(tmp0, plot = p0, width = 8, height = 5, dpi = 160)
  ggsave(tmp1, plot = p1, width = 8, height = 5, dpi = 160)

  img0 <- knitr::image_uri(tmp0)
  img1 <- knitr::image_uri(tmp1)

  carousel_id <- paste0("stim-pref-carousel-", as.integer(stats::runif(1, 1, 1e9)))

  htmltools::browsable(
    htmltools::tagList(
      htmltools::tags$style(htmltools::HTML("
        .eda-carousel-wrap { max-width: 920px; margin: 8px 0 18px 0; }
        .eda-carousel {
          display: flex;
          align-items: center;
          gap: 10px;
        }
        .eda-carousel .viewport { flex: 1 1 auto; }
        .eda-carousel .slide { display: none; }
        .eda-carousel .slide.active { display: block; }
        .eda-carousel img { width: 100%; height: auto; border-radius: 6px; }
        .eda-carousel button.nav {
          width: 44px; height: 44px; border-radius: 22px;
          border: 1px solid rgba(0,0,0,0.25);
          background: rgba(255,255,255,0.85);
          color: rgba(0,0,0,0.75);
          font-size: 26px; line-height: 40px;
          cursor: pointer;
          box-shadow: 0 2px 8px rgba(0,0,0,0.12);
          user-select: none;
          flex: 0 0 auto;
        }
        .eda-carousel button.nav:hover { background: rgba(255,255,255,0.95); }
        .eda-carousel .caption { text-align: center; margin-top: 6px; color: rgba(0,0,0,0.65); font-size: 14px; }
      ")),
      htmltools::tags$div(
        class = "eda-carousel-wrap",
        htmltools::tags$div(
          id = carousel_id,
          class = "eda-carousel",
          `data-idx` = "0",
          htmltools::tags$button(
            class = "nav prev",
            type = "button",
            onclick = sprintf("edaCarouselStep('%s', -1)", carousel_id),
            htmltools::HTML("&#10094;")
          ),
          htmltools::tags$div(
            class = "viewport",
            htmltools::tags$div(class = "slide active", htmltools::tags$img(src = img0, alt = "Stimulus 0 preference plot")),
            htmltools::tags$div(class = "slide", htmltools::tags$img(src = img1, alt = "Stimulus 1 preference plot"))
          ),
          htmltools::tags$button(
            class = "nav next",
            type = "button",
            onclick = sprintf("edaCarouselStep('%s', 1)", carousel_id),
            htmltools::HTML("&#10095;")
          )
        ),
        htmltools::tags$div(class = "caption", "Use arrows to switch: Stimulus 0 ↔ Stimulus 1")
      ),
      htmltools::tags$script(htmltools::HTML("
        function edaCarouselShow(id, idx) {
          const el = document.getElementById(id);
          if (!el) return;
          const slides = el.querySelectorAll('.slide');
          const n = slides.length;
          const i = ((idx % n) + n) % n;
          slides.forEach((s, k) => s.classList.toggle('active', k === i));
          el.setAttribute('data-idx', String(i));
        }
        function edaCarouselStep(id, delta) {
          const el = document.getElementById(id);
          if (!el) return;
          const cur = parseInt(el.getAttribute('data-idx') || '0', 10);
          edaCarouselShow(id, cur + delta);
        }
      "))
    )
  )
}
```

## 2.3 Significance Test (Difference in Proportions)

We test whether participants’ stimulus 1 choice proportion differs from chance (0.5) using a one-sample t-test on subject-level proportions.

```{r stim-pref-test}
if (!is.null(params$stim_pref_test)) {
  params$stim_pref_test %>%
    dplyr::transmute(
      `\\(\\mathbf{N}\\)` = n,
      `\\(\\mathbf{\\mu_0}\\)` = mu,
      `\\(\\mathbf{\\bar{p}}\\)` = mean_prop_choice_1,
      `\\(\\mathbf{SD}\\)` = sd_prop_choice_1,
      `\\(\\mathbf{\\Delta}\\)` = mean_diff_from_mu,
      `\\(\\mathbf{t}\\)` = t,
      `\\(\\mathbf{df}\\)` = df,
      `\\(\\mathbf{p}\\)` = p_value,
      `\\(\\mathbf{CI}_{95\\%}^{low}\\)` = conf_low,
      `\\(\\mathbf{CI}_{95\\%}^{high}\\)` = conf_high
    ) %>%
    kable(
      digits = 4,
      escape = FALSE,
      caption = "Table 2.3: One-sample t-test of Subject-Level Preference for Stimulus 1 vs Chance (0.5)"
    ) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE) %>%
    row_spec(0, bold = FALSE)
} else {
  print("No stimulus preference test results provided.")
}
```

# 3. Reaction Time Analysis

This section summarizes reaction times (RTs) on valid-choice trials. We visualize the overall distribution, RT changes over time, and differences by feedback condition. We also inspect subject-level RT distributions and flag participants with unusually frequent very fast responses.

## 3.1 Aggregate

```{r rt-agg-table}
if (!is.null(params$rt_summary_agg)) {
  params$rt_summary_agg %>%
    kable(digits = 3, caption = "Table 3.1: Aggregate Reaction Time Summary") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
} else {
  print("No aggregate RT summary provided.")
}
```

```{r rt-agg-plots, results='asis'}
if (!is.null(params$rt_by_condition_data) && !is.null(params$rt_over_bins)) {
  # Use the same fast-RT threshold as cleaning statistics (run_analysis.R)
  fast_rt_threshold <- 0.2

  # ---- Plot 1: Overall RT distribution ----
  p_dist <- ggplot(params$rt_by_condition_data, aes(x = reaction_time)) +
    geom_histogram(aes(y = after_stat(density)), binwidth = 0.05, fill = "cornflowerblue", color = "black", alpha = 0.7, boundary = 0) +
    geom_density(alpha = 0.2, fill = "lightblue") +
    geom_vline(xintercept = fast_rt_threshold, color = "red", linetype = "dashed", linewidth = 1) +
    annotate(
      "text",
      x = fast_rt_threshold + 0.05,
      y = Inf,
      label = paste0("Fast RT threshold (", fast_rt_threshold * 1000, "ms)"),
      hjust = 0,
      vjust = 1.5,
      color = "red",
      size = 4
    ) +
    scale_x_continuous(limits = c(0, NA), expand = expansion(mult = c(0.01, 0.05))) +
    labs(
      title = "Overall Distribution of Reaction Times (Valid Trials)",
      subtitle = paste0("N = ", nrow(params$rt_by_condition_data), " trials. Red line at ", fast_rt_threshold * 1000, "ms."),
      x = "Reaction Time (seconds)",
      y = "Density"
    ) +
    theme_minimal(base_size = 14) +
    theme(plot.title = element_text(face = "bold"), plot.subtitle = element_text(color = "grey30"))

  tmp_dist <- tempfile(fileext = ".png")
  ggsave(tmp_dist, plot = p_dist, width = 8, height = 5, dpi = 170)

  # ---- Plot 2: Median RT over trial bins ----
  bins <- params$rt_over_bins
  p_bins <- ggplot(bins, aes(x = trial_bin, y = median_rt)) +
    geom_line(color = "blue", linewidth = 1) +
    geom_point(color = "blue", size = 2) +
    geom_errorbar(aes(ymin = median_rt - sem_rt, ymax = median_rt + sem_rt), width = 0.2, color = "blue", alpha = 0.5) +
    labs(
      title = "Median Reaction Time Over Trial Bins",
      x = "Trial Bin (10 bins)",
      y = "Median Reaction Time (s) ± SEM"
    ) +
    scale_x_continuous(breaks = sort(unique(bins$trial_bin))) +
    theme_minimal(base_size = 14) +
    theme(plot.title = element_text(face = "bold"))

  tmp_bins <- tempfile(fileext = ".png")
  ggsave(tmp_bins, plot = p_bins, width = 8, height = 5, dpi = 170)

  # ---- Plot 3: RT by feedback condition ----
  cond_df <- params$rt_by_condition_data %>%
    dplyr::filter(condition_label %in% c("Salient", "Non-Salient"))

  if (nrow(cond_df) > 5) {
    y_lo <- as.numeric(stats::quantile(cond_df$reaction_time, 0.01, na.rm = TRUE))
    y_hi <- as.numeric(stats::quantile(cond_df$reaction_time, 0.99, na.rm = TRUE))
  } else {
    y_lo <- min(cond_df$reaction_time, na.rm = TRUE)
    y_hi <- max(cond_df$reaction_time, na.rm = TRUE)
  }

  p_cond <- ggplot(cond_df, aes(x = condition_label, y = reaction_time, fill = condition_label)) +
    geom_boxplot(alpha = 0.7, outlier.shape = NA) +
    geom_jitter(width = 0.1, alpha = 0.06, size = 0.6) +
    scale_y_continuous(limits = c(y_lo, y_hi)) +
    scale_fill_manual(values = c("Non-Salient" = "grey70", "Salient" = "gold")) +
    labs(
      title = "Reaction Time by Feedback Condition",
      subtitle = "Valid-choice trials only. Boxes show median & IQR; y-axis trimmed to 1st–99th percentile.",
      x = "Feedback Condition",
      y = "Reaction Time (s)"
    ) +
    theme_minimal(base_size = 14) +
    theme(legend.position = "none", plot.title = element_text(face = "bold"))

  tmp_cond <- tempfile(fileext = ".png")
  ggsave(tmp_cond, plot = p_cond, width = 7, height = 5, dpi = 170)

  # ---- Embed all 3 plots as robust HTML images ----
  img_dist <- knitr::image_uri(tmp_dist)
  img_bins <- knitr::image_uri(tmp_bins)
  img_cond <- knitr::image_uri(tmp_cond)

  htmltools::browsable(
    htmltools::tagList(
      htmltools::tags$div(
        style = "max-width: 920px; margin: 8px 0 18px 0;",
        htmltools::tags$img(src = img_dist, style = "width: 100%; height: auto; border-radius: 6px;")
      ),
      htmltools::tags$div(
        style = "max-width: 920px; margin: 8px 0 18px 0;",
        htmltools::tags$img(src = img_bins, style = "width: 100%; height: auto; border-radius: 6px;")
      ),
      htmltools::tags$div(
        style = "max-width: 820px; margin: 8px 0 18px 0;",
        htmltools::tags$img(src = img_cond, style = "width: 100%; height: auto; border-radius: 6px;")
      )
    )
  )
}
```

```{r rt-by-condition-table}
if (!is.null(params$rt_by_condition_summary)) {
  params$rt_by_condition_summary %>%
    dplyr::rename(
      "Condition" = condition_label,
      "N Trials" = n,
      "Mean RT (s)" = mean_rt,
      "Median RT (s)" = median_rt,
      "SD RT (s)" = sd_rt,
      "Min RT (s)" = min_rt,
      "Max RT (s)" = max_rt
    ) %>%
    kable(digits = 3, caption = "Table 3.2: Reaction Time Summary by Feedback Condition") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
} else {
  print("No RT-by-condition summary provided.")
}
```

## 3.2 Subject-Level

```{r rt-subj-table}
if (!is.null(params$rt_summary_subj)) {
  params$rt_summary_subj %>%
    dplyr::rename(
      "Subject ID" = participant_id,
      "N Trials (RT available)" = n_trials_rt,
      "Mean RT (s)" = mean_rt,
      "Median RT (s)" = median_rt,
      "SD RT (s)" = sd_rt,
      "Min RT (s)" = min_rt,
      "Max RT (s)" = max_rt,
      "N Fast RT" = n_fast_rt,
      "Fast RT (%)" = percent_fast_rt
    ) %>%
    kable(digits = 3, caption = "Table 3.3: Subject-Level Reaction Time Summary") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE) %>%
    scroll_box(height = "500px")
} else {
  print("No subject-level RT summary provided.")
}
```

```{r rt-subj-hist, results='asis'}
if (!is.null(params$rt_by_condition_data) && !is.null(params$rt_summary_subj)) {
  fast_rt_threshold <- 0.2

  rt_trials <- params$rt_by_condition_data %>%
    dplyr::select(participant_id, reaction_time) %>%
    dplyr::filter(!is.na(reaction_time))

  # Highlight participants with >5% very fast RTs (legacy heuristic)
  rt_annot <- params$rt_summary_subj %>%
    dplyr::mutate(
      label_text = paste0(round(percent_fast_rt, 1), "%"),
      highlight_flag = percent_fast_rt > 5
    ) %>%
    dplyr::select(participant_id, label_text, highlight_flag)

  rt_plot_df <- rt_trials %>%
    dplyr::left_join(rt_annot, by = "participant_id")

  n_subjects <- dplyr::n_distinct(rt_plot_df$participant_id)
  ncol <- 4
  nrow <- max(1, ceiling(n_subjects / ncol))
  plot_height <- max(7, 3 * nrow)

  p_subj <- ggplot(rt_plot_df, aes(x = reaction_time)) +
    geom_histogram(
      aes(y = after_stat(density), fill = highlight_flag),
      binwidth = 0.1,
      boundary = 0,
      color = "black",
      alpha = 0.7
    ) +
    scale_fill_manual(values = c("TRUE" = "firebrick", "FALSE" = "grey80"), guide = "none") +
    geom_vline(xintercept = fast_rt_threshold, linetype = "dashed", color = "darkred", linewidth = 0.6) +
    geom_text(
      data = rt_annot,
      aes(x = Inf, y = Inf, label = label_text),
      hjust = 1.1, vjust = 1.5, size = 5, alpha = 0.7, fontface = "bold", color = "black",
      inherit.aes = FALSE
    ) +
    facet_wrap(~ participant_id, scales = "free_y", ncol = ncol) +
    scale_x_continuous(
      limits = c(0, max(rt_plot_df$reaction_time, na.rm = TRUE) * 1.05),
      expand = c(0.01, 0.01)
    ) +
    scale_y_continuous(expand = expansion(mult = c(0.01, 0.15))) +
    labs(
      title = "Individual Reaction Time Distributions",
      subtitle = "Dashed line: 200ms threshold. Highlighted: >5% trials < 200ms.",
      x = "Reaction Time (s)",
      y = "Density"
    ) +
    theme_bw(base_size = 10) +
    theme(
      plot.title = element_text(face = "bold", size = rel(1.2)),
      plot.subtitle = element_text(color = "grey30"),
      strip.background = element_blank(),
      strip.text = element_text(face = "bold")
    )

  tmp_subj <- tempfile(fileext = ".png")
  ggsave(tmp_subj, plot = p_subj, width = 12, height = plot_height, units = "in", dpi = 170)
  img_subj <- knitr::image_uri(tmp_subj)

  htmltools::browsable(
    htmltools::tags$div(
      style = "max-width: 1080px; margin: 10px 0 18px 0;",
      htmltools::tags$img(src = img_subj, style = "width: 100%; height: auto; border-radius: 6px;")
    )
  )
}
```

# 4. Accuracy

Accuracy is defined as choosing the option with the higher reward probability on a given trial (ties contribute 0.5). Missed trials and trials with missing reward probabilities are excluded.

## 4.1 Aggregate

```{r accuracy-agg-table}
if (!is.null(params$accuracy_agg)) {
  params$accuracy_agg %>%
    kable(digits = 3, caption = "Table 4.1: Aggregate Accuracy Summary") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
} else {
  print("No aggregate accuracy summary provided.")
}
```

```{r accuracy-ttest}
if (!is.null(params$accuracy_test)) {
  params$accuracy_test %>%
    dplyr::transmute(
      `\\(\\mathbf{N}\\)` = n,
      `\\(\\mathbf{\\mu_0}\\)` = mu,
      `\\(\\mathbf{\\bar{a}}\\)` = mean_accuracy,
      `\\(\\mathbf{SD}\\)` = sd_accuracy,
      `\\(\\mathbf{\\Delta}\\)` = mean_diff_from_mu,
      `\\(\\mathbf{t}\\)` = t,
      `\\(\\mathbf{df}\\)` = df,
      `\\(\\mathbf{p}\\)` = p_value,
      `\\(\\mathbf{CI}_{95\\%}^{low}\\)` = conf_low,
      `\\(\\mathbf{CI}_{95\\%}^{high}\\)` = conf_high
    ) %>%
    kable(
      digits = 4,
      escape = FALSE,
      caption = "Table 4.2: One-sample t-test of Subject-Level Accuracy vs Chance (0.5)"
    ) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE) %>%
    row_spec(0, bold = FALSE)
} else {
  print("No accuracy t-test results provided.")
}
```

```{r accuracy-agg-plots, results='asis'}
if (!is.null(params$accuracy_subj) && !is.null(params$accuracy_test) && !is.null(params$accuracy_over_bins)) {
  subj <- params$accuracy_subj
  tt <- params$accuracy_test
  bins <- params$accuracy_over_bins

  p_value_formatted <- if (is.finite(tt$p_value)) {
    scales::pvalue(tt$p_value, accuracy = .001, add_p = TRUE)
  } else {
    NA_character_
  }

  t_test_caption <- if (!is.finite(tt$p_value)) {
    "Not enough data for t-test (N < 2)"
  } else {
    paste0(
      "One-sample t-test vs 0.5: t(",
      round(tt$df, 1),
      ") = ",
      round(tt$t, 2),
      ", ",
      p_value_formatted
    )
  }

  overall_mean_accuracy <- mean(subj$mean_accuracy, na.rm = TRUE)

  # Boxplot of overall accuracy with (optional) significance bracket
  significance_y_start <- 0.5
  significance_y_end <- overall_mean_accuracy
  significance_x <- 1.3
  annotation_y <- (significance_y_start + significance_y_end) / 2

  p_box <- ggplot(subj, aes(x = factor(1), y = mean_accuracy)) +
    geom_hline(yintercept = 0.5, linetype = "dashed", color = "grey50") +
    geom_jitter(width = 0.2, height = 0, size = 1.5, alpha = 0.5) +
    geom_boxplot(width = 0.35, outlier.shape = NA, fill = "grey80", alpha = 0.6) +
    stat_summary(fun = mean, geom = "point", shape = 18, size = 3, color = "firebrick") +
    {if (is.finite(tt$p_value) && tt$p_value < 0.05)
      list(
        geom_segment(aes(x = significance_x, xend = significance_x, y = significance_y_start, yend = significance_y_end),
                     color = "black", linewidth = 0.5),
        geom_segment(aes(x = significance_x - 0.02, xend = significance_x, y = significance_y_end, yend = significance_y_end),
                     color = "black", linewidth = 0.5),
        geom_segment(aes(x = significance_x - 0.02, xend = significance_x, y = significance_y_start, yend = significance_y_start),
                     color = "black", linewidth = 0.5),
        annotate("text", x = significance_x + 0.05, y = annotation_y,
                 label = p_value_formatted, hjust = 0, size = 4)
      )
    } +
    labs(
      title = "Overall Accuracy Distribution",
      y = "Accuracy",
      x = NULL,
      caption = t_test_caption
    ) +
    scale_y_continuous(
      limits = c(min(0.3, min(subj$mean_accuracy, na.rm = TRUE) * 0.9),
                 max(0.75, max(subj$mean_accuracy, na.rm = TRUE) * 1.05)),
      breaks = seq(0.3, 0.8, by = 0.1)
    ) +
    scale_x_discrete(expand = expansion(add = c(0.6, 0.6))) +
    theme_classic(base_size = 13) +
    theme(
      plot.title = element_text(face = "bold", hjust = 0.5),
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank()
    )

  tmp_box <- tempfile(fileext = ".png")
  ggsave(tmp_box, plot = p_box, width = 6, height = 5, dpi = 170)

  # Learning curve
  p_curve <- ggplot(bins, aes(x = trial_bin, y = mean_accuracy_across_subjects)) +
    geom_ribbon(
      aes(ymin = mean_accuracy_across_subjects - sem_accuracy, ymax = mean_accuracy_across_subjects + sem_accuracy),
      fill = "dodgerblue",
      alpha = 0.2
    ) +
    geom_line(color = "dodgerblue", linewidth = 1) +
    geom_point(color = "dodgerblue", size = 2.5) +
    geom_hline(yintercept = 0.5, linetype = "dashed", color = "grey30") +
    labs(
      title = "Learning Curve: Accuracy Over Trial Bins",
      x = "Trial Bin",
      y = "Mean Accuracy",
      caption = "Shaded area represents SEM."
    ) +
    scale_x_continuous(breaks = sort(unique(bins$trial_bin))) +
    theme_bw(base_size = 14) +
    theme(plot.title = element_text(face = "bold", hjust = 0.5))

  tmp_curve <- tempfile(fileext = ".png")
  ggsave(tmp_curve, plot = p_curve, width = 8, height = 5, dpi = 170)

  img_box <- knitr::image_uri(tmp_box)
  img_curve <- knitr::image_uri(tmp_curve)

  htmltools::browsable(
    htmltools::tagList(
      htmltools::tags$div(
        style = "max-width: 720px; margin: 8px 0 18px 0;",
        htmltools::tags$img(src = img_box, style = "width: 100%; height: auto; border-radius: 6px;")
      ),
      htmltools::tags$div(
        style = "max-width: 920px; margin: 8px 0 18px 0;",
        htmltools::tags$img(src = img_curve, style = "width: 100%; height: auto; border-radius: 6px;")
      )
    )
  )
}
```

## 4.2 Subject-Level

```{r accuracy-subj-table}
if (!is.null(params$accuracy_subj)) {
  params$accuracy_subj %>%
    dplyr::rename(
      "Subject ID" = participant_id,
      "Mean Accuracy" = mean_accuracy,
      "N Valid Trials" = n_valid_trials
    ) %>%
    kable(digits = 3, caption = "Table 4.3: Subject-Level Accuracy") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE) %>%
    scroll_box(height = "500px")
} else {
  print("No subject-level accuracy provided.")
}
```

```{r accuracy-subj-plots, results='asis'}
if (!is.null(params$accuracy_subj)) {
  subj <- params$accuracy_subj %>%
    dplyr::mutate(below_chance = mean_accuracy < 0.5) %>%
    dplyr::arrange(mean_accuracy)

  n_subjects_accuracy <- nrow(subj)

  p_sorted <- ggplot(
    subj,
    aes(x = mean_accuracy, y = reorder(participant_id, mean_accuracy), color = below_chance)
  ) +
    geom_point(size = 2.5, alpha = 0.85) +
    geom_vline(xintercept = 0.5, linetype = "dashed", color = "red", linewidth = 0.7) +
    geom_text(
      aes(label = sprintf("%.3f", mean_accuracy), hjust = ifelse(mean_accuracy < 0.5, 1.3, -0.3)),
      vjust = 0.5,
      size = 3,
      check_overlap = TRUE
    ) +
    scale_color_manual(values = c("TRUE" = "firebrick", "FALSE" = "black"), name = "Below Chance (0.5)") +
    labs(
      title = "Individual Participant Accuracy (Sorted by Accuracy)",
      subtitle = paste0("Each point represents a participant (N=", n_subjects_accuracy, ")."),
      x = "Mean Accuracy",
      y = "Participant ID"
    ) +
    theme_bw(base_size = 12) +
    theme(
      plot.title = element_text(face = "bold", hjust = 0.5),
      legend.position = "top",
      plot.subtitle = element_text(hjust = 0.5, color = "grey30")
    )

  p_by_id <- ggplot(
    subj,
    aes(x = mean_accuracy, y = factor(participant_id, levels = rev(sort(unique(participant_id)))), color = below_chance)
  ) +
    geom_point(size = 2.5, alpha = 0.85) +
    geom_vline(xintercept = 0.5, linetype = "dashed", color = "red", linewidth = 0.7) +
    geom_text(
      aes(label = sprintf("%.3f", mean_accuracy), hjust = ifelse(mean_accuracy < 0.5, 1.3, -0.3)),
      vjust = 0.5,
      size = 3,
      check_overlap = TRUE
    ) +
    scale_color_manual(values = c("TRUE" = "firebrick", "FALSE" = "black"), name = "Below Chance (0.5)") +
    labs(
      title = "Individual Participant Accuracy (Sorted by ID)",
      subtitle = paste0("Each point represents a participant (N=", n_subjects_accuracy, ")."),
      x = "Mean Accuracy",
      y = "Participant ID"
    ) +
    theme_bw(base_size = 12) +
    theme(
      plot.title = element_text(face = "bold", hjust = 0.5),
      legend.position = "top",
      plot.subtitle = element_text(hjust = 0.5, color = "grey30")
    )

  tmp0 <- tempfile(fileext = ".png")
  tmp1 <- tempfile(fileext = ".png")
  ggsave(tmp0, plot = p_sorted, width = 8, height = max(4, 0.25 * n_subjects_accuracy), dpi = 160, limitsize = FALSE)
  ggsave(tmp1, plot = p_by_id, width = 8, height = max(4, 0.25 * n_subjects_accuracy), dpi = 160, limitsize = FALSE)

  img0 <- knitr::image_uri(tmp0)
  img1 <- knitr::image_uri(tmp1)

  carousel_id <- paste0("accuracy-carousel-", as.integer(stats::runif(1, 1, 1e9)))

  htmltools::browsable(
    htmltools::tagList(
      htmltools::tags$style(htmltools::HTML("
        .eda-carousel-wrap { max-width: 920px; margin: 8px 0 18px 0; }
        .eda-carousel { display: flex; align-items: center; gap: 10px; }
        .eda-carousel .viewport { flex: 1 1 auto; }
        .eda-carousel .slide { display: none; }
        .eda-carousel .slide.active { display: block; }
        .eda-carousel img { width: 100%; height: auto; border-radius: 6px; }
        .eda-carousel button.nav {
          width: 44px; height: 44px; border-radius: 22px;
          border: 1px solid rgba(0,0,0,0.25);
          background: rgba(255,255,255,0.85);
          color: rgba(0,0,0,0.75);
          font-size: 26px; line-height: 40px;
          cursor: pointer;
          box-shadow: 0 2px 8px rgba(0,0,0,0.12);
          user-select: none;
          flex: 0 0 auto;
        }
        .eda-carousel button.nav:hover { background: rgba(255,255,255,0.95); }
        .eda-carousel .caption { text-align: center; margin-top: 6px; color: rgba(0,0,0,0.65); font-size: 14px; }
      ")),
      htmltools::tags$div(
        class = "eda-carousel-wrap",
        htmltools::tags$div(
          id = carousel_id,
          class = "eda-carousel",
          `data-idx` = "0",
          htmltools::tags$button(
            class = "nav prev",
            type = "button",
            onclick = sprintf("edaCarouselStep('%s', -1)", carousel_id),
            htmltools::HTML("&#10094;")
          ),
          htmltools::tags$div(
            class = "viewport",
            htmltools::tags$div(class = "slide active", htmltools::tags$img(src = img0, alt = "Accuracy plot (sorted by accuracy)")),
            htmltools::tags$div(class = "slide", htmltools::tags$img(src = img1, alt = "Accuracy plot (sorted by ID)"))
          ),
          htmltools::tags$button(
            class = "nav next",
            type = "button",
            onclick = sprintf("edaCarouselStep('%s', 1)", carousel_id),
            htmltools::HTML("&#10095;")
          )
        ),
        htmltools::tags$div(class = "caption", "Use arrows to switch: Sorted by Accuracy ↔ Sorted by ID")
      ),
      htmltools::tags$script(htmltools::HTML("
        function edaCarouselShow(id, idx) {
          const el = document.getElementById(id);
          if (!el) return;
          const slides = el.querySelectorAll('.slide');
          const n = slides.length;
          const i = ((idx % n) + n) % n;
          slides.forEach((s, k) => s.classList.toggle('active', k === i));
          el.setAttribute('data-idx', String(i));
        }
        function edaCarouselStep(id, delta) {
          const el = document.getElementById(id);
          if (!el) return;
          const cur = parseInt(el.getAttribute('data-idx') || '0', 10);
          edaCarouselShow(id, cur + delta);
        }
      "))
    )
  )
}
```
