---
title: "Exploratory Data Analysis Report"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: readable
    toc: true
    toc_float: true
params:
  cleaning_stats_agg: NA
  cleaning_stats_subj: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(knitr)
library(kableExtra)
library(dplyr)
```

# 1. Data Cleaning Statistics

This section summarizes data quality, including missed trials and trials with unrealistically fast reaction times (e.g., < 200ms).

## 1.1 Aggregate Statistics

```{r cleaning-agg}
if (!is.null(params$cleaning_stats_agg)) {
  params$cleaning_stats_agg %>%
    kable(digits = 2, caption = "Table 1.1: Aggregate Data Cleaning Statistics") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
} else {
  print("No aggregate statistics provided.")
}
```

## 1.2 Subject-Level Statistics

```{r cleaning-subj}
if (!is.null(params$cleaning_stats_subj)) {
  params$cleaning_stats_subj %>%
    dplyr::rename(
      "Subject ID" = participant_id,
      "Total Trials" = total_main_trials,
      "Missed" = n_missed_choice,
      "Fast RT" = n_fast_rt,
      "Valid Trials" = n_valid_trials,
      "Invalid Trials" = n_invalid_trials,
      "Valid (%)" = percent_valid_trials
    ) %>%
    kable(digits = 2, caption = "Table 1.2: Subject-Level Data Cleaning Summary") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE) %>%
    scroll_box(height = "500px")
} else {
  print("No subject-level statistics provided.")
}
```
