---
title: "EDA Results (LLM-Ready, Tables Only)"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output:
  github_document:
    toc: false
    html_preview: false
params:
  cleaning_stats_agg: NA
  cleaning_stats_subj: NA
  stim_pref_agg: NA
  stim_pref_subj: NA
  stim_pref_test: NA
  reward_rate_by_choice: NA
  reward_rate_over_bins: NA
  feedback_condition_overall: NA
  feedback_condition_by_subject: NA
  rt_summary_agg: NA
  rt_summary_subj: NA
  rt_over_bins: NA
  rt_by_condition_summary: NA
  rt_by_condition_data: NA
  accuracy_agg: NA
  accuracy_subj: NA
  accuracy_test: NA
  accuracy_over_bins: NA
  wsls_by_outcome_subj: NA
  prp_by_outcome_subj: NA
  wsls_test: NA
  wsls_loss_vs_wins_test: NA
  prp_test: NA
  reward_rate_subj: NA
  win_stay_overall_subj: NA
  glmm_stay_or: NA
  glmm_optimality_or: NA
  glmm_stay_report: NA
  glmm_optimality_report: NA
  questionnaire_scores_subj: NA
  questionnaire_scores_long: NA
  questionnaire_score_summaries: NA
  bis_ss_corr: NA
  bis_ss_lm: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
options(knitr.kable.NA = "NA")

library(dplyr)
library(tidyr)
library(knitr)

.as_tbl <- function(x) {
  #####
  # Convert common objects into a tibble suitable for printing
  #
  # Parameters
  # ----
  # x : any
  #     Object expected to be a tibble/data.frame, or NULL/NA placeholder
  #
  # Returns
  # ----
  # tibble | NULL
  #     A tibble for printing, or NULL if not printable.
  #####
  if (is.null(x)) return(NULL)
  if (length(x) == 1 && is.atomic(x) && is.na(x)) return(NULL)
  if (inherits(x, "data.frame")) return(dplyr::as_tibble(x))
  NULL
}

.kbl <- function(x, digits = 3) {
  #####
  # Print a tibble/data.frame as a Markdown table
  #
  # Parameters
  # ----
  # x : data.frame | tibble
  #     Table-like object
  # digits : integer
  #     Digits for numeric formatting (default: 3)
  #
  # Returns
  # ----
  # character
  #     Markdown table (as-is in the knitted document)
  #####
  x <- .as_tbl(x)
  if (is.null(x) || nrow(x) == 0) return(knitr::asis_output("_No data._\n"))
  knitr::kable(x, format = "pipe", digits = digits)
}

.pivot_wide_safe <- function(df, id_col, name_col, value_cols) {
  #####
  # Pivot long participant tables to wide format (safe for Markdown readability)
  #
  # Parameters
  # ----
  # df : tibble
  #     Long table to pivot
  # id_col : character
  #     ID column name (e.g., "participant_id")
  # name_col : character
  #     Column name holding the category names (e.g., "outcome_type")
  # value_cols : character
  #     Columns to pivot as values
  #
  # Returns
  # ----
  # tibble
  #     Wide table with prefixed columns
  #####
  df <- .as_tbl(df)
  if (is.null(df) || nrow(df) == 0) return(tibble::tibble())
  value_cols <- value_cols[value_cols %in% names(df)]
  if (length(value_cols) == 0) return(tibble::tibble())

  df %>%
    dplyr::mutate(
      "{name_col}" := as.character(.data[[name_col]]),
      "{id_col}" := as.character(.data[[id_col]])
    ) %>%
    tidyr::pivot_wider(
      id_cols = dplyr::all_of(id_col),
      names_from = dplyr::all_of(name_col),
      values_from = dplyr::all_of(value_cols),
      names_sep = "__"
    ) %>%
    dplyr::arrange(.data[[id_col]])
}
```

This file contains **tables and statistical summaries only** (no plots), structured for downstream LLM inspection.

- **Generated at**: `r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`

## 1) Data cleaning

### 1.1 Aggregate cleaning statistics

```{r}
.kbl(params$cleaning_stats_agg, digits = 2)
```

### 1.2 Participant-level cleaning statistics

```{r}
df <- .as_tbl(params$cleaning_stats_subj)
if (!is.null(df)) df <- df %>% dplyr::mutate(participant_id = as.character(participant_id))
.kbl(df, digits = 2)
```

## 2) Stimulus preference

### 2.1 Aggregate stimulus preference

```{r}
.kbl(params$stim_pref_agg, digits = 4)
```

### 2.2 Participant-level stimulus preference

```{r}
df <- .as_tbl(params$stim_pref_subj)
if (!is.null(df)) df <- df %>% dplyr::mutate(participant_id = as.character(participant_id))
.kbl(df, digits = 4)
```

### 2.3 Preference test (vs chance)

```{r}
.kbl(params$stim_pref_test, digits = 6)
```

## 3) Rewards & feedback conditions

### 3.1 Reward rate by chosen stimulus

```{r}
.kbl(params$reward_rate_by_choice, digits = 4)
```

### 3.2 Reward rate over trial bins

```{r}
.kbl(params$reward_rate_over_bins, digits = 4)
```

### 3.3 Feedback condition proportions (overall; valid trials)

```{r}
.kbl(params$feedback_condition_overall, digits = 4)
```

### 3.4 Feedback condition proportions (participant-level; valid trials)

```{r}
df <- .as_tbl(params$feedback_condition_by_subject)
wide <- .pivot_wide_safe(
  df = df,
  id_col = "participant_id",
  name_col = "condition_label",
  value_cols = c("n", "prop")
)
.kbl(wide, digits = 4)
```

## 4) Reaction time (RT)

### 4.1 Aggregate RT summary

```{r}
.kbl(params$rt_summary_agg, digits = 4)
```

### 4.2 RT summary by feedback condition

```{r}
.kbl(params$rt_by_condition_summary, digits = 4)
```

### 4.3 RT over trial bins

```{r}
.kbl(params$rt_over_bins, digits = 4)
```

### 4.4 Participant-level RT summary

```{r}
df <- .as_tbl(params$rt_summary_subj)
if (!is.null(df)) df <- df %>% dplyr::mutate(participant_id = as.character(participant_id))
.kbl(df, digits = 4)
```

## 5) Accuracy

### 5.1 Aggregate accuracy summary

```{r}
.kbl(params$accuracy_agg, digits = 4)
```

### 5.2 Accuracy test (vs chance)

```{r}
.kbl(params$accuracy_test, digits = 6)
```

### 5.3 Accuracy over trial bins

```{r}
.kbl(params$accuracy_over_bins, digits = 4)
```

### 5.4 Participant-level accuracy

```{r}
df <- .as_tbl(params$accuracy_subj)
if (!is.null(df)) df <- df %>% dplyr::mutate(participant_id = as.character(participant_id))
.kbl(df, digits = 4)
```

## 6) Choice strategy metrics (WSLS, PRP)

### 6.1 WSLS by previous outcome (participant-level)

```{r}
df <- .as_tbl(params$wsls_by_outcome_subj)
wide <- .pivot_wide_safe(
  df = df,
  id_col = "participant_id",
  name_col = "outcome_type",
  value_cols = c("n_opportunities", "n_stay", "prob_stay")
)
.kbl(wide, digits = 4)
```

### 6.2 WSLS tests

```{r}
.kbl(params$wsls_test, digits = 6)
```

```{r}
.kbl(params$wsls_loss_vs_wins_test, digits = 6)
```

### 6.3 PRP median by previous outcome (participant-level)

```{r}
df <- .as_tbl(params$prp_by_outcome_subj)
wide <- .pivot_wide_safe(
  df = df,
  id_col = "participant_id",
  name_col = "outcome_type_prp",
  value_cols = c("n_trials", "median_prp")
)
.kbl(wide, digits = 4)
```

### 6.4 PRP test

```{r}
.kbl(params$prp_test, digits = 6)
```

### 6.5 Reward rate (participant-level)

```{r}
df <- .as_tbl(params$reward_rate_subj)
if (!is.null(df)) df <- df %>% dplyr::mutate(participant_id = as.character(participant_id))
.kbl(df, digits = 4)
```

### 6.6 Overall win-stay probability (participant-level)

```{r}
df <- .as_tbl(params$win_stay_overall_subj)
if (!is.null(df)) df <- df %>% dplyr::mutate(participant_id = as.character(participant_id))
.kbl(df, digits = 4)
```

## 7) Model-agnostic GLMMs

### 7.1 GLMM: Stay probability by previous outcome

#### 7.1.1 Model specification

```{r}
spec <- params$glmm_stay_report$specification
if (is.null(spec) || length(spec) == 0) {
  knitr::asis_output("_No data._\n")
} else {
  cat(paste0("- formula: `", spec$formula, "`\n"))
  cat(paste0("- family: `", spec$family, "`\n"))
  cat(paste0("- reference level for outcome_type: `", spec$reference_level_outcome_type, "`\n"))
  cat(paste0("- n_observations: ", spec$n_observations, "\n"))
  cat(paste0("- n_participants: ", spec$n_participants, "\n"))
  cat(paste0("- optimizer / fitting method: `", spec$optimizer, "`\n"))
  cat(paste0("- convergence_warnings: `", ifelse(nchar(spec$convergence_warnings) == 0, "None", spec$convergence_warnings), "`\n"))
  cat(paste0("- singular_fit: `", spec$singular_fit, "`\n"))
}
```

#### 7.1.2 Fixed effects (log-odds scale)

```{r}
.kbl(params$glmm_stay_report$fixed_logit, digits = 6)
```

#### 7.1.3 Fixed effects (odds-ratio scale)

```{r}
.kbl(params$glmm_stay_report$fixed_or, digits = 6)
```

#### 7.1.4 Random effects

```{r}
.kbl(params$glmm_stay_report$random_effects, digits = 6)
```

#### 7.1.5 Planned contrasts from estimated marginal means

```{r}
.kbl(params$glmm_stay_report$contrasts, digits = 6)
```

#### 7.1.6 Estimated marginal means / predicted probabilities

```{r}
.kbl(params$glmm_stay_report$emmeans_prob, digits = 6)
```

#### 7.1.7 Notes

```{r}
notes <- params$glmm_stay_report$notes
if (is.null(notes) || length(notes) == 0) {
  knitr::asis_output("_No notes._\n")
} else {
  cat(paste0("- ", notes, collapse = "\n"))
  cat("\n")
}
```

### 7.2 GLMM: Choice optimality by previous outcome

#### 7.2.1 Model specification

```{r}
spec <- params$glmm_optimality_report$specification
if (is.null(spec) || length(spec) == 0) {
  knitr::asis_output("_No data._\n")
} else {
  cat(paste0("- formula: `", spec$formula, "`\n"))
  cat(paste0("- family: `", spec$family, "`\n"))
  cat(paste0("- reference level for prev_outcome: `", spec$reference_level_prev_outcome, "`\n"))
  cat(paste0("- n_observations: ", spec$n_observations, "\n"))
  cat(paste0("- n_participants: ", spec$n_participants, "\n"))
  cat(paste0("- optimizer / fitting method: `", spec$optimizer, "`\n"))
  cat(paste0("- convergence_warnings: `", ifelse(nchar(spec$convergence_warnings) == 0, "None", spec$convergence_warnings), "`\n"))
  cat(paste0("- singular_fit: `", spec$singular_fit, "`\n"))
}
```

#### 7.2.2 Fixed effects (log-odds scale)

```{r}
.kbl(params$glmm_optimality_report$fixed_logit, digits = 6)
```

#### 7.2.3 Fixed effects (odds-ratio scale)

```{r}
.kbl(params$glmm_optimality_report$fixed_or, digits = 6)
```

#### 7.2.4 Random effects

```{r}
.kbl(params$glmm_optimality_report$random_effects, digits = 6)
```

#### 7.2.5 Planned contrasts from estimated marginal means

```{r}
.kbl(params$glmm_optimality_report$contrasts, digits = 6)
```

#### 7.2.6 Estimated marginal means / predicted probabilities

```{r}
.kbl(params$glmm_optimality_report$emmeans_prob, digits = 6)
```

#### 7.2.7 Notes

```{r}
notes <- params$glmm_optimality_report$notes
if (is.null(notes) || length(notes) == 0) {
  knitr::asis_output("_No notes._\n")
} else {
  cat(paste0("- ", notes, collapse = "\n"))
  cat("\n")
}
```

## 8) Questionnaire scores

### 8.1 Questionnaire scores (participant-level)

```{r}
df <- .as_tbl(params$questionnaire_scores_subj)
if (!is.null(df)) df <- df %>% dplyr::mutate(participant_id = as.character(participant_id))
.kbl(df, digits = 4)
```

### 8.2 Questionnaire score summaries

```{r}
.kbl(params$questionnaire_score_summaries, digits = 4)
```

### 8.3 BIS vs SSS relationship

```{r}
.kbl(params$bis_ss_corr, digits = 6)
```

```{r}
.kbl(params$bis_ss_lm, digits = 6)
```
