---
title: "Winning Model Results (LLM-Ready, Tables Only)"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output:
  github_document:
    toc: false
    html_preview: false
params:
  metadata: NA
  model_comparison: NA
  parameter_summary: NA
  parameter_diagnostics: NA
  alpha_shift_hdi: NA
  notes: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
options(knitr.kable.NA = "NA")

library(dplyr)
library(knitr)

.as_tbl <- function(x) {
  #####
  # Convert common objects into a tibble suitable for printing
  #
  # Parameters
  # ----
  # x : any
  #     Object expected to be a tibble/data.frame, or NULL/NA placeholder
  #
  # Returns
  # ----
  # tibble | NULL
  #     A tibble for printing, or NULL if not printable
  #####
  if (is.null(x)) return(NULL)
  if (length(x) == 1 && is.atomic(x) && is.na(x)) return(NULL)
  if (inherits(x, "data.frame")) return(dplyr::as_tibble(x))
  NULL
}

.kbl <- function(x, digits = 3) {
  #####
  # Print a tibble/data.frame as a Markdown table
  #
  # Parameters
  # ----
  # x : data.frame | tibble
  #     Table-like object
  # digits : integer
  #     Digits for numeric formatting (default: 3)
  #
  # Returns
  # ----
  # character
  #     Markdown table (as-is in the knitted document)
  #####
  x <- .as_tbl(x)
  if (is.null(x) || nrow(x) == 0) return(knitr::asis_output("_No data._\n"))
  knitr::kable(x, format = "pipe", digits = digits)
}
```

This file contains **tables and statistical summaries only** for the winning reinforcement-learning model and its model-selection context.

- **Generated at**: `r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`

## 1) Run metadata

### 1.1 Metadata

```{r}
.kbl(params$metadata, digits = 4)
```

### 1.2 Notes

```{r}
notes <- params$notes
if (is.null(notes) || length(notes) == 0 || (length(notes) == 1 && is.na(notes))) {
  knitr::asis_output("_No notes._\n")
} else {
  cat(paste0("- ", notes, collapse = "\n"))
  cat("\n")
}
```

## 2) Model comparison context

### 2.1 LOO comparison across fitted models

```{r}
.kbl(params$model_comparison, digits = 4)
```

## 3) Parameter-level diagnostics

```{r}
.kbl(params$parameter_diagnostics, digits = 4)
```

## 4) Posterior parameter summaries

### 4.1 Key group-level parameters

```{r}
.kbl(params$parameter_summary, digits = 4)
```

### 4.2 Upper 95% interval for alpha_shift

```{r}
.kbl(params$alpha_shift_hdi, digits = 4)
```
