---
title: "Winning Model Posterior Predictive Checks (LLM-Ready, Tables Only)"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output:
  github_document:
    toc: false
    html_preview: false
params:
  metadata: NA
  ppc_discrepancy_summary: NA
  ppc_choice_distribution: NA
  ppc_accuracy: NA
  ppc_stay: NA
  ppc_learning_curve: NA
  ppc_prob_overview: NA
  ppc_prob_by_condition: NA
  artifact_paths: NA
  settings: NA
  notes: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
options(knitr.kable.NA = "NA")

library(dplyr)
library(knitr)

.as_tbl <- function(x) {
  #####
  # Convert common objects into a tibble suitable for printing
  #
  # Parameters
  # ----
  # x : any
  #     Object expected to be a tibble/data.frame, or NULL/NA placeholder
  #
  # Returns
  # ----
  # tibble | NULL
  #     A tibble for printing, or NULL if not printable
  #####
  if (is.null(x)) return(NULL)
  if (length(x) == 1 && is.atomic(x) && is.na(x)) return(NULL)
  if (inherits(x, "data.frame")) return(dplyr::as_tibble(x))
  NULL
}

.kbl <- function(x, digits = 3) {
  #####
  # Print a tibble/data.frame as a Markdown table
  #
  # Parameters
  # ----
  # x : data.frame | tibble
  #     Table-like object
  # digits : integer
  #     Digits for numeric formatting (default: 3)
  #
  # Returns
  # ----
  # character
  #     Markdown table (as-is in the knitted document)
  #####
  x <- .as_tbl(x)
  if (is.null(x) || nrow(x) == 0) return(knitr::asis_output("_No data._\n"))
  knitr::kable(x, format = "pipe", digits = digits)
}

.sub <- function(lst, key) {
  #####
  # Safely extract a named slot from a list-valued param
  #
  # Parameters
  # ----
  # lst : any
  #     Expected to be a list; may be NULL or NA
  # key : character
  #     Name to extract
  #
  # Returns
  # ----
  # any
  #     lst[[key]] if available, else NULL
  #####
  if (is.null(lst)) return(NULL)
  if (length(lst) == 1 && is.atomic(lst) && is.na(lst)) return(NULL)
  if (!is.list(lst)) return(NULL)
  lst[[key]]
}
```

Tables-only posterior predictive summaries for the winning reinforcement-learning model.

- **Generated at**: `r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`

## 1. Run metadata

```{r}
.kbl(params$metadata, digits = 4)
```

### 1.1 PPC settings

```{r}
.kbl(params$settings, digits = 4)
```

## 2. Discrepancy summary (at-a-glance)

```{r}
.kbl(params$ppc_discrepancy_summary, digits = 4)
```

## 3. Choice distribution PPC

### 3.1 Observed counts and proportions

```{r}
.kbl(.sub(params$ppc_choice_distribution, "observed"), digits = 4)
```

### 3.2 Replicated distribution (across simulations)

```{r}
.kbl(.sub(params$ppc_choice_distribution, "replicated_summary"), digits = 3)
```

### 3.3 Discrepancy

```{r}
.kbl(.sub(params$ppc_choice_distribution, "chi_squared"), digits = 4)
```

## 4. Overall accuracy PPC

### 4.1 Group-level summary

```{r}
.kbl(.sub(params$ppc_accuracy, "group_summary"), digits = 4)
```

### 4.2 Discrepancy

```{r}
.kbl(.sub(params$ppc_accuracy, "discrepancy"), digits = 4)
```

### 4.3 Per-subject comparison

```{r}
.kbl(.sub(params$ppc_accuracy, "per_subject"), digits = 4)
```

## 5. Conditional stay PPC

### 5.1 Observed stay probabilities by previous outcome

```{r}
.kbl(.sub(params$ppc_stay, "observed"), digits = 4)
```

### 5.2 Replicated stay probabilities by previous outcome

```{r}
.kbl(.sub(params$ppc_stay, "replicated_summary"), digits = 4)
```

### 5.3 Discrepancy

```{r}
.kbl(.sub(params$ppc_stay, "discrepancy"), digits = 4)
```

## 6. Learning curve PPC

### 6.1 Per-block observed vs replicated

```{r}
.kbl(.sub(params$ppc_learning_curve, "per_block"), digits = 4)
```

### 6.2 Discrepancy

```{r}
.kbl(.sub(params$ppc_learning_curve, "discrepancy"), digits = 4)
```

## 7. Aggregate choice probability PPC

### 7.1 Overview (pp_choice_stim2_prob)

```{r}
.kbl(params$ppc_prob_overview, digits = 4)
```

### 7.2 By feedback condition

```{r}
.kbl(params$ppc_prob_by_condition, digits = 4)
```

## 8. Saved PPC artifacts

```{r}
.kbl(params$artifact_paths, digits = 4)
```

## 9. Notes

```{r}
notes <- params$notes
if (is.null(notes) || length(notes) == 0 || (length(notes) == 1 && is.na(notes))) {
  knitr::asis_output("_No notes._\n")
} else {
  cat(paste0("- ", notes, collapse = "\n"))
  cat("\n")
}
```
