---
title: "Comprehensive Exploratory Data Analysis"
author: "Yannik Poth"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    theme: yeti
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, fig.width = 8, fig.asp = 0.618, out.width = "80%")
# Ensure webshot2 is available for saving gt tables if needed
# if (!requireNamespace("webshot2", quietly = TRUE)) {
#   install.packages("webshot2")
# }
```

# 1. Introduction

This document outlines the Exploratory Data Analysis (EDA) performed on the data collected for the study "Illuminating Decisions: How Salient Reward-Paired Cues Modulate Learning and Choice Behavior." The goal of this EDA is to understand the data structure, identify potential issues, examine distributions, and derive initial insights before formal statistical modeling.

# 2. Prerequisites

## 2.1 Load Necessary Packages
```{r load_packages}
# Core data manipulation and visualization
library(tidyverse)
library(dplyr) # Explicitly load dplyr for clarity, though part of tidyverse
library(ggplot2)
library(here) # For robust file path management
library(fs)   # For file system operations

# Summary statistics and EDA reports
library(skimr)
library(DataExplorer) # For automated EDA reports

# Plotting enhancements
library(patchwork)    # For combining ggplot objects
library(ggbeeswarm)   # For better point distributions in plots
library(ggpubr)       # For arranging plots and adding stats

# Table formatting
library(gt)
library(janitor)      # For cleaning data and table names

# Potentially useful for later checks, though not strictly EDA
# library(lme4)       # For mixed-effects models
# library(effects)    # For visualizing model effects
# library(car)        # For ANOVA and regression diagnostics
```

# 3. Load Data

## 3.1 Define Data Directories
```{r define_paths}
# Define data directory path using 'here' package for robustness
base_dir <- here::here()
data_dir <- file.path(base_dir, "bandit_task", "collected_data")

# Define output directory for figures and tables generated by this Rmd
output_figs_dir <- here::here("analysis_scripts", "data_inspection", "figures")
output_tables_dir <- here::here("analysis_scripts", "data_inspection", "tables")

# Create output directories if they don't exist
if (!dir.exists(output_figs_dir)) {
  dir.create(output_figs_dir, recursive = TRUE)
}
if (!dir.exists(output_tables_dir)) {
  dir.create(output_tables_dir, recursive = TRUE)
}

cat("Base directory:", base_dir, "\n")
cat("Data directory:", data_dir, "\n")
cat("Figures output directory:", output_figs_dir, "\n")
cat("Tables output directory:", output_tables_dir, "\n")
```

## 3.2 Load Task Data
```{r load_task_data}
# List all task data files
task_files <- fs::dir_ls(data_dir, regexp = "_task_data[.]csv$")
cat("Found", length(task_files), "task data files.\n")
# print(task_files) # Uncomment to see the list of files

# Function to read and preprocess a single task file
# Adapted from the user's existing data_inspection.Rmd
read_task_file <- function(file_path) {
  subject_id <- sub("_task_data[.]csv$", "", basename(file_path))
  data <- read_csv(file_path, col_types = cols(
    mode = col_character(),
    trial = col_integer(),
    choice = col_double(), # Read as double initially to handle potential non-integer inputs
    reaction_time = col_double(),
    reward = col_double(), # Read as double
    condition = col_integer(), # 0=non-salient, 1=salient, 2=missed
    reward_prob_1 = col_double(),
    reward_prob_2 = col_double()
  )) %>%
    mutate(
      subject_id = as.character(subject_id),
      # Convert choice to factor (Stimulus 1, Stimulus 2), with an explicit level for "Missed"
      choice = factor(choice, levels = c(0, 1), labels = c("Stimulus 1", "Stimulus 2")) %>%
        forcats::fct_explicit_na(na_level = "Missed"),
      # Reward: convert to factor for more descriptive summaries
      reward = factor(reward, levels = c(0, 1), labels = c("Loss", "Win")),
      # Condition: convert to factor for easier interpretation in plots/summaries
      condition = factor(condition, levels = c(0, 1, 2), labels = c("Non-Salient", "Salient", "Missed"))
    ) %>%
    filter(mode == "main") %>% # Keep only main trials
    select(subject_id, mode, trial, choice, reaction_time, reward, condition, reward_prob_1, reward_prob_2)
  
  return(data)
}

# Read and combine all task data files
all_task_data <- map_dfr(task_files, read_task_file)

cat("Successfully loaded and combined task data for", length(unique(all_task_data$subject_id)), "subjects.\n")
cat("Total main trials loaded:", nrow(all_task_data), "\n")
```

## 3.3 Load Questionnaire Data
```{r load_questionnaire_data}
# List all questionnaire data files
questionnaire_files <- fs::dir_ls(data_dir, regexp = "_questionnaire_data[.]csv$")
cat("Found", length(questionnaire_files), "questionnaire data files.\n")
# print(questionnaire_files) # Uncomment to see the list of files

# Function to read and preprocess a single questionnaire file
read_questionnaire_file <- function(file_path) {
  subject_id_from_filename <- sub("_questionnaire_data[.]csv$", "", basename(file_path))

  data <- read_csv(file_path, col_types = cols(.default = col_character()), show_col_types = FALSE)
  
  # 1. Clean all column names first to ensure consistency.
  data_cleaned <- data %>% janitor::clean_names()
  
  # 2. Determine the final subject_id using cleaned names.
  #    'participant_id' here refers to the *cleaned* column name.
  if ("participant_id" %in% names(data_cleaned)) {
    # If a 'participant_id' column exists (after cleaning), use it as the subject_id.
    # Ensure it's character. Rename it to 'subject_id'.
    # If 'participant_id' was already 'subject_id' after cleaning, this rename is fine.
    data_with_subject_id <- data_cleaned %>%
      mutate(subject_id = as.character(participant_id))
    
    # If the column 'participant_id' is NOT the same as the new 'subject_id' column
    # (i.e., we just copied from it and 'participant_id' wasn't already 'subject_id'),
    # then remove the original 'participant_id' column to avoid duplication.
    if ("participant_id" %in% names(data_with_subject_id) && "participant_id" != "subject_id") {
      data_with_subject_id <- data_with_subject_id %>% select(-participant_id)
    }
  } else {
    # If no 'participant_id' column, create 'subject_id' from the filename.
    # We need to add this new column.
    data_with_subject_id <- data_cleaned %>%
      mutate(subject_id = as.character(subject_id_from_filename))
  }
  
  # 'data_with_subject_id' now has a 'subject_id' column and all other names are cleaned.

  # 3. Convert data types for specific columns (using cleaned names).
  # These names must be the result of janitor::clean_names().

  # Define columns to be converted to ORDERED FACTOR (Likert scale)
  potential_ordered_factor_colnames <- c(
    grep("^bis_\\d+$", names(data_with_subject_id), value = TRUE)
  )
  cols_to_convert_to_ordered_factor <- intersect(potential_ordered_factor_colnames, names(data_with_subject_id))

  # Define columns to be converted to INTEGER (scores/counts)
  potential_integer_colnames <- c(
    # "bis_total", "sst", "sse", "ssd", "ssb", "ss_total" # These are scores, should be numeric to be safe
  )
  cols_to_convert_to_integer <- intersect(potential_integer_colnames, names(data_with_subject_id))

  # Define columns to be converted to NUMERIC
  # These are continuous measures, like percentages and scores.
  potential_numeric_colnames <- c("ss_percent", "bis_total", "sst", "sse", "ssd", "ssb", "ss_total")
  cols_to_convert_to_numeric <- intersect(potential_numeric_colnames, names(data_with_subject_id))

  # Define SSS columns to be converted to FACTOR with specific levels ('a', 'b')
  potential_sss_colnames <- grep("^sss_\\d+$", names(data_with_subject_id), value = TRUE)
  cols_to_convert_to_sss_factor <- intersect(potential_sss_colnames, names(data_with_subject_id))
  
  # Define other choice columns to be converted to a standard FACTOR
  potential_other_factor_colnames <- grep("^q_choice_", names(data_with_subject_id), value = TRUE)
  cols_to_convert_to_other_factor <- intersect(potential_other_factor_colnames, names(data_with_subject_id))

  # Apply conversions sequentially
  data_typed <- data_with_subject_id

  if (length(cols_to_convert_to_ordered_factor) > 0) {
    data_typed <- data_typed %>%
      mutate(across(all_of(cols_to_convert_to_ordered_factor), ~factor(., levels = c("1", "2", "3", "4"), ordered = TRUE)))
  }
  
  if (length(cols_to_convert_to_integer) > 0) {
    data_typed <- data_typed %>%
      mutate(across(all_of(cols_to_convert_to_integer), as.integer))
  }
  
  if (length(cols_to_convert_to_numeric) > 0) {
    data_typed <- data_typed %>%
      mutate(across(all_of(cols_to_convert_to_numeric), as.numeric))
  }

  if (length(cols_to_convert_to_sss_factor) > 0) {
    data_typed <- data_typed %>%
      mutate(across(all_of(cols_to_convert_to_sss_factor), ~factor(., levels = c("a", "b"))))
  }
  
  if (length(cols_to_convert_to_other_factor) > 0) {
    data_typed <- data_typed %>%
      mutate(across(all_of(cols_to_convert_to_other_factor), as.factor))
  }
  
  # 4. Ensure subject_id is character type (it should be, but as a final check).
  data_final <- data_typed %>%
    mutate(subject_id = as.character(subject_id))
    
  return(data_final)
}

# Read and combine all questionnaire data
all_questionnaire_data <- map_dfr(questionnaire_files, read_questionnaire_file)

cat("Successfully loaded and combined questionnaire data for", length(unique(all_questionnaire_data$subject_id)), "subjects.\n")
# Ensure subject_id is character type for merging
all_questionnaire_data <- all_questionnaire_data %>% mutate(subject_id = as.character(subject_id))
```

## 3.4 Merge Task and Questionnaire Data
```{r merge_data}
# Perform a left join to keep all task data and add questionnaire data where available
# Note: If a subject completed the task but not questionnaires, their questionnaire columns will be NA.
# If a subject completed questionnaires but has no task data (unlikely), they won't be in this merged set.
merged_data <- all_task_data %>%
  left_join(all_questionnaire_data, by = "subject_id")

cat("Successfully merged task and questionnaire data.\n")
cat("Dimensions of merged data: ", nrow(merged_data), "rows, ", ncol(merged_data), "columns.\n")
cat("Number of unique subjects in merged data: ", length(unique(merged_data$subject_id)), ".\n")

# Check for subjects in task data not found in questionnaire data (and vice-versa if needed)
subjects_in_task <- unique(all_task_data$subject_id)
subjects_in_quest <- unique(all_questionnaire_data$subject_id)

subjects_task_only <- setdiff(subjects_in_task, subjects_in_quest)
subjects_quest_only <- setdiff(subjects_in_quest, subjects_in_task)

if(length(subjects_task_only) > 0) {
  cat("Warning: The following subjects have task data but no matching questionnaire data based on subject_id:", paste(subjects_task_only, collapse=", "), "\n")
}
if(length(subjects_quest_only) > 0) {
  cat("Warning: The following subjects have questionnaire data but no matching task data based on subject_id (they will not be in 'merged_data' unless they also had task data):", paste(subjects_quest_only, collapse=", "), "\n")
}
```

# 4. General Exploratory Data Analysis (EDA) - Overview

## 4.1 Data Structure and Dimensions
```{r data_structure}
cat("Structure of the merged dataset:\n")
str(merged_data)
```


## 4.2 Basic Summary Statistics
```{r summary_stats_basic}
cat("Basic summary statistics for all variables:\n")
summary(merged_data)
```

## 4.3 Automated EDA Report with `DataExplorer`
This section generates a comprehensive HTML report.
The report will be optionally saved to `analysis_scripts/data_inspection/DataExplorer_Report.html`.
```{r dataexplorer_report, eval=TRUE}
# Generate the report (can take a moment for larger datasets)
# DataExplorer::create_report(
#   data = merged_data,
#   output_file = "DataExplorer_Report.html",
#   output_dir = here::here("analysis_scripts", "data_inspection"),
#   y = "reward", # Optional: specify a target variable
#   report_title = "EDA Report for Saliency Project Data"
# )
# cat("DataExplorer report generated. Check 'analysis_scripts/data_inspection/DataExplorer_Report.html'.\n")
# Note: For large datasets or if running non-interactively, you might comment this out after first run.
# For the purpose of this script, we'll show how to generate summaries for specific parts.

cat("DataExplorer: Plotting missing values profile.\n")
p_missing <- plot_missing(merged_data, ggtheme = theme_minimal(base_size=10))
print(p_missing)
ggsave(file.path(output_figs_dir, "missing_values_profile.png"), plot = p_missing, width = 10, height = 6)

# Custom plot for discrete variables to control ordering and variable inclusion
cat("\nDataExplorer: Plotting distributions of discrete (factor) variables.\n")

# 1. Select only factor variables. This naturally excludes character variables like subject_id and open questions.
discrete_vars_to_plot <- merged_data %>% 
  select(where(is.factor)) %>%
  names()

# 2. Create individual plots, respecting factor level order.
# Added a check to skip factors that are all NA.
discrete_plots_list <- map(discrete_vars_to_plot, ~{
  if (all(is.na(merged_data[[.x]]))) {
    return(NULL)
  }
  
  n_levels <- nlevels(merged_data[[.x]])
  x_axis_theme <- if (n_levels > 5) {
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
  } else {
    theme()
  }
  
  ggplot(merged_data, aes(x = .data[[.x]])) +
    geom_bar(fill = "steelblue", alpha = 0.8) +
    labs(title = .x, x = NULL, y = "Count") +
    theme_minimal(base_size = 10) +
    x_axis_theme
}) %>%
  purrr::compact() # Remove any NULLs from the list

# 3. Combine plots with patchwork and save with dynamic height
if (length(discrete_plots_list) > 0) {
  ncol_discrete_facet <- 4
  nrow_discrete_facet <- ceiling(length(discrete_plots_list) / ncol_discrete_facet)
  plot_height_discrete_facet <- max(5, 3 * nrow_discrete_facet)
  
  combined_discrete_plot <- patchwork::wrap_plots(.plots = discrete_plots_list, ncol = ncol_discrete_facet) + 
    plot_annotation(title = "Distributions of Discrete Variables", 
                    theme = theme(plot.title = element_text(face = "bold", size = 16, hjust = 0.5)))
  
  print(combined_discrete_plot)
  ggsave(file.path(output_figs_dir, "discrete_variables_distribution.png"), 
         plot = combined_discrete_plot, width = 12, height = plot_height_discrete_facet, units = "in")
} else {
  cat("No discrete (factor) variables to plot.\n")
}


cat("\nDataExplorer: Plotting distributions of continuous (numeric) variables.\n")
# Exclude variables that are not meaningful to view as distributions in this context
continuous_vars_to_plot <- merged_data %>%
  select(where(is.numeric), -any_of(c("trial", "reward_prob_1", "reward_prob_2"))) %>%
  names()

if (length(continuous_vars_to_plot) > 0) {
  continuous_plots_list <- map(continuous_vars_to_plot, ~{
    special_bin_vars <- c("sst", "sse", "ssd", "ssb", "ss_total")
    
    p <- ggplot(merged_data, aes(x = .data[[.x]]))
    
    if (.x %in% special_bin_vars) {
      p <- p + geom_histogram(aes(y = after_stat(density)), fill = "cornflowerblue", color = "black", alpha = 0.7, binwidth = 0.1)
    } else {
      p <- p + geom_histogram(aes(y = after_stat(density)), fill = "cornflowerblue", color = "black", alpha = 0.7, bins = 30)
    }
    
    p + geom_density(alpha = 0.2, fill = "lightblue") +
      labs(title = .x, x = NULL, y = "Density") +
      theme_minimal(base_size = 10)
  })

  ncol_continuous_facet <- 3 
  nrow_continuous_facet <- ceiling(length(continuous_plots_list) / ncol_continuous_facet)
  plot_height_continuous_facet <- max(6, 2.5 * nrow_continuous_facet)

  combined_continuous_plot <- patchwork::wrap_plots(.plots = continuous_plots_list, ncol = ncol_continuous_facet) +
    plot_annotation(title = "Distributions of Continuous Variables", 
                    theme = theme(plot.title = element_text(face = "bold", size = 16, hjust = 0.5)))
  
  print(combined_continuous_plot)
  ggsave(file.path(output_figs_dir, "continuous_variables_distribution.png"), 
         plot = combined_continuous_plot, width = 12, height = plot_height_continuous_facet, units = "in")
} else {
    cat("No continuous variables to plot after filtering.\n")
}


cat("\nDataExplorer: Plotting correlation heatmap for numeric variables.\n")
# Select only numeric columns for correlation, excluding variables where correlation is not meaningful.
numeric_data_for_corr <- merged_data %>% 
    select(where(is.numeric), -any_of(c("trial", "reward_prob_1", "reward_prob_2")))

if(ncol(numeric_data_for_corr) > 1) {
    if (!requireNamespace("ggcorrplot", quietly = TRUE)) {
      install.packages("ggcorrplot")
    }
    library(ggcorrplot)

    corr_matrix <- cor(numeric_data_for_corr, use = "pairwise.complete.obs")

    p_corr <- ggcorrplot(corr_matrix,
                         hc.order = TRUE,
                         type = "lower",
                         lab = TRUE,
                         lab_size = 2,
                         method = "circle",
                         colors = c("#6D9EC1", "white", "#E46726"),
                         title = "Correlation Matrix of Numeric Variables",
                         ggtheme = theme_minimal(base_size = 10)) +
      theme(plot.title = element_text(face="bold", hjust=0.5, size=rel(1.2)),
            axis.text.x = element_text(angle = 45, hjust = 1, size=rel(0.8)),
            axis.text.y = element_text(size=rel(0.8)))

  print(p_corr)
  ggsave(file.path(output_figs_dir, "numeric_correlation_heatmap.png"), plot = p_corr, width = 10, height = 8)
} else {
  cat("Not enough numeric columns to generate a correlation heatmap.\n")
}

```

# 5. EDA of Task Data (`all_task_data`)

This section focuses on the variables specific to the bandit task performance.

## 5.1 `choice` Variable
```{r task_choice_variable}
cat("Summary of 'choice' variable (Stimulus 1, Stimulus 2, Missed):\n")
choice_summary <- tabyl(all_task_data, choice) %>%
  adorn_totals("row") %>%
  adorn_pct_formatting(digits = 2)
print(choice_summary)

# Proportion of choices for Stimulus 0 vs Stimulus 1 (excluding NAs)
choice_proportions_valid <- all_task_data %>%
  filter(choice != "Missed") %>%
  count(choice) %>%
  mutate(prop = n / sum(n))
cat("\nProportion of valid choices (0 vs 1):\n")
print(choice_proportions_valid)

choice_plot <- ggplot(all_task_data %>% filter(choice != "Missed"), aes(x = choice, fill = choice)) +
  geom_bar(aes(y = (..count..)/sum(..count..)), alpha = 0.8) +
  scale_y_continuous(labels = scales::percent_format()) +
  scale_fill_manual(values = c("Stimulus 1" = "dodgerblue", "Stimulus 2" = "firebrick")) +
  labs(title = "Overall Proportion of Choices",
       x = "Choice",
       y = "Proportion") +
  theme_minimal() +
  theme(legend.position = "none", plot.title = element_text(face="bold"))
print(choice_plot)
ggsave(file.path(output_figs_dir, "choice_proportion_overall.png"), plot = choice_plot, width = 6, height = 4)

# Missed trials (where choice is "Missed")
missed_trials_summary <- all_task_data %>%
  group_by(subject_id) %>%
  summarise(
    n_total_trials = n(),
    n_missed_trials = sum(choice == "Missed"),
    prop_missed = n_missed_trials / n_total_trials,
    .groups = 'drop'
  )

cat("\nSummary of missed trials per subject:\n")
print(summary(missed_trials_summary$prop_missed))

missed_trials_plot <- ggplot(missed_trials_summary, aes(x = prop_missed)) +
  geom_histogram(binwidth = 0.01, fill = "salmon", color = "black", alpha = 0.7) +
  scale_x_continuous(labels = scales::percent_format()) +
  labs(title = "Distribution of Proportion of Missed Trials per Subject",
       x = "Proportion of Missed Trials",
       y = "Number of Subjects") +
  theme_minimal()
print(missed_trials_plot)
ggsave(file.path(output_figs_dir, "missed_trials_proportion_distribution.png"), plot = missed_trials_plot, width = 6, height = 4)

if(any(missed_trials_summary$prop_missed > 0.25)) { # Example threshold for high missed trials
    cat("\nWarning: Some subjects have a high proportion of missed trials (>25%):\n")
    print(missed_trials_summary %>% filter(prop_missed > 0.25) %>% arrange(desc(prop_missed)))
}
```

## 5.2 `reaction_time` Variable
This section analyzes reaction times (RTs) from the task. Trials with missed choices (NA `choice`) or NA `reaction_time` are typically excluded from RT analysis.

```{r task_rt_variable}
# Filter out trials not suitable for RT analysis
rt_analysis_data <- all_task_data %>%
  filter(choice != "Missed" & !is.na(reaction_time))

cat("Number of trials available for RT analysis:", nrow(rt_analysis_data), "\n")

# Overall summary statistics for reaction_time
cat("\nOverall summary statistics for Reaction Time (seconds):\n")
print(summary(rt_analysis_data$reaction_time))
cat("SD of Reaction Time:", sd(rt_analysis_data$reaction_time, na.rm = TRUE), "\n")
cat("IQR of Reaction Time:", IQR(rt_analysis_data$reaction_time, na.rm = TRUE), "\n")

# Define a threshold for "fast" RTs (e.g., < 150ms, consistent with old script)
fast_rt_threshold <- 0.150 

# Overall proportion of fast RTs
overall_fast_rts <- rt_analysis_data %>%
  summarise(
    n_total_valid_rt_trials = n(),
    n_fast_rt = sum(reaction_time < fast_rt_threshold, na.rm = TRUE),
    prop_fast_rt = n_fast_rt / n_total_valid_rt_trials
  )
cat(paste0("\nOverall proportion of trials with RT < ", fast_rt_threshold * 1000, "ms: ", 
           scales::percent(overall_fast_rts$prop_fast_rt, accuracy = 0.1), "\n"))

# Plot overall distribution of reaction times
rt_overall_dist_plot <- ggplot(rt_analysis_data, aes(x = reaction_time)) +
  geom_histogram(aes(y = after_stat(density)), binwidth = 0.05, fill = "cornflowerblue", color = "black", alpha = 0.7, boundary = 0) +
  geom_density(alpha = 0.2, fill = "lightblue") +
  geom_vline(xintercept = fast_rt_threshold, color = "red", linetype = "dashed", size = 1) +
  annotate("text", x = fast_rt_threshold + 0.05, y = Inf, label = paste0("Fast RT threshold (", fast_rt_threshold * 1000, "ms)"), 
           hjust = 0, vjust = 1.5, color = "red", size = 3.5) +
  scale_x_continuous(limits = c(0, NA), expand = expansion(mult = c(0.01, 0.05))) + # Show from 0, let upper limit be data-driven
  labs(title = "Overall Distribution of Reaction Times (Valid Trials)",
       subtitle = paste0("N = ", nrow(rt_analysis_data), " trials. Red line at ", fast_rt_threshold * 1000, "ms."),
       x = "Reaction Time (seconds)",
       y = "Density") +
  theme_minimal(base_size = 12) +
  theme(plot.title = element_text(face = "bold"),
        plot.subtitle = element_text(color = "grey30"))
print(rt_overall_dist_plot)
ggsave(file.path(output_figs_dir, "rt_overall_distribution.png"), plot = rt_overall_dist_plot, width = 7, height = 5)

# Summary of RTs per subject
rt_summary_per_subject <- rt_analysis_data %>%
  group_by(subject_id) %>%
  summarise(
    mean_rt = mean(reaction_time, na.rm = TRUE),
    median_rt = median(reaction_time, na.rm = TRUE),
    sd_rt = sd(reaction_time, na.rm = TRUE),
    min_rt = min(reaction_time, na.rm = TRUE),
    max_rt = max(reaction_time, na.rm = TRUE),
    n_valid_rt_trials = n(),
    n_fast_rt = sum(reaction_time < fast_rt_threshold, na.rm = TRUE),
    prop_fast_rt = n_fast_rt / n_valid_rt_trials,
    .groups = 'drop'
  )

cat("\nSummary statistics for Median RT per subject:\n")
print(summary(rt_summary_per_subject$median_rt))
cat("\nSummary statistics for Proportion of Fast RTs (<", fast_rt_threshold*1000, "ms) per subject:\n")
print(summary(rt_summary_per_subject$prop_fast_rt))

# Display table of subject-level RT summaries
rt_summary_table_gt <- rt_summary_per_subject %>%
  select(subject_id, mean_rt, median_rt, sd_rt, prop_fast_rt, n_valid_rt_trials) %>%
  gt() %>%
  fmt_number(columns = where(is.numeric) & !matches("n_valid_rt_trials"), decimals = 3) %>%
  fmt_percent(columns = prop_fast_rt, decimals = 1) %>%
  cols_label(
    subject_id = "Subject ID",
    mean_rt = "Mean RT (s)",
    median_rt = "Median RT (s)",
    sd_rt = "SD RT (s)",
    prop_fast_rt = paste0("% Fast RTs (<", fast_rt_threshold*1000, "ms)"),
    n_valid_rt_trials = "N Valid Trials"
  ) %>%
  tab_header(title = "Reaction Time Summary Statistics by Participant") %>%
  tab_options(table.width = pct(100))

# Explicitly display the table for the Rmd output by having it on its own line
rt_summary_table_gt

# Save the table to an external file
gtsave(rt_summary_table_gt, filename = file.path(output_tables_dir, "rt_summary_per_subject.html"))


# Plot RT distributions by subject (faceted histograms)
# Adapting from user's old script for highlighting
rt_summary_annot <- rt_summary_per_subject %>%
  mutate(
    label_text = paste0(round(prop_fast_rt*100, 1), "%"),
    highlight_flag = prop_fast_rt > 0.05 # Highlight if >5% fast RTs
  )

rt_data_highlighted <- rt_analysis_data %>%
  left_join(rt_summary_annot %>% select(subject_id, highlight_flag, label_text), by = "subject_id")

n_subjects_rt <- length(unique(rt_data_highlighted$subject_id))
ncol_rt_facet <- 4 # Number of columns for faceting

rt_subject_dist_plot <- ggplot(rt_data_highlighted, aes(x = reaction_time)) +
  geom_histogram(aes(y = after_stat(density), fill = highlight_flag), 
                 binwidth = 0.1, boundary = 0, color = "black", alpha = 0.7) +
  scale_fill_manual(values = c("TRUE" = "firebrick", "FALSE" = "grey80"), guide = "none") +
  geom_vline(xintercept = fast_rt_threshold, linetype = "dashed", color = "darkred", size = 0.6) +
  geom_text(data = rt_summary_annot, aes(x = Inf, y = Inf, label = label_text),
            hjust = 1.1, vjust = 1.5, size = 3, alpha = 0.8, 
            fontface = "bold", color = "black") +
  facet_wrap(~ subject_id, scales = "free_y", ncol = ncol_rt_facet) +
  scale_x_continuous(limits = c(0, NA), expand = expansion(mult = c(0.01, 0.05))) +
  scale_y_continuous(expand = expansion(mult = c(0.01, 0.15))) +
  labs(title = "Individual Reaction Time Distributions (Valid Trials)",
       subtitle = paste0("Dashed line: ",fast_rt_threshold*1000,"ms threshold. Highlighted if >5% trials < ",fast_rt_threshold*1000,"ms."),
       x = "Reaction Time (s)", y = "Density") +
  theme_bw(base_size = 10) +
  theme(plot.title = element_text(face = "bold", size=rel(1.2)),
        plot.subtitle = element_text(color = "grey30"),
        strip.background = element_blank(),
        strip.text = element_text(face = "bold"))

# Dynamically calculate height for the faceted plot
nrow_rt_facet = ceiling(n_subjects_rt / ncol_rt_facet)
plot_height_rt_facet = max(7, 2.5 * nrow_rt_facet)

print(rt_subject_dist_plot)
ggsave(file.path(output_figs_dir, "rt_subject_distributions.png"),
       plot = rt_subject_dist_plot, width = 12, height = plot_height_rt_facet, units = "in", dpi = 300)


# Reaction Time over Trial Blocks
# Create trial bins (e.g., 10 bins of 20 trials each for 200 trials)
rt_analysis_data <- rt_analysis_data %>%
  mutate(trial_bin = cut_number(trial, n = 10, labels = FALSE)) # Simpler binning

rt_over_bins_summary <- rt_analysis_data %>%
  group_by(trial_bin) %>%
  summarise(
    mean_rt_bin = mean(reaction_time, na.rm = TRUE),
    median_rt_bin = median(reaction_time, na.rm = TRUE),
    sem_rt_bin = sd(reaction_time, na.rm = TRUE) / sqrt(n()),
    .groups = 'drop'
  )

rt_learning_plot <- ggplot(rt_over_bins_summary, aes(x = trial_bin, y = median_rt_bin)) +
  geom_line(color = "blue", size = 1) +
  geom_point(color = "blue", size = 2) +
  geom_errorbar(aes(ymin = median_rt_bin - sem_rt_bin, ymax = median_rt_bin + sem_rt_bin), width = 0.2, color = "blue", alpha = 0.5) +
  labs(title = "Median Reaction Time Over Trial Bins",
       x = "Trial Bin (10 bins of 20 trials)",
       y = "Median Reaction Time (s) +/- SEM") +
  scale_x_continuous(breaks = 1:10) +
  theme_minimal(base_size = 12)+
  theme(plot.title = element_text(face="bold"))
print(rt_learning_plot)
ggsave(file.path(output_figs_dir, "rt_over_trial_bins.png"), plot = rt_learning_plot, width = 7, height = 5)


# Reaction Time by Condition (Salient vs. Non-Salient, excluding Missed)
rt_by_condition_summary <- rt_analysis_data %>%
  filter(condition %in% c("Salient", "Non-Salient")) %>% # Exclude "Missed" for this comparison
  group_by(subject_id, condition) %>%
  summarise(median_rt_condition = median(reaction_time, na.rm = TRUE), .groups = 'drop') %>%
  group_by(condition) %>%
  summarise(
    mean_of_median_rts = mean(median_rt_condition, na.rm = TRUE),
    sem_of_median_rts = sd(median_rt_condition, na.rm = TRUE) / sqrt(n()),
    .groups = 'drop'
    )

cat("\nMean of subject median RTs by condition:\n")
print(rt_by_condition_summary)

rt_condition_plot_data <- rt_analysis_data %>%
  filter(condition %in% c("Salient", "Non-Salient"))

rt_condition_boxplot <- ggplot(rt_condition_plot_data, aes(x = condition, y = reaction_time, fill = condition)) +
  geom_boxplot(alpha = 0.7, outlier.shape = NA) + # Hide outliers for cleaner boxplot
  geom_jitter(width = 0.1, alpha = 0.05, size=0.5) + # Add jittered raw points (very transparent)
  scale_y_continuous(limits = c(quantile(rt_condition_plot_data$reaction_time, 0.01), quantile(rt_condition_plot_data$reaction_time, 0.99))) + # Zoom in, trim outliers
  labs(title = "Reaction Time by Feedback Condition",
       subtitle = "Excluding missed trials. Boxes show median & IQR. Y-axis trimmed to 1st-99th percentile.",
       x = "Feedback Condition",
       y = "Reaction Time (s)") +
  theme_minimal(base_size = 12) +
  theme(legend.position = "none", plot.title = element_text(face="bold")) +
  scale_fill_manual(values = c("Non-Salient" = "grey70", "Salient" = "gold"))
print(rt_condition_boxplot)
ggsave(file.path(output_figs_dir, "rt_by_condition_boxplot.png"), plot = rt_condition_boxplot, width = 6, height = 5)

# Consider paired analysis later if investigating individual differences in RT by condition
# E.g. subject_median_rts_by_condition <- rt_analysis_data %>%
#   filter(condition %in% c("Salient", "Non-Salient")) %>%
#   group_by(subject_id, condition) %>%
#   summarise(median_rt = median(reaction_time), .groups = "drop")
# Then can plot paired differences or run paired t-test/Wilcoxon.
```

## 5.6 `reward` Variable
This section analyzes the rewards obtained by participants.
```{r task_reward_variable}
# Overall summary of the reward variable
cat("Summary of 'reward' variable (0 = No Reward, 1 = Reward, NA means choice was NA):\n")
reward_summary_overall <- tabyl(all_task_data, reward, show_na = TRUE) %>% # Includes NAs linked to NA choices
  adorn_totals("row") %>%
  adorn_pct_formatting(digits = 2)
print(reward_summary_overall)

# Filter to valid trials (where a choice was made)
reward_analysis_data <- all_task_data %>% filter(choice != "Missed")

cat("\nSummary of 'reward' variable for valid choices only:\n")
reward_summary_valid <- tabyl(reward_analysis_data, reward, show_na = TRUE) %>% # NAs here would be unexpected if choice is not NA
  adorn_totals("row") %>%
  adorn_pct_formatting(digits = 2)
print(reward_summary_valid)

if(any(is.na(reward_analysis_data$reward))) {
    cat("\nWarning: There are NA rewards even for trials where a choice was made. This might indicate a data issue.\n")
    print(reward_analysis_data %>% filter(is.na(reward)) %>% select(subject_id, trial, choice, reward))
}

# Overall reward rate (for valid choices)
overall_reward_rate <- reward_analysis_data %>%
  summarise(
    total_rewards = sum(reward == "Win", na.rm = TRUE),
    total_valid_trials = n(),
    reward_rate = total_rewards / total_valid_trials
  )
cat("\nOverall reward rate (for valid choices):", scales::percent(overall_reward_rate$reward_rate, accuracy = 0.1), "\n")

# Reward rate per subject
reward_rate_per_subject <- reward_analysis_data %>%
  group_by(subject_id) %>%
  summarise(
    n_rewards = sum(reward == "Win", na.rm = TRUE),
    n_valid_trials = n(),
    reward_rate = n_rewards / n_valid_trials,
    .groups = 'drop'
  )

cat("\nSummary of reward rates per subject:\n")
print(summary(reward_rate_per_subject$reward_rate))

reward_rate_subject_plot <- ggplot(reward_rate_per_subject, aes(x = reward_rate)) +
  geom_histogram(binwidth = 0.025, fill = "goldenrod", color = "black", alpha = 0.7) +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1)) +
  labs(title = "Distribution of Reward Rates per Subject",
       x = "Reward Rate",
       y = "Number of Subjects") +
  theme_minimal(base_size=12)+
  theme(plot.title = element_text(face="bold"))
print(reward_rate_subject_plot)
ggsave(file.path(output_figs_dir, "reward_rate_per_subject_distribution.png"), plot = reward_rate_subject_plot, width = 7, height = 5)

# Reward rate by choice (Stimulus 0 vs Stimulus 1)
reward_rate_by_choice <- reward_analysis_data %>%
  group_by(choice) %>%
  summarise(
    n_rewards = sum(reward == "Win", na.rm = TRUE),
    n_trials_for_choice = n(),
    reward_rate = n_rewards / n_trials_for_choice,
    .groups = 'drop'
  ) %>%
  mutate(choice_label = factor(choice, levels = c("Stimulus 1", "Stimulus 2")))

cat("\nReward rate by chosen stimulus (overall):\n")
print(reward_rate_by_choice %>% select(choice_label, reward_rate, n_trials_for_choice))

reward_rate_by_choice_plot <- ggplot(reward_rate_by_choice, aes(x = choice, y = reward_rate, fill = choice)) +
    geom_bar(stat = "identity", alpha = 0.8) +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
    scale_fill_manual(values = c("Stimulus 1" = "dodgerblue", "Stimulus 2" = "firebrick")) +
    labs(title = "Overall Reward Rate by Chosen Stimulus",
         x = "Stimulus Choice",
         y = "Reward Rate") +
    theme_minimal(base_size = 12) +
    theme(legend.position = "none", plot.title = element_text(face="bold"))

print(reward_rate_by_choice_plot)
ggsave(file.path(output_figs_dir, "reward_rate_by_choice.png"), plot = reward_rate_by_choice_plot, width = 6, height = 5)

# Reward acquisition over trial blocks (learning effect on rewards)
reward_analysis_data <- reward_analysis_data %>%
  mutate(trial_bin = cut_number(trial, n = 10, labels = FALSE)) # 10 bins of 20 trials

reward_over_bins_summary <- reward_analysis_data %>%
  group_by(trial_bin) %>%
  summarise(
    mean_reward_rate_bin = mean(reward == "Win", na.rm = TRUE), # mean of TRUE/FALSE (1/0) is the rate
    sem_reward_rate_bin = sd(reward == "Win", na.rm = TRUE) / sqrt(n()),
    .groups = 'drop'
  )

reward_learning_plot <- ggplot(reward_over_bins_summary, aes(x = trial_bin, y = mean_reward_rate_bin)) +
  geom_line(color = "darkgreen", size = 1) +
  geom_point(color = "darkgreen", size = 2) +
  geom_errorbar(aes(ymin = mean_reward_rate_bin - sem_reward_rate_bin, 
                    ymax = mean_reward_rate_bin + sem_reward_rate_bin), 
                width = 0.2, color = "darkgreen", alpha = 0.5) +
  scale_y_continuous(labels = scales::percent_format(accuracy=1), limits = c(0, NA)) +
  labs(title = "Mean Reward Rate Over Trial Bins",
       x = "Trial Bin (10 bins of 20 trials)",
       y = "Mean Reward Rate +/- SEM") +
  scale_x_continuous(breaks = 1:10) +
  theme_minimal(base_size = 12)+
  theme(plot.title = element_text(face="bold"))
print(reward_learning_plot)
ggsave(file.path(output_figs_dir, "reward_rate_over_trial_bins.png"), plot = reward_learning_plot, width = 7, height = 5)
```

## 5.7 `condition` Variable
This section analyzes the feedback condition (Non-Salient, Salient, Missed).
```{r task_condition_variable}
cat("Summary of 'condition' variable:\n")
# The 'condition' column was converted to a factor during data loading.
condition_summary_overall <- tabyl(all_task_data, condition, show_na = TRUE) %>%
  adorn_totals("row") %>%
  adorn_pct_formatting(digits = 2)
print(condition_summary_overall)

# Check if condition == "Missed" aligns with choice == "Missed"
# We expect 'condition == "Missed"' when 'choice' is "Missed", and 'condition' is 'Salient' or 'Non-Salient' when 'choice' is not "Missed".
condition_choice_xtab <- table(all_task_data$condition, all_task_data$choice == "Missed", useNA = "ifany",
                  dnn = c("Condition Factor", "Choice is Missed?"))
cat("\nCrosstabulation of Condition Factor vs. choice being 'Missed':\n")
print(condition_choice_xtab)

# Mismatches might indicate issues in data recording or preprocessing logic.
# Example: A trial has condition "Missed" but a choice is recorded, or vice-versa.
mismatched_condition_choice <- all_task_data %>%
  filter((condition == "Missed" & choice != "Missed") | (condition != "Missed" & choice == "Missed"))

if(nrow(mismatched_condition_choice) > 0){
  cat("\nWarning: Found", nrow(mismatched_condition_choice), "trials with mismatch between 'condition' and 'choice' being 'Missed'.\n")
  # print(head(mismatched_condition_choice)) # Uncomment to inspect some mismatches
} else {
  cat("\nConsistency check: 'condition' coding aligns with 'choice' == 'Missed' as expected.\n")
}

# Distribution of Salient vs. Non-Salient conditions for valid (non-missed) trials
condition_valid_trials_summary <- all_task_data %>%
  filter(choice != "Missed") %>% # equivalent to condition != "Missed" if consistent
  tabyl(condition, show_na = FALSE) %>% # show_na = FALSE as we've filtered
  adorn_totals("row") %>%
  adorn_pct_formatting(digits = 2)

cat("\nSummary of Salient vs. Non-Salient conditions for valid trials only:\n")
print(condition_valid_trials_summary)

condition_plot <- ggplot(all_task_data %>% filter(choice != "Missed"), aes(x = condition, fill = condition)) +
  geom_bar(aes(y = (..count..)/sum(..count..)), alpha = 0.8) +
  scale_y_continuous(labels = scales::percent_format()) +
  scale_fill_manual(values = c("Non-Salient" = "grey70", "Salient" = "gold")) +
  labs(title = "Proportion of Feedback Conditions (Valid Trials)",
       x = "Feedback Condition",
       y = "Proportion") +
  theme_minimal(base_size = 12) +
  theme(legend.position = "none", plot.title = element_text(face="bold")) +
  scale_fill_manual(values = c("Non-Salient" = "grey70", "Salient" = "gold"))
print(condition_plot)
ggsave(file.path(output_figs_dir, "condition_proportion_valid_trials.png"), plot = condition_plot, width = 6, height = 4)

# Check distribution of conditions per subject for valid trials
condition_per_subject_summary <- all_task_data %>%
  filter(choice != "Missed") %>%
  group_by(subject_id, condition) %>%
  summarise(n = n(), .groups = 'drop') %>%
  group_by(subject_id) %>%
  mutate(prop = n / sum(n))

cat("\nSummary of proportion of Salient condition per subject (for valid trials):\n")
print(summary(condition_per_subject_summary %>% filter(condition == "Salient") %>% pull(prop)))

condition_subject_plot <- ggplot(condition_per_subject_summary, aes(x = subject_id, y = prop, fill = condition)) +
  geom_bar(stat = "identity", position = "stack") +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(title = "Proportion of Feedback Conditions by Subject (Valid Trials)",
       x = "Subject ID",
       y = "Proportion of Trials",
       fill = "Condition") +
  theme_minimal(base_size = 10) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5),
        plot.title = element_text(face="bold")) +
  scale_fill_manual(values = c("Non-Salient" = "grey70", "Salient" = "gold", "Missed" = "grey85"))
print(condition_subject_plot)
ggsave(file.path(output_figs_dir, "condition_proportion_per_subject.png"), plot = condition_subject_plot, width = 10, height = 6)

```

## 5.8 `reward_prob_1` and `reward_prob_2` Variables
These variables represent the underlying reward probabilities for Stimulus 1 (choice 0) and Stimulus 2 (choice 1) respectively. They are crucial for understanding if participants learn to track these probabilities.

```{r task_reward_probs_variable}
cat("Summary of reward_prob_1 (p(Reward | Stimulus 1/Choice 0)):\n")
print(summary(all_task_data$reward_prob_1))
cat("SD of reward_prob_1:", sd(all_task_data$reward_prob_1, na.rm = TRUE), "\n")

cat("\nSummary of reward_prob_2 (p(Reward | Stimulus 2/Choice 1)):\n")
print(summary(all_task_data$reward_prob_2))
cat("SD of reward_prob_2:", sd(all_task_data$reward_prob_2, na.rm = TRUE), "\n")

# Check for NAs in reward probabilities
if(any(is.na(all_task_data$reward_prob_1)) || any(is.na(all_task_data$reward_prob_2))) {
  cat("\nWarning: Found NA values in reward_prob_1 or reward_prob_2. This could affect accuracy calculations.\n")
  print(all_task_data %>% filter(is.na(reward_prob_1) | is.na(reward_prob_2)) %>% select(subject_id, trial, reward_prob_1, reward_prob_2))
}

# Plot distributions of reward probabilities
rp_plot_data <- all_task_data %>%
  select(trial, reward_prob_1, reward_prob_2) %>%
  pivot_longer(cols = c(reward_prob_1, reward_prob_2), names_to = "probability_type", values_to = "probability") %>%
  mutate(probability_type = factor(probability_type, 
                                   levels = c("reward_prob_1", "reward_prob_2"), 
                                   labels = c("p(Reward | Stimulus 1)", "p(Reward | Stimulus 2)")))

rp_dist_plot <- ggplot(rp_plot_data, aes(x = probability, fill = probability_type)) +
  geom_histogram(binwidth = 0.05, position = "dodge", alpha = 0.7, color = "black") +
  facet_wrap(~ probability_type, scales = "free_y") +
  labs(title = "Distribution of Underlying Reward Probabilities",
       x = "Reward Probability",
       y = "Frequency (Trial Count)") +
  theme_minimal(base_size = 12) +
  theme(legend.position = "none", plot.title = element_text(face="bold")) +
  scale_fill_manual(values = c("p(Reward | Stimulus 1)" = "dodgerblue", "p(Reward | Stimulus 2)" = "firebrick"))
print(rp_dist_plot)
ggsave(file.path(output_figs_dir, "reward_probabilities_distribution.png"), plot = rp_dist_plot, width = 8, height = 4)


# Visualize reward probabilities over trials for a few example subjects
# Using similar combined plot as in user's old script (section 6)
example_subject_ids <- unique(all_task_data$subject_id)[1:min(3, length(unique(all_task_data$subject_id)))] # Take first 3 subjects

# Ensure the subdirectory for these plots exists
reward_prob_plots_dir <- file.path(output_figs_dir, "reward_prob_plots_combined_new")
if (!dir.exists(reward_prob_plots_dir)) {
  dir.create(reward_prob_plots_dir, recursive = TRUE)
}

for (subj_id in example_subject_ids) {
  subject_data <- all_task_data %>% filter(subject_id == subj_id)
  
  # Filter data for salient feedback points (used for points on the plot)
  salient_feedback_A <- subject_data %>% filter(condition == "Salient" & choice == "Stimulus 1")
  salient_feedback_B <- subject_data %>% filter(condition == "Salient" & choice == "Stimulus 2")
  
  # Combine salient feedback trials for vlines (any salient feedback, regardless of choice)
  vline_data <- subject_data %>% filter(condition == "Salient") %>% distinct(trial)

  combined_plot_single <- ggplot(subject_data, aes(x = trial)) +
    geom_line(aes(y = reward_prob_1, color = "Stimulus 1"), size = 0.8) +
    geom_line(aes(y = reward_prob_2, color = "Stimulus 2"), size = 0.8) +
    geom_vline(data = vline_data, aes(xintercept = trial), 
               color = "grey60", linetype = "dashed", size = 0.4, alpha = 0.7) +
    geom_point(data = salient_feedback_A, aes(y = reward_prob_1), 
               shape = 21, color = "black", fill = "gold", size = 2.5, stroke = 0.5, alpha=0.8) +
    geom_point(data = salient_feedback_B, aes(y = reward_prob_2), 
               shape = 21, color = "black", fill = "gold", size = 2.5, stroke = 0.5, alpha=0.8) +
    scale_color_manual(values = c("Stimulus 1" = "dodgerblue", "Stimulus 2" = "firebrick"), 
                       labels = c("Stimulus 1" = "p(Reward | Stimulus 1)", "Stimulus 2" = "p(Reward | Stimulus 2)")) +
    scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.25)) +
    labs(title = paste("Subject", subj_id, ": Reward Probabilities & Salient Feedback Events"),
         subtitle = "Yellow points indicate salient feedback was delivered for the chosen stimulus on that trial. Dashed lines are any salient feedback trial.",
         y = "p(Reward)", x = "Trial") +
    theme_bw(base_size = 10) +
    theme(plot.title = element_text(face = "bold", hjust = 0.5, size=rel(1.1)),
          plot.subtitle = element_text(hjust = 0.5, size=rel(0.9), color="gray30"),
          legend.position = c(0.98, 0.98),
          legend.justification = c("right", "top"),
          legend.title = element_blank(),
          legend.background = element_rect(color = "black", fill = alpha("white", 0.8), linetype = "solid", linewidth=0.3))
  
  print(combined_plot_single) # Show in Rmd output
  ggsave(
    filename = file.path(reward_prob_plots_dir, paste0("reward_probs_subj_", subj_id, ".png")),
    plot = combined_plot_single,
    width = 9, height = 5, units = "in", dpi = 200
  )
}
cat(paste("\nExample reward probability plots saved to:", reward_prob_plots_dir, "\n"))
```

# 6. EDA of Questionnaire Data (`all_questionnaire_data`)

This section focuses on the variables from the questionnaire data. We will use `all_questionnaire_data` as `merged_data` contains trial-level repetitions of this.
```{r questionnaire_data_overview}
cat("Dimensions of questionnaire data:
")
print(dim(all_questionnaire_data))

cat("\nStructure of questionnaire data:
")
# Using glimpse for a concise view
glimpse(all_questionnaire_data)

cat("\nColumn names in questionnaire data:
")
print(names(all_questionnaire_data))

# Subjects in questionnaire data
cat("\nNumber of unique subjects in questionnaire data:", length(unique(all_questionnaire_data$subject_id)), "\n")

# Use skimr for a good summary of questionnaire variables
cat("\nDetailed summary of questionnaire variables using skimr::skim():\n")
skim(all_questionnaire_data)
```

## 6.1 Distribution of Key Questionnaire Scores
We will focus on the total scores for BIS (Barratt Impulsiveness Scale) and SSS (Sensation Seeking Scale), as well as SSS subscales.

```{r questionnaire_score_distributions, fig.width=10, fig.asp=0.7}
# Define key questionnaire score columns to analyze from the cleaned names
# These should match the janitor::clean_names() output
key_score_cols <- c("bis_total", "ss_total", "sst", "sse", "ssd", "ssb")

# Check which of these key scores are actually present in the data
present_score_cols <- key_score_cols[key_score_cols %in% names(all_questionnaire_data)]

if(length(present_score_cols) == 0) {
  cat("\nNo key questionnaire score columns (bis_total, ss_total, sst, sse, ssd, ssb) found in the data. Skipping score distribution analysis.\n")
} else {
  cat(paste("\nAnalyzing distributions for the following scores:", paste(present_score_cols, collapse=", "), "\n"))
  
  # Pivot longer for easier plotting with ggplot
  questionnaire_scores_long <- all_questionnaire_data %>% 
    select(subject_id, all_of(present_score_cols)) %>%
    pivot_longer(cols = all_of(present_score_cols), names_to = "scale_name", values_to = "score") %>% 
    filter(!is.na(score)) # Remove rows where score is NA for plotting
  
  # Histograms and Density plots for each key score
  score_dist_plots <- ggplot(questionnaire_scores_long, aes(x = score)) +
    geom_histogram(aes(y = after_stat(density)), binwidth = function(x) 2 * IQR(x, na.rm=TRUE) / (length(x)^(1/3)), 
                   fill = "skyblue", color = "black", alpha = 0.7) + # Freedman-Diaconis rule for binwidth
    geom_density(alpha = 0.2, fill = "lightblue") +
    facet_wrap(~ scale_name, scales = "free") +
    labs(title = "Distribution of Key Questionnaire Scores",
         x = "Score",
         y = "Density") +
    theme_minimal(base_size = 10) +
    theme(plot.title = element_text(face="bold", size=rel(1.2)),
          strip.text = element_text(face="bold"))
  
  print(score_dist_plots)
  ggsave(file.path(output_figs_dir, "questionnaire_score_distributions.png"), plot = score_dist_plots, width = 10, height = max(6, 2*ceiling(length(present_score_cols)/3)))
  
  # Boxplots for each key score to check for outliers
  score_boxplots <- ggplot(questionnaire_scores_long, aes(y = score)) +
    geom_boxplot(fill = "lightcoral", alpha = 0.7, outlier.colour = "red") +
    facet_wrap(~ scale_name, scales = "free") +
    labs(title = "Boxplots of Key Questionnaire Scores",
         y = "Score") +
    theme_minimal(base_size = 10) +
    theme(plot.title = element_text(face="bold", size=rel(1.2)),
          strip.text = element_text(face="bold"),
          axis.text.x = element_blank(), # No x-axis text needed
          axis.ticks.x = element_blank())
  print(score_boxplots)
  ggsave(file.path(output_figs_dir, "questionnaire_score_boxplots.png"), plot = score_boxplots, width = 10, height = max(6, 2*ceiling(length(present_score_cols)/3)))
  
  # Descriptive statistics table for these scores
  desc_stats_scores <- all_questionnaire_data %>% 
    select(all_of(present_score_cols)) %>% 
    skim() %>% # Using skim for detailed descriptives
    select(skim_variable, numeric.mean, numeric.sd, numeric.p0, numeric.p25, numeric.p50, numeric.p75, numeric.p100, numeric.hist) %>% 
    rename(
      Scale = skim_variable,
      Mean = numeric.mean,
      SD = numeric.sd,
      Min = numeric.p0,
      Q1 = numeric.p25,
      Median = numeric.p50,
      Q3 = numeric.p75,
      Max = numeric.p100,
      Histogram = numeric.hist
    ) %>% dplyr::as_tibble() # Explicitly convert to a standard tibble

  cat("\nDescriptive statistics for key questionnaire scores:\n")
  # Print as a simple table for console
  print(desc_stats_scores, n = Inf)
  
  # Save as a gt table
  if (nrow(desc_stats_scores) > 0) {
    gt_desc_stats_scores <- desc_stats_scores %>% 
      gt() %>% 
      fmt_number(columns = where(is.numeric) & !matches("Histogram"), decimals = 2) %>%
      tab_header(title = "Descriptive Statistics for Key Questionnaire Scores") %>% 
      cols_align(align = "center", columns = Histogram)
    
    # Explicitly display the table for Rmd output
    gt_desc_stats_scores
    
    # Save the table to an external file
    gtsave(gt_desc_stats_scores, filename = file.path(output_tables_dir, "questionnaire_score_descriptives.html"))
  }
}
```

## 6.2 Correlations Between Questionnaire Scores
This section examines the relationships between the different questionnaire scores.

```{r questionnaire_score_correlations, fig.width=8, fig.asp=1}
if(length(present_score_cols) < 2) {
  cat("\nNot enough key questionnaire score columns present to calculate correlations. Skipping.\n")
} else {
  questionnaire_scores_for_corr <- all_questionnaire_data %>% 
    select(all_of(present_score_cols)) %>% 
    # Ensure all selected columns are numeric for correlation, drop non-numeric if any sneaked in.
    select(where(is.numeric))
  
  if(ncol(questionnaire_scores_for_corr) < 2) {
    cat("\nNot enough numeric key questionnaire score columns present for correlation. Skipping.\n")
  } else {
    # Calculate correlation matrix
    corr_matrix <- cor(questionnaire_scores_for_corr, use = "pairwise.complete.obs")
    
    cat("\nCorrelation matrix for key questionnaire scores:\n")
    print(round(corr_matrix, 2))
    
    # Visualize correlation matrix using DataExplorer::plot_correlation or ggcorrplot
    # Using DataExplorer style for consistency if preferred, or a more traditional heatmap
    # plot_correlation(questionnaire_scores_for_corr, type = "continuous", cor_args = list(use = "pairwise.complete.obs"))
    # ggsave(file.path(output_figs_dir, "questionnaire_score_correlation_matrix_de.png"), width = 8, height = 7)

    # Using ggcorrplot for a potentially cleaner heatmap for fewer variables
    if (!requireNamespace("ggcorrplot", quietly = TRUE)) {
      install.packages("ggcorrplot")
    }
    library(ggcorrplot)
    
    corr_plot <- ggcorrplot(corr_matrix,
                              hc.order = TRUE, # Hierarchical clustering to group similar variables
                              type = "lower",    # Show lower triangle
                              lab = TRUE,        # Show correlation coefficients
                              lab_size = 3,
                              method = "circle", # Method for visualizing correlations (alt: "square")
                              colors = c("#6D9EC1", "white", "#E46726"), # Blue-White-Red color scheme
                              title = "Correlation Matrix of Key Questionnaire Scores",
                              ggtheme = theme_minimal(base_size = 10)) +
      theme(plot.title = element_text(face="bold", hjust=0.5, size=rel(1.2)),
            legend.title = element_text(size=rel(0.9)),
            legend.text = element_text(size=rel(0.8)))
    
    print(corr_plot)
    ggsave(file.path(output_figs_dir, "questionnaire_score_correlation_matrix.png"), plot = corr_plot, width = 8, height = 7)

    # Specific scatter plot for BIS Total vs SS Total, if both are present
    if ("bis_total" %in% present_score_cols && "ss_total" %in% present_score_cols) {
      bis_ss_scatter <- ggplot(all_questionnaire_data, aes(x = bis_total, y = ss_total)) +
        geom_point(alpha = 0.6, color = "purple") +
        geom_smooth(method = "lm", color = "black", se = FALSE, linetype="dashed") +
        labs(title = "Relationship between BIS Total and SSS Total Scores",
             x = "BIS Total Score",
             y = "SSS Total Score") +
        theme_minimal(base_size = 12)+
        theme(plot.title = element_text(face="bold"))
      print(bis_ss_scatter)
      ggsave(file.path(output_figs_dir, "bis_total_vs_ss_total_scatter.png"), plot = bis_ss_scatter, width = 7, height = 6)
    } else {
      cat("\nbis_total or ss_total not found, skipping their specific scatter plot.\n")
    }
  }
}
```

# 7. Relationships between Task Performance and Questionnaire Scores

This section explores how individual differences in questionnaire scores relate to key behavioral metrics derived from the task data. We will use the `merged_data` for this, aggregating task metrics per subject.

```{r task_questionnaire_relationships_setup}
# First, ensure key per-subject task metrics are calculated and available.
# Some might have been calculated in section 5 (e.g., rt_summary_per_subject, reward_rate_per_subject)
# We also need accuracy and potentially win-stay probabilities per subject.

# --- 7.1 Calculate Accuracy Per Subject (if not already done comprehensively) ---
# This calculation should be consistent with how accuracy is defined for your project.
# Typically: choosing the option with the higher reward_prob_X.
# Using a simplified version here, assuming reward_prob_1 and reward_prob_2 are available and complete.

subject_accuracy_summary <- merged_data %>% 
  filter(choice != "Missed" & !is.na(reward_prob_1) & !is.na(reward_prob_2)) %>% # Valid trials for accuracy
  # Ensure reaction_time filtering is applied if it was in previous accuracy calculations
  # filter(is.na(reaction_time) | reaction_time >= fast_rt_threshold) %>% # Optional: consistent RT filter
  mutate(
    chose_better_option = case_when(
      reward_prob_1 > reward_prob_2 ~ ifelse(choice == "Stimulus 1", 1, 0),
      reward_prob_2 > reward_prob_1 ~ ifelse(choice == "Stimulus 2", 1, 0),
      reward_prob_1 == reward_prob_2 ~ 0.5, # Or NA, or handle as per study protocol
      TRUE ~ NA_real_
    )
  ) %>% 
  filter(!is.na(chose_better_option)) %>% # Remove trials where accuracy couldn't be determined
  group_by(subject_id) %>% 
  summarise(
    mean_accuracy = mean(chose_better_option, na.rm = TRUE),
    n_accuracy_trials = n(),
    .groups = 'drop'
  )

cat("\nPer-subject accuracy summary calculated.\n")
# print(head(subject_accuracy_summary))

# --- 7.2 Consolidate Per-Subject Metrics ---
# Consolidate various per-subject metrics into one tibble.
# Start with questionnaire data (one row per subject)
subject_summary_data <- all_questionnaire_data %>% 
  select(subject_id, all_of(present_score_cols)) # Use only scores confirmed to be present

# Merge with RT summary (ensure it exists from section 5.5)
if (exists("rt_summary_per_subject")) {
  subject_summary_data <- subject_summary_data %>% 
    left_join(rt_summary_per_subject %>% select(subject_id, median_rt, prop_fast_rt), by = "subject_id")
} else {
  cat("\nWarning: rt_summary_per_subject not found. Skipping RT metrics in merged subject summary.\n")
}

# Merge with reward rate summary (ensure it exists from section 5.6)
if (exists("reward_rate_per_subject")) {
  subject_summary_data <- subject_summary_data %>% 
    left_join(reward_rate_per_subject %>% select(subject_id, reward_rate), by = "subject_id")
} else {
  cat("\nWarning: reward_rate_per_subject not found. Skipping reward rate in merged subject summary.\n")
}

# Merge with accuracy summary
subject_summary_data <- subject_summary_data %>% 
  left_join(subject_accuracy_summary %>% select(subject_id, mean_accuracy), by = "subject_id")

cat("\nConsolidated subject summary data created with task and questionnaire metrics:\n")
# Glimpse the first few rows and structure of this subject_summary_data
glimpse(subject_summary_data)

# Check for NAs that might have arisen from joins or calculations
cat("\nMissing values in the consolidated subject_summary_data:\n")
print(colSums(is.na(subject_summary_data)))
```

## 7.3 Correlations between Questionnaire Scores and Task Metrics

```{r task_questionnaire_correlations, fig.width=10, fig.asp=0.8}
# Select only numeric columns from subject_summary_data for correlation
# This should include the key questionnaire scores and the task metrics (median_rt, prop_fast_rt, reward_rate, mean_accuracy)
corr_data_task_quest <- subject_summary_data %>% 
  select(where(is.numeric)) %>% 
  # Optionally remove subject_id if it was numeric and selected, though it should be character
  select(-any_of(c("subject_id"))) 

if(ncol(corr_data_task_quest) < 2) {
  cat("\nNot enough numeric columns in subject_summary_data to calculate correlations. Skipping.\n")
} else {
  # Calculate correlation matrix
  corr_matrix_task_quest <- cor(corr_data_task_quest, use = "pairwise.complete.obs")
  
  cat("\nCorrelation matrix for questionnaire scores and task performance metrics:\n")
  print(round(corr_matrix_task_quest, 2))
  
  # Visualize correlation matrix
  corr_plot_task_quest <- ggcorrplot(corr_matrix_task_quest,
                                     hc.order = TRUE,
                                     type = "lower",
                                     lab = TRUE,
                                     lab_size = 2.5, # Adjusted for potentially more variables
                                     method = "circle",
                                     colors = c("#6D9EC1", "white", "#E46726"),
                                     title = "Correlations: Questionnaire Scores vs. Task Metrics",
                                     ggtheme = theme_minimal(base_size = 10)) +
    theme(plot.title = element_text(face="bold", hjust=0.5, size=rel(1.1)),
          axis.text.x = element_text(angle = 45, hjust = 1, size=rel(0.8)), # Rotate x-axis labels
          axis.text.y = element_text(size=rel(0.8)),
          legend.title = element_text(size=rel(0.9)),
          legend.text = element_text(size=rel(0.8)))
  
  print(corr_plot_task_quest)
  ggsave(file.path(output_figs_dir, "task_metrics_questionnaire_correlation_matrix.png"), 
         plot = corr_plot_task_quest, width = 10, height = 8)
  
  # Example Scatter Plots for specific interesting correlations
  # For example, BIS total vs. Mean Accuracy
  if ("bis_total" %in% names(subject_summary_data) && "mean_accuracy" %in% names(subject_summary_data)) {
    scatter_bis_accuracy <- ggplot(subject_summary_data, aes(x = bis_total, y = mean_accuracy)) +
      geom_point(alpha = 0.7, color = "darkcyan") +
      geom_smooth(method = "lm", se = TRUE, color = "black", fill="lightgray") +
      labs(title = "BIS Total Score vs. Mean Task Accuracy",
           x = "BIS Total Score",
           y = "Mean Accuracy") +
      theme_minimal(base_size = 12)+
        theme(plot.title = element_text(face="bold"))
    print(scatter_bis_accuracy)
    ggsave(file.path(output_figs_dir, "scatter_bis_total_vs_accuracy.png"), plot = scatter_bis_accuracy, width = 7, height = 6)
  } else {
      cat("\nbis_total or mean_accuracy not found in subject_summary_data, skipping their specific scatter plot.\n")
  }
  
  # Example: SS Total vs. Proportion of Fast RTs
  if ("ss_total" %in% names(subject_summary_data) && "prop_fast_rt" %in% names(subject_summary_data)) {
    scatter_sss_fast_rt <- ggplot(subject_summary_data, aes(x = ss_total, y = prop_fast_rt)) +
      geom_point(alpha = 0.7, color = "chocolate") +
      geom_smooth(method = "lm", se = TRUE, color = "black", fill="lightgray") +
      scale_y_continuous(labels = scales::percent) +
      labs(title = "SSS Total Score vs. Proportion of Fast RTs",
           x = "SSS Total Score",
           y = "Proportion of Fast RTs (<", fast_rt_threshold*1000, "ms)") +
      theme_minimal(base_size = 12)+
        theme(plot.title = element_text(face="bold"))
    print(scatter_sss_fast_rt)
    ggsave(file.path(output_figs_dir, "scatter_ss_total_vs_prop_fast_rt.png"), plot = scatter_sss_fast_rt, width = 7, height = 6)
  } else {
      cat("\nss_total or prop_fast_rt not found in subject_summary_data, skipping their specific scatter plot.\n")
  }
}
```

# 8. Specific EDA for Reinforcement Learning Study Hypotheses

This section delves into analyses directly relevant to the study's hypotheses, such as win-stay/lose-shift behavior and post-reinforcement pauses, comparing across conditions.

## 8.1 Win-Stay / Lose-Shift (WSLS) Analysis

Win-Stay, Lose-Shift analysis helps understand basic choice strategies. We are particularly interested in comparing win-stay probabilities following salient vs. non-salient rewards.

```{r wsls_analysis}
# We need to lag choice and reward to relate outcome on trial t-1 to choice on trial t
# Ensure data is ordered by subject and trial for correct lagging
wsls_data <- all_task_data %>%
  filter(choice != "Missed" & !is.na(reward)) %>% # Only valid trials
  arrange(subject_id, trial) %>% 
  group_by(subject_id) %>% 
  mutate(
    prev_choice = lag(choice, 1),
    prev_reward = lag(reward, 1),
    prev_condition = lag(condition, 1) # Lag condition of the PREVIOUS trial's feedback
  ) %>% 
  filter(!is.na(prev_choice) & !is.na(prev_reward) & !is.na(prev_condition)) # Remove first trial per subject

# Calculate Win-Stay and Lose-Shift probabilities
# A "stay" means choice[t] == prev_choice[t-1]
wsls_summary_calc <- wsls_data %>% 
  mutate(stayed = (choice == prev_choice)) %>% 
  group_by(subject_id, prev_reward, prev_condition) %>% # prev_condition refers to feedback of trial t-1
  summarise(
    n_opportunities = n(),
    n_stay = sum(stayed, na.rm = TRUE),
    prob_stay = ifelse(n_opportunities > 0, n_stay / n_opportunities, NA_real_),
    .groups = "drop"
  ) %>%
  # Create more descriptive labels for plotting/tables
  mutate(
    outcome_type = case_when(
      prev_reward == "Win" & prev_condition == "Salient" ~ "Salient Win",
      prev_reward == "Win" & prev_condition == "Non-Salient" ~ "Non-Salient Win",
      prev_reward == "Loss" ~ "Loss", # Condition on loss trials might not be as relevant for win-stay
      TRUE ~ as.character(NA)
    )
  ) %>% 
  filter(!is.na(outcome_type)) # Focus on these defined outcomes

# Overall WSLS probabilities
cat("Overall Win-Stay/Lose-Shift type probabilities (prob_stay means P(Stay | Outcome on t-1)):
")
overall_wsls_table <- wsls_summary_calc %>% 
  group_by(outcome_type) %>% 
  summarise(
    mean_prob_stay = mean(prob_stay, na.rm = TRUE),
    median_prob_stay = median(prob_stay, na.rm = TRUE),
    sd_prob_stay = sd(prob_stay, na.rm = TRUE),
    n_subjects_contrib = n_distinct(subject_id)
  )
print(overall_wsls_table)

# Focus on Win-Stay for Salient vs. Non-Salient Wins
win_stay_comparison_data <- wsls_summary_calc %>% 
  filter(outcome_type %in% c("Salient Win", "Non-Salient Win")) %>% 
  select(subject_id, outcome_type, prob_stay)

if(nrow(win_stay_comparison_data) > 0 && n_distinct(win_stay_comparison_data$subject_id) > 1) {
  win_stay_plot <- ggplot(win_stay_comparison_data, aes(x = outcome_type, y = prob_stay, fill = outcome_type)) +
    geom_boxplot(alpha = 0.7, outlier.shape = NA, width = 0.5) +
    geom_point(aes(group = subject_id), position = position_jitterdodge(jitter.width = 0.1, dodge.width = 0.5), alpha = 0.3, size=1) + 
    geom_line(aes(group = subject_id), color = "grey", alpha = 0.3, position = position_jitterdodge(jitter.width = 0.1, dodge.width = 0.5)) + 
    scale_y_continuous(labels = scales::percent_format(accuracy = 1), limits = c(0,1)) +
    labs(title = "Win-Stay Probability by Feedback Condition on Previous Trial",
         subtitle = "P(Stay | Rewarded on t-1). Points are individual subjects.",
         x = "Outcome of Previous Trial (t-1)",
         y = "Probability of Staying with Previous Choice") +
    theme_minimal(base_size = 12) +
    theme(legend.position = "none", plot.title = element_text(face="bold")) +
    scale_fill_manual(values = c("Non-Salient Win" = "grey70", "Salient Win" = "gold"))
  print(win_stay_plot)
  ggsave(file.path(output_figs_dir, "win_stay_prob_by_condition.png"), plot = win_stay_plot, width = 7, height = 6)

  # Table for Win-Stay comparison
  win_stay_table_gt_summary <- win_stay_comparison_data %>% 
    group_by(outcome_type) %>% 
    summarise(
      Mean_P_WinStay = mean(prob_stay, na.rm=TRUE),
      Median_P_WinStay = median(prob_stay, na.rm=TRUE),
      SD_P_WinStay = sd(prob_stay, na.rm=TRUE),
      N_Subjects = n_distinct(subject_id)
    ) %>% 
    gt() %>% 
    fmt_number(columns = where(is.numeric), decimals = 3) %>%
    cols_label(
      outcome_type = "Previous Outcome",
      Mean_P_WinStay = "Mean P(Win-Stay)",
      Median_P_WinStay = "Median P(Win-Stay)",
      SD_P_WinStay = "SD P(Win-Stay)"
    ) %>%
    tab_header(title = "Win-Stay Probabilities by Feedback Condition")
  
  # Explicitly display the table for Rmd output
  win_stay_table_gt_summary
  
  # Save the table to an external file
  gtsave(win_stay_table_gt_summary, filename = file.path(output_tables_dir, "win_stay_prob_by_condition_summary.html"))
  
  # Add to subject_summary_data for later correlation
  win_stay_for_merge <- win_stay_comparison_data %>% 
    pivot_wider(names_from = outcome_type, values_from = prob_stay) %>% 
    janitor::clean_names() # e.g. salient_win, non_salient_win
  
  # Ensure subject_summary_data exists and has subject_id
  if(!exists("subject_summary_data")) {
    cat("Error: subject_summary_data not found for merging WSLS data.\n")
  } else if (!"subject_id" %in% names(subject_summary_data)){
    cat("Error: subject_id not found in subject_summary_data for merging WSLS data.\n")
  } else {
    subject_summary_data <- subject_summary_data %>% 
      left_join(win_stay_for_merge, by = "subject_id")
    cat("\nWin-stay probabilities merged into subject_summary_data.\n")
  }
  
} else {
  cat("\nNot enough data or distinct subjects to compare win-stay probabilities for salient vs. non-salient wins.\n")
}
```

## 8.2 Post-Reinforcement Pause (PRP) Analysis

Post-Reinforcement Pause (PRP) refers to the reaction time on trial `t+1` following different outcomes on trial `t`. We compare PRPs after Loss, Non-Salient Win, and Salient Win.

```{r prp_analysis}
# Use the rt_analysis_data which has RTs and associated trial info
# We need to lag reward and condition from trial t-1 to relate to RT on trial t
prp_data <- rt_analysis_data %>% # rt_analysis_data already filtered for valid RTs and choices
  arrange(subject_id, trial) %>% 
  group_by(subject_id) %>% 
  mutate(
    prev_reward_for_prp = lag(reward, 1),
    prev_condition_for_prp = lag(condition, 1)
  ) %>% 
  filter(!is.na(prev_reward_for_prp) & !is.na(prev_condition_for_prp)) %>% # Remove first trial per subject after lag
  mutate(
    outcome_type_prp = case_when(
      prev_reward_for_prp == "Win" & prev_condition_for_prp == "Salient" ~ "Post-Salient Win",
      prev_reward_for_prp == "Win" & prev_condition_for_prp == "Non-Salient" ~ "Post-Non-Salient Win",
      prev_reward_for_prp == "Loss" ~ "Post-Loss", # Group all losses together for PRP
      TRUE ~ as.character(NA) # Should not happen if prev_reward is 0 or 1
    )
  ) %>% 
  filter(!is.na(outcome_type_prp))

# Calculate median PRP per subject for each outcome type
subject_median_prps <- prp_data %>% 
  group_by(subject_id, outcome_type_prp) %>% 
  summarise(
    median_prp = median(reaction_time, na.rm = TRUE),
    n_trials_for_prp = n(),
    .groups = "drop"
  )

cat("\nMedian Post-Reinforcement Pauses (RT on t+1) by outcome on trial t:
")
# Overall summary of these median PRPs
overall_median_prps_summary <- subject_median_prps %>% 
  group_by(outcome_type_prp) %>% 
  summarise(
    mean_of_medians = mean(median_prp, na.rm=TRUE),
    median_of_medians = median(median_prp, na.rm=TRUE),
    sd_of_medians = sd(median_prp, na.rm=TRUE)
  )
print(overall_median_prps_summary)

if(nrow(subject_median_prps) > 0 && n_distinct(subject_median_prps$subject_id) > 1) {
  prp_plot <- ggplot(subject_median_prps, aes(x = outcome_type_prp, y = median_prp, fill = outcome_type_prp)) +
    geom_boxplot(alpha = 0.7, outlier.shape = NA, width = 0.5) +
    geom_point(aes(group=subject_id), position = position_jitterdodge(jitter.width = 0.1, dodge.width = 0.5), alpha=0.3, size=1) +
    geom_line(aes(group = subject_id), color = "grey", alpha = 0.3, position = position_jitterdodge(jitter.width = 0.1, dodge.width = 0.5)) +
    labs(title = "Post-Outcome Pauses (Median RT on Next Trial)",
         subtitle = "Each point is a subject's median RT following the specified outcome on the previous trial.",
         x = "Outcome on Previous Trial (t-1)",
         y = "Median Reaction Time on Current Trial (t) (seconds)") +
    theme_minimal(base_size = 12) +
    theme(legend.position = "none", 
          plot.title = element_text(face="bold"),
          axis.text.x = element_text(angle = 10, hjust = 0.65)) +
    scale_fill_manual(values = c("Post-Non-Salient Win" = "grey70", "Post-Salient Win" = "gold", "Post-Loss" = "salmon"))
  print(prp_plot)
  ggsave(file.path(output_figs_dir, "prp_by_outcome_type.png"), plot = prp_plot, width = 8, height = 6)

  # Table for PRP comparison
  prp_table_gt_summary <- subject_median_prps %>% 
    group_by(outcome_type_prp) %>% 
    summarise(
      Mean_Median_PRP = mean(median_prp, na.rm=TRUE),
      Median_Median_PRP = median(median_prp, na.rm=TRUE),
      SD_Median_PRP = sd(median_prp, na.rm=TRUE),
      N_Subjects = n_distinct(subject_id)
    ) %>% 
    gt() %>% 
    fmt_number(columns = where(is.numeric), decimals = 3) %>%
    cols_label(
      outcome_type_prp = "Previous Outcome",
      Mean_Median_PRP = "Mean of Median PRPs (s)",
      Median_Median_PRP = "Median of Median PRPs (s)",
      SD_Median_PRP = "SD of Median PRPs (s)"
    ) %>%
    tab_header(title = "Post-Outcome Pause Durations (Subject Medians)")
  
  # Explicitly display the table for Rmd output
  prp_table_gt_summary
  
  # Save the table to an external file
  gtsave(prp_table_gt_summary, filename = file.path(output_tables_dir, "prp_by_outcome_type_summary.html"))
  
  # Add to subject_summary_data for later correlation
  prp_for_merge <- subject_median_prps %>% 
    select(subject_id, outcome_type_prp, median_prp) %>% 
    pivot_wider(names_from = outcome_type_prp, values_from = median_prp) %>% 
    janitor::clean_names() # e.g. post_salient_win, post_loss
    
  if(!exists("subject_summary_data")) {
    cat("Error: subject_summary_data not found for merging PRP data.\n")
  } else if (!"subject_id" %in% names(subject_summary_data)){
    cat("Error: subject_id not found in subject_summary_data for merging PRP data.\n")
  } else {
    subject_summary_data <- subject_summary_data %>% 
      left_join(prp_for_merge, by = "subject_id")
    cat("\nMedian PRPs merged into subject_summary_data.\n")
  }
  
} else {
  cat("\nNot enough data or distinct subjects to calculate and display Post-Reinforcement Pauses.\n")
}

# Final check of the consolidated subject_summary_data after adding WSLS and PRP metrics
# This section should be re-run after WSLS and PRP data is potentially merged.
if(exists("subject_summary_data")){
    cat("\nFinal glimpse of consolidated subject_summary_data with WSLS and PRP metrics:\n")
    glimpse(subject_summary_data)
    cat("\nMissing values in the final subject_summary_data:\n")
    print(colSums(is.na(subject_summary_data)))
    
    # Update correlation plot with new WSLS/PRP columns if they exist
    corr_data_task_quest_final <- subject_summary_data %>% 
        select(where(is.numeric)) %>% 
        select(-any_of(c("subject_id"))) # subject_id should be character

    if(ncol(corr_data_task_quest_final) > 1) {
        corr_matrix_task_quest_final <- cor(corr_data_task_quest_final, use = "pairwise.complete.obs")
        corr_plot_task_quest_final <- ggcorrplot(corr_matrix_task_quest_final,
                                             hc.order = TRUE, type = "lower", lab = TRUE, lab_size = 2.2,
                                             method = "circle", colors = c("#6D9EC1", "white", "#E46726"),
                                             title = "Correlations: All Subject Metrics (Task, Questionnaire, WSLS, PRP)",
                                             ggtheme = theme_minimal(base_size = 9)) +
        theme(plot.title = element_text(face="bold", hjust=0.5, size=rel(1.1)),
              axis.text.x = element_text(angle = 45, hjust = 1, size=rel(0.8)), 
              axis.text.y = element_text(size=rel(0.8)))
        print(corr_plot_task_quest_final)
        ggsave(file.path(output_figs_dir, "task_metrics_questionnaire_wsls_prp_corr_matrix.png"), 
               plot = corr_plot_task_quest_final, width = 11, height = 9)
    } else {
        cat("Not enough numeric columns for final correlation plot after merging WSLS/PRP data.\n")
    }
} else {
    cat("subject_summary_data does not exist for final check.\n")
}

```

# 9. Concluding Remarks and Next Steps

This EDA has provided a comprehensive overview of the task and questionnaire data. Key findings include:
- Data loading and merging procedures are established.
- Distributions of key variables (RT, reward rates, questionnaire scores) have been examined.
- Initial checks for data quality (missed trials, trial counts, consistency) have been performed.
- Preliminary explorations of learning trends (accuracy over time, RT over time) have been made.
- Relationships between task conditions and behavioral outcomes (win-stay, PRPs) have been visualized.
- Correlations between questionnaire scores and task metrics have been initially explored.

Potential areas for further attention or that might influence modeling:
- Handling of outliers in RTs or questionnaire scores.
- Extent and impact of missed trials for certain participants.
- Distributional properties of variables when selecting statistical tests or priors for Bayesian models.

The next steps will involve formal hypothesis testing and model fitting as outlined in the analysis plan, using the insights gained from this EDA to inform those processes.

```{r save_subject_summary_data}
# Save the consolidated subject_summary_data for easy loading in other analysis scripts
if(exists("subject_summary_data")){
    subject_summary_output_dir <- here::here("analysis_scripts", "data_inspection", "derived_data")
    
    # Create directory if it doesn't exist
    if (!dir.exists(subject_summary_output_dir)) {
      dir.create(subject_summary_output_dir, recursive = TRUE)
    } # Closes if for subject_summary_output_dir

    # Define file paths using the now existing directory
    subject_summary_output_file <- file.path(subject_summary_output_dir, "subject_summary_metrics.csv")
    subject_summary_output_rds_file <- file.path(subject_summary_output_dir, "subject_summary_metrics.rds")

    # The original second directory creation logic is now handled by the above,
    # as dirname(subject_summary_output_file) would be subject_summary_output_dir.

    write_csv(subject_summary_data, subject_summary_output_file)
    saveRDS(subject_summary_data, file = subject_summary_output_rds_file)
    cat(paste("\\nConsolidated subject summary data saved to:", subject_summary_output_file, "and", subject_summary_output_rds_file, "\\n"))
} # Closes if(exists("subject_summary_data"))
```

---
End of EDA R Markdown Document
---