---
title: "Comprehensive Data Inspection"
author: "Yannik Poth"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    theme: yeti
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, fig.width = 8, fig.asp = 0.618, out.width = "80%")
# Ensure webshot2 is available for saving gt tables if needed
if (!requireNamespace("webshot2", quietly = TRUE)) {
  install.packages("webshot2")
}
```

# 1. Introduction

This document outlines the Exploratory Data Analysis (EDA) performed on the data collected for the study "Illuminating Decisions: How Salient Reward-Paired Cues Modulate Learning and Choice Behavior." The goal of this EDA is to understand the data structure, identify potential issues, examine distributions, and derive initial insights before formal statistical modeling.

# 2. Prerequisites

## 2.1 Load Necessary Packages
```{r load_packages}
# Core data manipulation and visualization
library(tidyverse)
library(dplyr) 
library(ggplot2)
library(here) 
library(fs)  

# Summary statistics and EDA reports
library(skimr)
library(DataExplorer)

# Plotting enhancements
library(patchwork)    
library(ggbeeswarm)  
library(ggpubr)       
library(ggpattern)

# Table formatting
library(gt)
library(janitor)      
library(RColorBrewer)
```

# 3. Load and Prepare Data

## 3.1 Define Data Directories
```{r define_paths}
# Define data directory path using 'here' package for robustness
base_dir <- here::here()
data_dir <- file.path(base_dir, "bandit_task", "collected_data")

# Define output directory for figures and tables generated by this Rmd
output_figs_dir <- here::here("analysis_scripts", "data_inspection", "figures_very_final")
output_tables_dir <- here::here("analysis_scripts", "data_inspection", "tables_very_final")

# Create output directories if they don't exist
if (!dir.exists(output_figs_dir)) {
  dir.create(output_figs_dir, recursive = TRUE)
}
if (!dir.exists(output_tables_dir)) {
  dir.create(output_tables_dir, recursive = TRUE)
}

cat("Base directory:", base_dir, "\n")
cat("Data directory:", data_dir, "\n")
cat("Figures output directory:", output_figs_dir, "\n")
cat("Tables output directory:", output_tables_dir, "\n")
```

## 3.2 Load Task Data
```{r load_task_data}
# List all task data files
task_files <- fs::dir_ls(data_dir, regexp = "_task_data[.]csv$")
cat("Found", length(task_files), "task data files.\n")

# Function to read and preprocess a single task file
read_task_file <- function(file_path) {
  subject_id <- sub("_task_data[.]csv$", "", basename(file_path))
  data <- read_csv(file_path, col_types = cols(
    mode = col_character(),
    trial = col_integer(),
    choice = col_double(), 
    reaction_time = col_double(),
    reward = col_double(), 
    condition = col_integer(), 
    reward_prob_1 = col_double(),
    reward_prob_2 = col_double()
  )) %>%
    mutate(
      subject_id = as.character(subject_id),
      choice = factor(choice, levels = c(0, 1), labels = c("Stimulus 1", "Stimulus 2")) %>%
        forcats::fct_explicit_na(na_level = "Missed"),
      reward = factor(reward, levels = c(0, 1), labels = c("Loss", "Win")),
      condition = factor(condition, levels = c(0, 1, 2), labels = c("Non-Salient", "Salient", "Missed"))
    ) %>%
    filter(mode == "main") %>% 
    select(subject_id, mode, trial, choice, reaction_time, reward, condition, reward_prob_1, reward_prob_2)
  
  return(data)
}

task_data <- map_dfr(task_files, read_task_file)

cat("Successfully loaded and combined task data for", length(unique(task_data$subject_id)), "subjects.\n")
cat("Total main trials loaded:", nrow(task_data), "\n")
```

## 3.3 Load Questionnaire Data
```{r load_questionnaire_data}
# List all questionnaire data files
questionnaire_files <- fs::dir_ls(data_dir, regexp = "_questionnaire_data[.]csv$")
cat("Found", length(questionnaire_files), "questionnaire data files.\n")

# Function to read and preprocess a single questionnaire file
read_questionnaire_file <- function(file_path) {
  subject_id_from_filename <- sub("_questionnaire_data[.]csv$", "", basename(file_path))

  data <- read_csv(file_path, col_types = cols(.default = col_character()), show_col_types = FALSE)
  
  data_cleaned <- data %>% janitor::clean_names()
  
  if ("participant_id" %in% names(data_cleaned)) {
    data_with_subject_id <- data_cleaned %>%
      mutate(subject_id = as.character(participant_id))
    
    if ("participant_id" %in% names(data_with_subject_id) && "participant_id" != "subject_id") {
      data_with_subject_id <- data_with_subject_id %>% select(-participant_id)
    }
  } else {
    data_with_subject_id <- data_cleaned %>%
      mutate(subject_id = as.character(subject_id_from_filename))
  }
  
  potential_ordered_factor_colnames <- c(
    grep("^bis_\\d+$", names(data_with_subject_id), value = TRUE)
  )
  cols_to_convert_to_ordered_factor <- intersect(potential_ordered_factor_colnames, names(data_with_subject_id))

  potential_numeric_colnames <- c("ss_percent", "bis_total", "sst", "sse", "ssd", "ssb", "ss_total")
  cols_to_convert_to_numeric <- intersect(potential_numeric_colnames, names(data_with_subject_id))

  potential_sss_colnames <- grep("^sss_\\d+$", names(data_with_subject_id), value = TRUE)
  cols_to_convert_to_sss_factor <- intersect(potential_sss_colnames, names(data_with_subject_id))
  
  potential_other_factor_colnames <- grep("^q_choice_", names(data_with_subject_id), value = TRUE)
  cols_to_convert_to_other_factor <- intersect(potential_other_factor_colnames, names(data_with_subject_id))

  data_typed <- data_with_subject_id

  if (length(cols_to_convert_to_ordered_factor) > 0) {
    data_typed <- data_typed %>%
      mutate(across(all_of(cols_to_convert_to_ordered_factor), ~factor(., levels = c("1", "2", "3", "4"), ordered = TRUE)))
  }
  
  if (length(cols_to_convert_to_numeric) > 0) {
    data_typed <- data_typed %>%
      mutate(across(all_of(cols_to_convert_to_numeric), as.numeric))
  }

  if (length(cols_to_convert_to_sss_factor) > 0) {
    data_typed <- data_typed %>%
      mutate(across(all_of(cols_to_convert_to_sss_factor), ~factor(., levels = c("a", "b"))))
  }
  
  if (length(cols_to_convert_to_other_factor) > 0) {
    data_typed <- data_typed %>%
      mutate(across(all_of(cols_to_convert_to_other_factor), as.factor))
  }
  
  data_final <- data_typed %>%
    mutate(subject_id = as.character(subject_id))
    
  return(data_final)
}

questionnaire_data <- map_dfr(questionnaire_files, read_questionnaire_file)

cat("Successfully loaded and combined questionnaire data for", length(unique(questionnaire_data$subject_id)), "subjects.\n")
```

# 4. General Data Overview

## 4.1 Basic Summary Statistics
```{r summary_stats_basic}
cat("Basic summary statistics for Task Data:\n")
summary(task_data)

cat("\n\nBasic summary statistics for Questionnaire Data:\n")
summary(questionnaire_data)
```

## 4.2 Distributions of Categorical Variables
```{r discrete_distributions, fig.width=12}
cat("\nPlotting distributions of discrete (factor) variables.\n")

# --- Task Data Subheading ---
task_heading <- ggplot() + 
  labs(title = "Task Data") +
  theme_void() +
  theme(plot.title = element_text(hjust = 0.5, size = 14, face = "bold"))

# --- Task Data Plots (1x3 Row) ---
# 1. Choice Plot
choice_plot <- ggplot(task_data, aes(x = choice, fill = choice)) +
  geom_bar(alpha = 0.9, color = "black") +
  scale_fill_manual(
    values = c("Stimulus 1" = "dodgerblue", "Stimulus 2" = "firebrick", "Missed" = "black"),
    name = "Choice",
    drop = FALSE
  ) +
  labs(title = "Choice", x = NULL, y = "Trial Count") +
  theme_minimal(base_size = 10) +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5))

# 2. Reward Plot
reward_plot <- ggplot(task_data, aes(x = reward, fill = reward)) +
  geom_bar(alpha = 0.9, color = "black") +
  scale_fill_manual(
    values = c("Win" = "forestgreen", "Loss" = "darkred"),
    na.value = "grey50",
    name = "Reward",
    drop = FALSE
  ) +
  labs(title = "Reward", x = NULL, y = "Trial Count") +
  theme_minimal(base_size = 10) +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5))

# 3. Condition Plot
condition_plot <- ggplot(task_data, aes(x = condition, fill = condition)) +
  geom_bar(alpha = 0.9, color = "black") +
  scale_fill_manual(
    values = c("Non-Salient" = "grey70", "Salient" = "gold", "Missed" = "black"),
    name = "Condition",
    drop = FALSE
  ) +
  labs(title = "Condition", x = NULL, y = "Trial Count") +
  theme_minimal(base_size = 10) +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5))

task_plots_row <- (choice_plot | reward_plot | condition_plot)

# --- Questionnaire Data Subheading ---
quest_heading <- ggplot() + 
  labs(title = "Questionnaire Data") +
  theme_void() +
  theme(plot.title = element_text(hjust = 0.5, size = 14, face = "bold"))

# --- Questionnaire Data Plots (4-column grid) ---
# Define negative BIS items
negative_bis_items <- c("bis_1", "bis_4", "bis_5", "bis_7", "bis_8", "bis_15")

# Define BIS palettes
positive_bis_palette <- brewer.pal(4, "YlOrRd")
names(positive_bis_palette) <- c("1", "2", "3", "4")
negative_bis_palette <- rev(positive_bis_palette)
names(negative_bis_palette) <- c("1", "2", "3", "4")

# Define SSS items and palettes
positive_sss_items <- c("sss_1", "sss_3", "sss_4", "sss_7")
# Using a Blue-Green palette for SSS items
sss_palette <- brewer.pal(4, "BuGn")[c(2, 4)] # Select a light and dark shade
# For positive items, 'a' is high (dark), 'b' is low (light)
positive_sss_palette <- setNames(c(sss_palette[2], sss_palette[1]), c("a", "b"))
# For negative items, 'b' is high (dark), 'a' is low (light)
negative_sss_palette <- setNames(c(sss_palette[1], sss_palette[2]), c("a", "b"))

# Define Evaluation Questionnaire palettes
q_palette_yesno <- setNames(c("white", "black", "white"), c("Ja", "Nein", "Unsicher"))
q_contingency_levels <- c("Gar nicht auffällig", "Kaum auffällig", "Moderat auffällig", "Sehr auffällig")
q_palette_contingency <- setNames(gray.colors(4, start = 0.0, end = 0.9), q_contingency_levels)
q_motivation_levels <- c("Wenig motiviert", "Moderat motiviert", "Sehr motiviert")
q_palette_motivation <- setNames(gray.colors(3, start = 0.2, end = 0.8), q_motivation_levels)

# Include BIS items now
quest_discrete_vars <- questionnaire_data %>% 
  select(where(is.factor)) %>%
  names()

quest_plots_list <- map(quest_discrete_vars, ~{
  current_var <- .x
  
  # --- Create plot title ---
  plot_title <- case_when(
    startsWith(current_var, "bis_") ~ paste0("BIS: Item ", sub("bis_", "", current_var)),
    startsWith(current_var, "sss_") ~ paste0("SSS: Item ", sub("sss_", "", current_var)),
    current_var == "q_choice_noticed_saliency" ~ "EVAL: Noticed Saliency",
    current_var == "q_choice_saliency_strength" ~ "EVAL: Saliency Strength",
    current_var == "q_choice_saliency_impact" ~ "EVAL: Saliency Impact",
    current_var == "q_choice_saliency_value" ~ "EVAL: Saliency Value",
    current_var == "q_choice_win_motivation" ~ "EVAL: Win Motivation",
    TRUE ~ current_var # Fallback
  )

  plot_data <- questionnaire_data
  p <- NULL # Initialize plot object

  # Special handling for motivation factor ordering
  if (current_var == "q_choice_win_motivation") {
      plot_data[[current_var]] <- factor(plot_data[[current_var]], levels = q_motivation_levels)
  }

  if (current_var == "q_choice_saliency_strength") {
      plot_data[[current_var]] <- factor(plot_data[[current_var]], levels = q_contingency_levels)
  }

  # --- Create the plot object based on variable type ---
  if (startsWith(current_var, "bis_")) {
    palette <- if (current_var %in% negative_bis_items) negative_bis_palette else positive_bis_palette
    p <- ggplot(plot_data, aes(x = .data[[current_var]], fill = .data[[current_var]])) +
      geom_bar(alpha = 0.9, show.legend = FALSE, color = "black") +
      scale_fill_manual(values = palette, drop = FALSE)

  } else if (startsWith(current_var, "sss_")) {
    palette <- if (current_var %in% positive_sss_items) positive_sss_palette else negative_sss_palette
    p <- ggplot(plot_data, aes(x = .data[[current_var]], fill = .data[[current_var]])) +
      geom_bar(alpha = 0.9, show.legend = FALSE, color = "black") +
      scale_fill_manual(values = palette, drop = FALSE)

  } else if (current_var %in% c("q_choice_noticed_saliency", "q_choice_saliency_impact", "q_choice_saliency_value")) {
    p <- ggplot(plot_data, aes(x = .data[[current_var]], fill = .data[[current_var]])) +
        ggpattern::geom_bar_pattern(
          aes(pattern = .data[[current_var]]),
          alpha = 0.9, show.legend = FALSE, color = "black",
          pattern_fill    = "black",
          pattern_angle   = 45,
          pattern_density = 0.1,
          pattern_spacing = 0.025,
          pattern_colour = NA) +
        scale_fill_manual(values = q_palette_yesno, drop = FALSE, na.translate = FALSE) +
        ggpattern::scale_pattern_manual(values = c("Ja" = "none", "Nein" = "none", "Unsicher" = "stripe"), guide = 'none')
        
  } else if (current_var == "q_choice_saliency_strength") {
    p <- ggplot(plot_data, aes(x = .data[[current_var]], fill = .data[[current_var]])) +
      geom_bar(alpha = 0.9, show.legend = FALSE, color = "black") +
      scale_fill_manual(values = q_palette_contingency, drop = FALSE, na.translate = FALSE)

  } else if (current_var == "q_choice_win_motivation") {
      p <- ggplot(plot_data, aes(x = .data[[current_var]], fill = .data[[current_var]])) +
        geom_bar(alpha = 0.9, show.legend = FALSE, color = "black") +
        scale_fill_manual(values = q_palette_motivation, drop = FALSE, na.translate = FALSE)

  } else {
    # Fallback for any other variable to default ggplot grey with a black border
    p <- ggplot(plot_data, aes(x = .data[[current_var]])) +
      geom_bar(alpha = 0.8, color = "black")
  }
  
  # --- Add common layers to the final plot object `p` ---
  p +
    labs(title = plot_title, x = NULL, y = "Subject Count") +
    theme_minimal(base_size = 10) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), plot.title = element_text(hjust = 0.5))
})

# --- Combine, Save, and Display ---
if (length(quest_plots_list) > 0) {
    quest_plots_grid <- patchwork::wrap_plots(.plots = quest_plots_list, ncol = 4)

    # Calculate number of questionnaire rows for height adjustment
    nrow_quest <- ceiling(length(quest_plots_list) / 4)

    # Use patchwork's "/" to stack the headings and plot sections vertically
    combined_discrete_plot <- task_heading / task_plots_row / quest_heading / quest_plots_grid + 
      plot_layout(heights = c(0.1, 1, 0.1, nrow_quest)) +
      plot_annotation(
        title = "Distributions of Discrete Variables",
        caption = paste0(
          "**Note on Color Coding:**\n",
          "**BIS items:** The color gradient from light yellow to dark red corresponds to increasing levels of impulsiveness for the chosen response.\n",
          "**SSS items:** The darker shade represents the choice associated with higher sensation seeking.\n",
          "**EVAL items:** The coloring reflects alignment with the experimental manipulation's intended effects. Lighter colors denote stronger agreement (e.g., noticing saliency, high motivation), \n",
          "darker colors denote disagreement, and a striped pattern indicates uncertainty."
        ),
        theme = theme(
          plot.title = element_text(face = "bold", size = 16, hjust = 0.5),
          plot.caption = element_text(hjust = 0, size = 9, lineheight = 1.2)
        )
      )

    # Dynamic height calculation to reflect the new layout
    plot_height_discrete_facet <- 3 * (1 + nrow_quest) # ~3 inches per plot row

    print(combined_discrete_plot)
    ggsave(
      file.path(output_figs_dir, "discrete_variables_distribution.png"), 
      plot = combined_discrete_plot, 
      width = 12, 
      height = plot_height_discrete_facet, 
      units = "in",
      limitsize = FALSE
    )
} else {
  # Handle case with no questionnaire factors by just showing the task plots
  combined_plot <- task_heading / task_plots_row +
      plot_annotation(
        title = "Distributions of Task-Related Discrete Variables",
        theme = theme(plot.title = element_text(face = "bold", size = 16, hjust = 0.5))
      )
  print(combined_plot)
  ggsave(
      file.path(output_figs_dir, "discrete_variables_distribution.png"), 
      plot = combined_plot, 
      width = 12, 
      height = 4, 
      units = "in"
    )
}
```

# 5. Task Data Analysis

## 5.1 Choice Behavior
```{r choice_behavior_plots}
# Overall Proportion of Choices plot
choice_plot <- ggplot(task_data %>% filter(choice != "Missed"), aes(x = choice, fill = choice)) +
  geom_bar(aes(y = (..count..)/sum(..count..)), alpha = 0.8) +
  scale_y_continuous(labels = scales::percent_format()) +
  scale_fill_manual(values = c("Stimulus 1" = "dodgerblue", "Stimulus 2" = "firebrick")) +
  labs(title = "Overall Proportion of Choices", x = "Choice", y = "Proportion") +
  theme_minimal() +
  theme(legend.position = "none", plot.title = element_text(face="bold"))
print(choice_plot)
ggsave(file.path(output_figs_dir, "choice_proportion_overall.png"), plot = choice_plot, width = 6, height = 4)
```
### 5.1.1 Choice Switching Analysis
```{r choice_switching_plots}
# Calculate switching behavior from one trial to the next
switch_data <- task_data %>%
  filter(choice != "Missed") %>%
  arrange(subject_id, trial) %>%
  group_by(subject_id) %>%
  mutate(
    prev_choice = lag(choice, 1),
    switched = choice != prev_choice
  ) %>%
  ungroup() %>%
  filter(!is.na(prev_choice)) # Remove the first trial for each subject as there's no previous choice

# Summarize switch rates per participant
switch_summary <- switch_data %>%
  group_by(subject_id) %>%
  summarise(
    switch_rate = mean(switched, na.rm = TRUE),
    n_switches = sum(switched, na.rm = TRUE),
    n_opportunities = n()
  ) %>%
  ungroup()

# Plot 1: Distribution of switch rates across participants
switch_rate_dist_plot <- ggplot(switch_summary, aes(x = switch_rate)) +
  geom_histogram(aes(y = after_stat(density)), binwidth = 0.05, fill = "mediumpurple", color = "black", alpha = 0.7, boundary = 0) +
  geom_density(alpha = 0.2, fill = "purple") +
  geom_vline(xintercept = mean(switch_summary$switch_rate), color = "darkred", linetype = "dashed", size = 1) +
  annotate("text", x = mean(switch_summary$switch_rate) + 0.01, y = Inf, 
           label = paste0("Mean: ", scales::percent(mean(switch_summary$switch_rate), accuracy = 0.1)),
           hjust = 0, vjust = 1.5, color = "darkred", size = 3.5) +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1), limits = c(0, 1)) +
  labs(
    title = "Distribution of Choice Switch Rates Across Participants",
    subtitle = paste0("N = ", nrow(switch_summary), " participants. A 'switch' is choosing a different stimulus than on the previous trial."),
    x = "Switch Rate",
    y = "Density"
  ) +
  theme_minimal(base_size = 12) +
  theme(plot.title = element_text(face = "bold"), plot.subtitle = element_text(color = "grey30"))

print(switch_rate_dist_plot)
ggsave(file.path(output_figs_dir, "switch_rate_distribution.png"), plot = switch_rate_dist_plot, width = 7, height = 5)

# Plot 2: Switch rate over trial bins to observe changes over time
switch_data_binned <- switch_data %>%
  mutate(trial_bin = cut_number(trial, n = 10, labels = FALSE))

switch_rate_over_bins_summary <- switch_data_binned %>%
  group_by(trial_bin) %>%
  summarise(
    mean_switch_rate_bin = mean(switched, na.rm = TRUE),
    sem_switch_rate_bin = sd(switched, na.rm = TRUE) / sqrt(n()),
    .groups = 'drop'
  )

switch_learning_plot <- ggplot(switch_rate_over_bins_summary, aes(x = trial_bin, y = mean_switch_rate_bin)) +
  geom_line(color = "purple4", size = 1) +
  geom_point(color = "purple4", size = 2.5) +
  geom_errorbar(aes(ymin = mean_switch_rate_bin - sem_switch_rate_bin, ymax = mean_switch_rate_bin + sem_switch_rate_bin), width = 0.2, color = "purple4", alpha = 0.5) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  labs(title = "Mean Switch Rate Over Trial Bins",
       x = "Trial Bin (10 bins of ~20 trials)", y = "Mean Switch Rate +/- SEM") +
  scale_x_continuous(breaks = 1:10) +
  theme_minimal(base_size = 12) +
  theme(plot.title = element_text(face="bold"))

print(switch_learning_plot)
ggsave(file.path(output_figs_dir, "switch_rate_over_trial_bins.png"), plot = switch_learning_plot, width = 7, height = 5)
```

## 5.2 Reaction Time Analysis

### 5.2.1 Summary Table
```{r rt_summary_table}
# Calculate summary statistics per participant
rt_analysis_data <- task_data %>%
  filter(choice != "Missed" & !is.na(reaction_time))
fast_rt_threshold <- 0.150

rt_summary_per_subject <- rt_analysis_data %>% 
  group_by(subject_id) %>% 
  summarise(
    n_trials = n(),
    mean_rt = mean(reaction_time, na.rm = TRUE),
    median_rt = median(reaction_time, na.rm = TRUE),
    min_rt = min(reaction_time, na.rm = TRUE),
    max_rt = max(reaction_time, na.rm = TRUE),
    n_fast_rt = sum(reaction_time < fast_rt_threshold, na.rm = TRUE),
    percent_fast_rt = (n_fast_rt / n_trials) * 100
  ) %>% 
  ungroup() %>%
  arrange(desc(percent_fast_rt))

# Display as a basic printout to match original script
print(rt_summary_per_subject)
```

### 5.2.2 Plots
```{r reaction_time_plots}
# Filter out trials not suitable for RT analysis
rt_analysis_data <- task_data %>%
  filter(choice != "Missed" & !is.na(reaction_time))
fast_rt_threshold <- 0.150

# Overall Distribution of reaction times (Valid Trials) plot
rt_overall_dist_plot <- ggplot(rt_analysis_data, aes(x = reaction_time)) +
  geom_histogram(aes(y = after_stat(density)), binwidth = 0.05, fill = "cornflowerblue", color = "black", alpha = 0.7, boundary = 0) +
  geom_density(alpha = 0.2, fill = "lightblue") +
  geom_vline(xintercept = fast_rt_threshold, color = "red", linetype = "dashed", size = 1) +
  annotate("text", x = fast_rt_threshold + 0.05, y = Inf, label = paste0("Fast RT threshold (", fast_rt_threshold * 1000, "ms)"), 
           hjust = 0, vjust = 1.5, color = "red", size = 3.5) +
  scale_x_continuous(limits = c(0, NA), expand = expansion(mult = c(0.01, 0.05))) +
  labs(title = "Overall Distribution of Reaction Times (Valid Trials)",
       subtitle = paste0("N = ", nrow(rt_analysis_data), " trials. Red line at ", fast_rt_threshold * 1000, "ms."),
       x = "Reaction Time (seconds)", y = "Density") +
  theme_minimal(base_size = 12) +
  theme(plot.title = element_text(face = "bold"), plot.subtitle = element_text(color = "grey30"))
print(rt_overall_dist_plot)
ggsave(file.path(output_figs_dir, "rt_overall_distribution.png"), plot = rt_overall_dist_plot, width = 7, height = 5)

# Median Reaction Time Over Trial Bins plot
rt_analysis_data_binned <- rt_analysis_data %>%
  mutate(trial_bin = cut_number(trial, n = 10, labels = FALSE))

rt_over_bins_summary <- rt_analysis_data_binned %>%
  group_by(trial_bin) %>%
  summarise(
    mean_rt_bin = mean(reaction_time, na.rm = TRUE),
    median_rt_bin = median(reaction_time, na.rm = TRUE),
    sem_rt_bin = sd(reaction_time, na.rm = TRUE) / sqrt(n()),
    .groups = 'drop'
  )

rt_learning_plot <- ggplot(rt_over_bins_summary, aes(x = trial_bin, y = median_rt_bin)) +
  geom_line(color = "blue", size = 1) +
  geom_point(color = "blue", size = 2) +
  geom_errorbar(aes(ymin = median_rt_bin - sem_rt_bin, ymax = median_rt_bin + sem_rt_bin), width = 0.2, color = "blue", alpha = 0.5) +
  labs(title = "Median Reaction Time Over Trial Bins",
       x = "Trial Bin (10 bins of 20 trials)", y = "Median Reaction Time (s) +/- SEM") +
  scale_x_continuous(breaks = 1:10) +
  theme_minimal(base_size = 12)+
  theme(plot.title = element_text(face="bold"))
print(rt_learning_plot)
ggsave(file.path(output_figs_dir, "rt_over_trial_bins.png"), plot = rt_learning_plot, width = 7, height = 5)

# Reaction Time by Feedback Condition plot
rt_condition_plot_data <- rt_analysis_data %>%
  filter(condition %in% c("Salient", "Non-Salient"))

rt_condition_boxplot <- ggplot(rt_condition_plot_data, aes(x = condition, y = reaction_time, fill = condition)) +
  geom_boxplot(alpha = 0.7, outlier.shape = NA) +
  geom_jitter(width = 0.1, alpha = 0.05, size=0.5) +
  scale_y_continuous(limits = c(quantile(rt_condition_plot_data$reaction_time, 0.01), quantile(rt_condition_plot_data$reaction_time, 0.99))) +
  labs(title = "Reaction Time by Feedback Condition",
       subtitle = "Excluding missed trials. Boxes show median & IQR. Y-axis trimmed to 1st-99th percentile.",
       x = "Feedback Condition", y = "Reaction Time (s)") +
  theme_minimal(base_size = 12) +
  theme(legend.position = "none", plot.title = element_text(face="bold")) +
  scale_fill_manual(values = c("Non-Salient" = "grey70", "Salient" = "gold"))
print(rt_condition_boxplot)
ggsave(file.path(output_figs_dir, "rt_by_condition_boxplot.png"), plot = rt_condition_boxplot, width = 6, height = 5)
```

### 5.2.3 Individual Reaction Time Distributions
```{r rt_subject_histograms, fig.width=12, fig.height=15}
# Calculate summary stats for annotation, including highlight flag
rt_summary_annot <- rt_analysis_data %>% 
  group_by(subject_id) %>% 
  summarise(
    n_trials = n(),
    n_fast_rt = sum(reaction_time < fast_rt_threshold, na.rm = TRUE),
    percent_fast_rt = (n_fast_rt / n_trials) * 100,
    .groups = 'drop' 
  ) %>% 
  mutate(
    label_text = paste0(round(percent_fast_rt, 1), "%"),
    highlight_flag = percent_fast_rt > 5
  )

# Join highlight flag back to the main data
rt_data_highlighted <- rt_analysis_data %>% 
  left_join(rt_summary_annot %>% select(subject_id, highlight_flag), by = "subject_id")

# Calculate number of subjects for layout adjustments
n_subjects <- length(unique(rt_data_highlighted$subject_id))
ncol <- 4 

# Plot histogram of reaction times faceted by subject
rt_histogram_subject <- ggplot(rt_data_highlighted, aes(x = reaction_time)) +
  geom_histogram(aes(y = after_stat(density), fill = highlight_flag),
                 binwidth = 0.1,
                 boundary = 0,
                 color = "black", 
                 alpha = 0.7) +
  scale_fill_manual(values = c("TRUE" = "firebrick", "FALSE" = "grey80"), guide = "none") + 
  geom_vline(xintercept = fast_rt_threshold, linetype = "dashed", color = "darkred", size = 0.6) +      
  geom_text(data = rt_summary_annot,
            aes(x = Inf, y = Inf, label = label_text),
            hjust = 1.1, vjust = 1.5, size = 5, alpha = 0.7, fontface = "bold", color = "black") +
  facet_wrap(~ subject_id, scales = "free_y", ncol = ncol) + 
  scale_x_continuous(limits = c(0, max(rt_data_highlighted$reaction_time, na.rm = TRUE) * 1.05),
                     expand = c(0.01, 0.01)) + 
  scale_y_continuous(expand = expansion(mult = c(0.01, 0.15))) + 
  labs(
    title = "Individual Reaction Time Distributions",
    subtitle = "Dashed line: 150ms threshold. Highlighted: >5% trials < 150ms.",
    x = "Reaction Time (s)", y = "Density"
  ) +
  theme_bw(base_size = 10) + 
  theme(
    plot.title = element_text(face = "bold", size=rel(1.2)), 
    plot.subtitle = element_text(color = "grey30"),
    strip.background = element_blank(), 
    strip.text = element_text(face = "bold") 
  )

# Calculate dynamic height and save
nrow <- ceiling(n_subjects / ncol)
plot_height <- max(7, 3 * nrow) 
ggsave(
  filename = file.path(output_figs_dir, "rt_histogram_subject_level.png"), 
  plot = rt_histogram_subject,
  width = 12, height = plot_height, units = "in", dpi = 300
)

print(rt_histogram_subject)
```

## 5.3 Reward, Feedback, and Learning
```{r reward_feedback_plots}
reward_analysis_data <- task_data %>% filter(choice != "Missed")

# Overall Reward Rate by Chosen Stimulus plot
reward_rate_by_choice <- reward_analysis_data %>%
  group_by(choice) %>%
  summarise(
    n_rewards = sum(reward == "Win", na.rm = TRUE),
    n_trials_for_choice = n(),
    reward_rate = n_rewards / n_trials_for_choice,
    .groups = 'drop'
  ) %>%
  mutate(choice_label = factor(choice, levels = c("Stimulus 1", "Stimulus 2")))

reward_rate_by_choice_plot <- ggplot(reward_rate_by_choice, aes(x = choice, y = reward_rate, fill = choice)) +
    geom_bar(stat = "identity", alpha = 0.8) +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
    scale_fill_manual(values = c("Stimulus 1" = "dodgerblue", "Stimulus 2" = "firebrick")) +
    labs(title = "Overall Reward Rate by Chosen Stimulus", x = "Stimulus Choice", y = "Reward Rate") +
    theme_minimal(base_size = 12) +
    theme(legend.position = "none", plot.title = element_text(face="bold"))
print(reward_rate_by_choice_plot)
ggsave(file.path(output_figs_dir, "reward_rate_by_choice.png"), plot = reward_rate_by_choice_plot, width = 6, height = 5)

# Mean Reward Rate Over Trial Bins plot
reward_analysis_data_binned <- reward_analysis_data %>%
  mutate(trial_bin = cut_number(trial, n = 10, labels = FALSE))

reward_over_bins_summary <- reward_analysis_data_binned %>%
  group_by(trial_bin) %>%
  summarise(
    mean_reward_rate_bin = mean(reward == "Win", na.rm = TRUE),
    sem_reward_rate_bin = sd(reward == "Win", na.rm = TRUE) / sqrt(n()),
    .groups = 'drop'
  )

reward_learning_plot <- ggplot(reward_over_bins_summary, aes(x = trial_bin, y = mean_reward_rate_bin)) +
  geom_line(color = "darkgreen", size = 1) +
  geom_point(color = "darkgreen", size = 2) +
  geom_errorbar(aes(ymin = mean_reward_rate_bin - sem_reward_rate_bin, 
                    ymax = mean_reward_rate_bin + sem_reward_rate_bin), 
                width = 0.2, color = "darkgreen", alpha = 0.5) +
  scale_y_continuous(labels = scales::percent_format(accuracy=1), limits = c(0, NA)) +
  labs(title = "Mean Reward Rate Over Trial Bins",
       x = "Trial Bin (10 bins of 20 trials)", y = "Mean Reward Rate +/- SEM") +
  scale_x_continuous(breaks = 1:10) +
  theme_minimal(base_size = 12)+
  theme(plot.title = element_text(face="bold"))
print(reward_learning_plot)
ggsave(file.path(output_figs_dir, "reward_rate_over_trial_bins.png"), plot = reward_learning_plot, width = 7, height = 5)

# Proportion of Feedback Conditions plot
condition_plot <- ggplot(task_data %>% filter(choice != "Missed"), aes(x = condition, fill = condition)) +
  geom_bar(aes(y = (..count..)/sum(..count..)), alpha = 0.8) +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(title = "Proportion of Feedback Conditions (Valid Trials)",
       x = "Feedback Condition", y = "Proportion") +
  theme_minimal(base_size = 12) +
  theme(legend.position = "none", plot.title = element_text(face="bold")) +
  scale_fill_manual(values = c("Non-Salient" = "grey70", "Salient" = "gold", "Missed" = "grey85"))
print(condition_plot)
ggsave(file.path(output_figs_dir, "condition_proportion_valid_trials.png"), plot = condition_plot, width = 6, height = 4)

# Proportion of Feedback Conditions by Subject plot
condition_per_subject_summary <- task_data %>%
  filter(choice != "Missed") %>%
  group_by(subject_id, condition) %>%
  summarise(n = n(), .groups = 'drop') %>%
  group_by(subject_id) %>%
  mutate(prop = n / sum(n))

condition_subject_plot <- ggplot(condition_per_subject_summary, aes(x = subject_id, y = prop, fill = condition)) +
  geom_bar(stat = "identity", position = "stack") +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(title = "Proportion of Feedback Conditions by Subject (Valid Trials)",
       x = "Subject ID", y = "Proportion of Trials", fill = "Condition") +
  theme_minimal(base_size = 10) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5),
        plot.title = element_text(face="bold")) +
  scale_fill_manual(values = c("Non-Salient" = "grey70", "Salient" = "gold", "Missed" = "grey85"))
print(condition_subject_plot)
ggsave(file.path(output_figs_dir, "condition_proportion_per_subject.png"), plot = condition_subject_plot, width = 10, height = 6)
```

## 5.4 Accuracy Analysis
```{r accuracy_calculation}
# Calculate accuracy based on choosing the option with the higher reward probability.
accuracy_data <- task_data %>% 
  filter(choice != "Missed" & !is.na(reward_prob_1) & !is.na(reward_prob_2)) %>%
  # Optionally filter by RT if needed, e.g., reaction_time >= 0.150
  mutate(
    chose_better_option = case_when(
      reward_prob_1 > reward_prob_2 ~ ifelse(choice == "Stimulus 1", 1, 0),
      reward_prob_2 > reward_prob_1 ~ ifelse(choice == "Stimulus 2", 1, 0),
      reward_prob_1 == reward_prob_2 ~ 0.5, # Or handle as per study protocol
      TRUE ~ NA_real_
    )
  ) %>%
  filter(!is.na(chose_better_option))

# Calculate mean accuracy per participant
accuracy_summary <- accuracy_data %>%
  group_by(subject_id) %>%
  summarise(
    mean_accuracy = mean(chose_better_option, na.rm = TRUE),
    n_valid_trials = n(),
    .groups = 'drop'
  )
```

```{r accuracy_plots}
# --- Perform one-sample t-test against chance level (0.5) ---
n_subjects_accuracy <- nrow(accuracy_summary) 
if (n_subjects_accuracy >= 2) {
  t_test_result <- t.test(accuracy_summary$mean_accuracy, mu = 0.5)
  # Format p-value for caption
  p_value_formatted <- scales::pvalue(t_test_result$p.value, accuracy = .001, add_p = TRUE)
  t_test_caption <- paste0("One-sample t-test vs 0.5: t(", 
                           round(t_test_result$parameter, 1), ") = ",
                           round(t_test_result$statistic, 2), ", ",
                           p_value_formatted)
} else {
  t_test_result <- NULL # Set to NULL if t-test cannot be performed
  t_test_caption <- "Not enough data for t-test (N < 2)"
}

# --- Visualize Accuracy Boxplot ---
overall_mean_accuracy <- mean(accuracy_summary$mean_accuracy, na.rm = TRUE)
significance_y_start <- 0.5
significance_y_end <- overall_mean_accuracy
significance_x <- 1.3 
annotation_y <- (significance_y_start + significance_y_end) / 2

# Boxplot of overall accuracy
accuracy_boxplot <- ggplot(accuracy_summary, aes(x = factor(1), y = mean_accuracy)) +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "grey50") +
  geom_jitter(width = 0.2, height = 0, size = 1.5, alpha = 0.5) +
  geom_boxplot(width = 0.35, outlier.shape = NA, fill = "grey80", alpha = 0.6) +
  stat_summary(fun = mean, geom = "point", shape = 18, size = 3, color = "firebrick") +
    # Add significance annotation (only if t-test was performed and significant)
  {if (!is.null(t_test_result) && t_test_result$p.value < 0.05)
    list(
      # Vertical line of the bracket
      geom_segment(aes(x = significance_x, xend = significance_x, y = significance_y_start, yend = significance_y_end),
                   color = "black", size = 0.5),
      # Top horizontal line of the bracket
      geom_segment(aes(x = significance_x - 0.02, xend = significance_x, y = significance_y_end, yend = significance_y_end),
                   color = "black", size = 0.5),
      # Bottom horizontal line of the bracket
      geom_segment(aes(x = significance_x - 0.02, xend = significance_x, y = significance_y_start, yend = significance_y_start),
                   color = "black", size = 0.5),
      # P-value text annotation
      annotate("text", x = significance_x + 0.05, y = annotation_y, 
               label = p_value_formatted, 
               hjust = 0, size = 3.5)
    )
  } +
  labs(title = "Overall Accuracy Distribution", y = "Accuracy", x = NULL, caption = if(exists("t_test_caption")) t_test_caption else NULL) +
  scale_y_continuous(limits = c(min(0.3, min(accuracy_summary$mean_accuracy)*0.9), 
                                 max(0.75, max(accuracy_summary$mean_accuracy)*1.05)),
                     breaks = seq(0.3, 0.8, by = 0.1)) +
  scale_x_discrete(expand = expansion(add = c(0.6, 0.6))) +
  theme_classic(base_size = 12) +
  theme(plot.title = element_text(face = "bold", hjust = 0.5), axis.text.x = element_blank(), axis.ticks.x = element_blank())
print(accuracy_boxplot)
ggsave(file.path(output_figs_dir, "accuracy_boxplot.png"), plot = accuracy_boxplot, width = 5, height = 5)

# Learning Curve (Accuracy over time)
accuracy_data_binned <- accuracy_data %>%
  mutate(trial_bin = ceiling(trial / (max(trial) / 20)))

learning_curve_summary <- accuracy_data_binned %>%
  group_by(trial_bin) %>%
  summarise(
    mean_accuracy_across_subjects = mean(chose_better_option, na.rm = TRUE),
    sem_accuracy = sd(chose_better_option, na.rm = TRUE) / sqrt(n()),
    .groups = 'drop'
  )

learning_curve_plot <- ggplot(learning_curve_summary, aes(x = trial_bin, y = mean_accuracy_across_subjects)) +
  geom_ribbon(aes(ymin = mean_accuracy_across_subjects - sem_accuracy, ymax = mean_accuracy_across_subjects + sem_accuracy), fill = "dodgerblue", alpha = 0.2) +
  geom_line(color = "dodgerblue", size = 1) +
  geom_point(color = "dodgerblue", size = 2.5) +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "grey30") +
  labs(title = "Learning Curve: Accuracy Over Trial Bins", x = "Trial Bin", y = "Mean Accuracy", caption = "Shaded area represents SEM.") +
  theme_bw(base_size = 14) +
  theme(plot.title = element_text(face = "bold", hjust = 0.5))
print(learning_curve_plot)
ggsave(file.path(output_figs_dir, "learning_curve_accuracy.png"), plot = learning_curve_plot, width = 7, height = 5)
```

### 5.4.1 Individual Participant Accuracy
```{r individual_accuracy_plots, fig.width=7}
# --- Prepare Data ---
# accuracy_summary is already calculated.
# Add below_chance flag
accuracy_summary_sorted <- accuracy_summary %>%
  mutate(below_chance = mean_accuracy < 0.5) %>%
  arrange(mean_accuracy)

# --- Visualize Individual Accuracies (Sorted by Accuracy) ---
individual_accuracy_plot <- ggplot(accuracy_summary_sorted, 
                                   aes(x = mean_accuracy, 
                                       y = reorder(subject_id, mean_accuracy), 
                                       color = below_chance)) +
  geom_point(size = 2.5, alpha = 0.8) +
  geom_vline(xintercept = 0.5, linetype = "dashed", color = "red", size = 0.7) +
  geom_text(aes(label = sprintf("%.3f", mean_accuracy),
                hjust = ifelse(mean_accuracy < 0.5, 1.3, -0.3)),
            vjust = 0.5, size = 2.5, check_overlap = TRUE) +
  scale_color_manual(values = c("TRUE" = "firebrick", "FALSE" = "black"), name = "Below Chance (0.5)") +
  labs(title = "Individual Participant Accuracy (Sorted by Accuracy)",
       subtitle = paste0("Each point represents a participant (N=", n_subjects_accuracy, ")."),
       x = "Mean Accuracy", y = "Participant ID") +
  theme_bw(base_size = 11) +
  theme(plot.title = element_text(face = "bold", hjust = 0.5), legend.position = "top", plot.subtitle = element_text(hjust = 0.5, color="grey30"))

print(individual_accuracy_plot)
ggsave(file.path(output_figs_dir, "individual_accuracy_dotplot.png"),
       plot = individual_accuracy_plot, width = 7, height = max(4, 0.25 * n_subjects_accuracy), limitsize = FALSE)

# --- Visualize Individual Accuracies (Sorted by Participant ID) ---
individual_accuracy_by_id_plot <- ggplot(accuracy_summary_sorted,
                                   aes(x = mean_accuracy,
                                       y = factor(subject_id, levels = rev(sort(unique(subject_id)))),
                                       color = below_chance)) +
  geom_point(size = 2.5, alpha = 0.8) +
  geom_vline(xintercept = 0.5, linetype = "dashed", color = "red", size = 0.7) +
  geom_text(aes(label = sprintf("%.3f", mean_accuracy),
                hjust = ifelse(mean_accuracy < 0.5, 1.3, -0.3)),
            vjust = 0.5, size = 2.5, check_overlap = TRUE) +
  scale_color_manual(values = c("TRUE" = "firebrick", "FALSE" = "black"), name = "Below Chance (0.5)") +
  labs(title = "Individual Participant Accuracy (Sorted by ID)",
       subtitle = paste0("Each point represents a participant (N=", n_subjects_accuracy, ")."),
       x = "Mean Accuracy", y = "Participant ID") +
  theme_bw(base_size = 11) +
  theme(plot.title = element_text(face = "bold", hjust = 0.5), legend.position = "top", plot.subtitle = element_text(hjust = 0.5, color="grey30"))

print(individual_accuracy_by_id_plot)
ggsave(file.path(output_figs_dir, "individual_accuracy_by_id_dotplot.png"),
       plot = individual_accuracy_by_id_plot, width = 7, height = max(4, 0.25 * n_subjects_accuracy), limitsize = FALSE)
```

## 5.5 Choice Strategies
```{r choice_strategies_plots}
# Win-Stay Probability by Feedback Condition plot
wsls_data <- task_data %>%
  filter(choice != "Missed" & !is.na(reward)) %>%
  arrange(subject_id, trial) %>% 
  group_by(subject_id) %>% 
  mutate(
    prev_choice = lag(choice, 1),
    prev_reward = lag(reward, 1),
    prev_condition = lag(condition, 1)
  ) %>% 
  filter(!is.na(prev_choice) & !is.na(prev_reward) & !is.na(prev_condition))

wsls_summary_calc <- wsls_data %>% 
  mutate(stayed = (choice == prev_choice)) %>% 
  group_by(subject_id, prev_reward, prev_condition) %>%
  summarise(
    n_opportunities = n(),
    n_stay = sum(stayed, na.rm = TRUE),
    prob_stay = ifelse(n_opportunities > 0, n_stay / n_opportunities, NA_real_),
    .groups = "drop"
  ) %>% 
  mutate(
    outcome_type = case_when(
      prev_reward == "Win" & prev_condition == "Salient" ~ "Salient Win",
      prev_reward == "Win" & prev_condition == "Non-Salient" ~ "Non-Salient Win",
      prev_reward == "Loss" ~ "Loss",
      TRUE ~ as.character(NA)
    )
  ) %>% 
  filter(!is.na(outcome_type))

win_stay_comparison_data <- wsls_summary_calc %>% 
  filter(outcome_type %in% c("Salient Win", "Non-Salient Win")) %>% 
  select(subject_id, outcome_type, prob_stay)

if(nrow(win_stay_comparison_data) > 0 && n_distinct(win_stay_comparison_data$subject_id) > 1) {
  win_stay_plot <- ggplot(win_stay_comparison_data, aes(x = outcome_type, y = prob_stay, fill = outcome_type)) +
    geom_boxplot(alpha = 0.7, outlier.shape = NA, width = 0.5) +
    geom_point(aes(group = subject_id), position = position_jitterdodge(jitter.width = 0.1, dodge.width = 0.5), alpha = 0.3, size=1) + 
    geom_line(aes(group = subject_id), color = "grey", alpha = 0.3, position = position_jitterdodge(jitter.width = 0.1, dodge.width = 0.5)) + 
    scale_y_continuous(labels = scales::percent_format(accuracy = 1), limits = c(0,1)) +
    labs(title = "Win-Stay Probability by Feedback Condition on Previous Trial",
         subtitle = "P(Stay | Rewarded on t-1). Points are individual subjects.",
         x = "Outcome of Previous Trial (t-1)", y = "Probability of Staying with Previous Choice") +
    theme_minimal(base_size = 12) +
    theme(legend.position = "none", plot.title = element_text(face="bold")) +
    scale_fill_manual(values = c("Non-Salient Win" = "grey70", "Salient Win" = "gold"))
  print(win_stay_plot)
  ggsave(file.path(output_figs_dir, "win_stay_prob_by_condition.png"), plot = win_stay_plot, width = 7, height = 6)
}

# Post-Outcome Pauses (PRP) plot
prp_data <- rt_analysis_data %>%
  arrange(subject_id, trial) %>% 
  group_by(subject_id) %>% 
  mutate(
    prev_reward_for_prp = lag(reward, 1),
    prev_condition_for_prp = lag(condition, 1)
  ) %>% 
  filter(!is.na(prev_reward_for_prp) & !is.na(prev_condition_for_prp)) %>%
  mutate(
    outcome_type_prp = case_when(
      prev_reward_for_prp == "Win" & prev_condition_for_prp == "Salient" ~ "Post-Salient Win",
      prev_reward_for_prp == "Win" & prev_condition_for_prp == "Non-Salient" ~ "Post-Non-Salient Win",
      prev_reward_for_prp == "Loss" ~ "Post-Loss",
      TRUE ~ as.character(NA)
    )
  ) %>% 
  filter(!is.na(outcome_type_prp))

subject_median_prps <- prp_data %>% 
  group_by(subject_id, outcome_type_prp) %>% 
  summarise(
    median_prp = median(reaction_time, na.rm = TRUE),
    .groups = "drop"
  )

if(nrow(subject_median_prps) > 0 && n_distinct(subject_median_prps$subject_id) > 1) {
  prp_plot <- ggplot(subject_median_prps, aes(x = outcome_type_prp, y = median_prp, fill = outcome_type_prp)) +
    geom_boxplot(alpha = 0.7, outlier.shape = NA, width = 0.5) +
    geom_point(aes(group=subject_id), position = position_jitterdodge(jitter.width = 0.1, dodge.width = 0.5), alpha=0.3, size=1) +
    geom_line(aes(group = subject_id), color = "grey", alpha = 0.3, position = position_jitterdodge(jitter.width = 0.1, dodge.width = 0.5)) +
    labs(title = "Post-Outcome Pauses (Median RT on Next Trial)",
         subtitle = "Each point is a subject's median RT following the specified outcome on the previous trial.",
         x = "Outcome on Previous Trial (t-1)", y = "Median Reaction Time on Current Trial (t) (seconds)") +
    theme_minimal(base_size = 12) +
    theme(legend.position = "none", plot.title = element_text(face="bold"), axis.text.x = element_text(angle = 10, hjust = 0.65)) +
    scale_fill_manual(values = c("Post-Non-Salient Win" = "grey70", "Post-Salient Win" = "gold", "Post-Loss" = "salmon"))
  print(prp_plot)
  ggsave(file.path(output_figs_dir, "prp_by_outcome_type.png"), plot = prp_plot, width = 8, height = 6)
}
```

## 5.6 Reward Probability Visualization
```{r reward_prob_plots, fig.width=8, fig.height=6}
# Get unique subject IDs
unique_subjects <- unique(task_data$subject_id)

# Loop through each subject to create and save plots with separate panels
for (subj_id in unique_subjects) {
  # Filter data for the current subject
  subject_data <- task_data %>% filter(subject_id == subj_id)

  # Adapt to factor variables
  salient_feedback_A <- subject_data %>% filter(condition == "Salient" & choice == "Stimulus 1")
  salient_feedback_B <- subject_data %>% filter(condition == "Salient" & choice == "Stimulus 2")

  # Plot for Option A (Stimulus 1)
  plot_A <- ggplot(subject_data, aes(x = trial, y = reward_prob_1)) +
    geom_line(color = "dodgerblue", size = 0.8) +
    geom_vline(data = salient_feedback_A, aes(xintercept = trial), 
               color = "grey40", linetype = "dashed", size = 0.5, alpha = 0.6) +
    geom_point(data = salient_feedback_A, aes(x = trial, y = reward_prob_1), 
               shape = 21, color = "black", fill = "#ffc400", size = 3, stroke = 0.5) +
    scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.25)) +
    labs(y = "p(Reward | A)", x = NULL) +
    theme_bw(base_size = 10) +
    theme(axis.text.x = element_blank(), axis.ticks.x = element_blank())

  # Plot for Option B (Stimulus 2)
  plot_B <- ggplot(subject_data, aes(x = trial, y = reward_prob_2)) +
    geom_line(color = "firebrick", size = 0.8) +
    geom_vline(data = salient_feedback_B, aes(xintercept = trial), 
               color = "grey40", linetype = "dashed", size = 0.5, alpha = 0.6) +
    geom_point(data = salient_feedback_B, aes(x = trial, y = reward_prob_2), 
               shape = 21, color = "black", fill = "#ffc400", size = 3, stroke = 0.5) +
    scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.25)) +
    labs(y = "p(Reward | B)", x = "Trial") +
    theme_bw(base_size = 10)

  # Combine plots using patchwork
  combined_plot <- plot_A / plot_B + 
    plot_annotation(title = paste("Subject", subj_id, ": Reward Probabilities & Salient Feedback"),
                    theme = theme(plot.title = element_text(face = "bold", hjust = 0.5)))

  # Save the combined plot
  ggsave(
    filename = file.path(output_figs_dir, paste0("reward_probs_sep_subject_", subj_id, ".png")),
    plot = combined_plot, width = 8, height = 6, units = "in", dpi = 300
  )
}
combined_plot
```

```{r combined_reward_prob_plots, fig.width=8, fig.height=4}
# Loop through each subject to create and save combined plots
for (subj_id in unique_subjects) {
  # Filter data for the current subject
  subject_data <- task_data %>% filter(subject_id == subj_id)

  # Adapt to factor variables
  salient_feedback_A <- subject_data %>% filter(condition == "Salient" & choice == "Stimulus 1")
  salient_feedback_B <- subject_data %>% filter(condition == "Salient" & choice == "Stimulus 2")
  
  # Combine salient feedback trials for vlines
  vline_data <- subject_data %>% filter(condition == "Salient") %>% distinct(trial)

  # Create the combined plot
  combined_plot_single <- ggplot(subject_data, aes(x = trial)) +
    geom_line(aes(y = reward_prob_1, color = "A"), size = 0.8) +
    geom_line(aes(y = reward_prob_2, color = "B"), size = 0.8) +
    geom_vline(data = vline_data, aes(xintercept = trial), 
               color = "grey40", linetype = "dashed", size = 0.5, alpha = 0.6) +
    geom_point(data = salient_feedback_A, aes(y = reward_prob_1), 
               shape = 21, color = "black", fill = "#ffc400", size = 3, stroke = 0.5) +
    geom_point(data = salient_feedback_B, aes(y = reward_prob_2), 
               shape = 21, color = "black", fill = "#ffc400", size = 3, stroke = 0.5) +
    scale_color_manual(values = c("A" = "dodgerblue", "B" = "firebrick"), 
                       labels = c("A" = "p(Reward | A)", "B" = "p(Reward | B)")) +
    scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.25)) +
    labs(
      title = paste("Subject", subj_id, ": Combined Reward Probabilities & Salient Feedback"),
      y = "p(Reward)", x = "Trial"
    ) +
    theme_bw(base_size = 10) +
    theme(
      plot.title = element_text(face = "bold", hjust = 0.5),
      legend.position = c(0.98, 0.98),
      legend.justification = c("right", "top"),
      legend.title = element_blank(),
      legend.background = element_rect(color = "black", fill = rgb(1, 1, 1, alpha = 0.8), linetype = "solid", linewidth=0.5)
    )

  # Save the combined plot
  ggsave(
    filename = file.path(output_figs_dir, paste0("reward_probs_comb_subject_", subj_id, ".png")),
    plot = combined_plot_single, width = 8, height = 4, units = "in", dpi = 300
  )
}
combined_plot_single
```

## 5.7 Participant Behavioral Summary
```{r participant_summary_table, results='asis'}
# Get unique subject IDs from the loaded data
unique_subject_ids <- sort(unique(task_data$subject_id))

# Initialize a list to store stats for each participant
all_participant_stats <- list()

# Loop through each subject ID
for (current_subject_id in unique_subject_ids) {
  
  p_data <- task_data %>% 
    filter(subject_id == current_subject_id) %>%
    arrange(trial)

  # Use only valid trials (not missed)
  p_data_valid <- p_data %>% 
    filter(choice != "Missed" & !is.na(reward)) %>%
    # Temporarily convert factors to numeric for calculation
    mutate(
      choice_num = as.numeric(choice) - 1, # Stimulus 1 -> 0, Stimulus 2 -> 1
      reward_num = ifelse(reward == "Win", 1, 0)
    )
  
  prop_stim1 <- NA_real_
  prop_stim2 <- NA_real_
  overall_reward_rate_p <- NA_real_
  win_stay_prob_p <- NA_real_
  current_accuracy <- NA_real_

  if (nrow(p_data_valid) > 0) {
    prop_stim1 <- sum(p_data_valid$choice_num == 0) / nrow(p_data_valid)
    prop_stim2 <- 1 - prop_stim1
    overall_reward_rate_p <- sum(p_data_valid$reward_num == 1) / nrow(p_data_valid)
    
    # Calculate Win-Stay probability
    win_stay_count_p <- 0
    opportunities_to_win_stay_p <- 0
    if (nrow(p_data_valid) > 1) {
      for (i in 1:(nrow(p_data_valid) - 1)) {
        if (p_data_valid$reward_num[i] == 1) {
          opportunities_to_win_stay_p <- opportunities_to_win_stay_p + 1
          if (p_data_valid$choice_num[i+1] == p_data_valid$choice_num[i]) {
            win_stay_count_p <- win_stay_count_p + 1
          }
        }
      }
    }
    if (opportunities_to_win_stay_p > 0) {
      win_stay_prob_p <- win_stay_count_p / opportunities_to_win_stay_p
    }
    
    # Fetch pre-calculated accuracy for this participant from accuracy_summary
    if (exists("accuracy_summary") && current_subject_id %in% accuracy_summary$subject_id) {
      current_accuracy <- accuracy_summary$mean_accuracy[accuracy_summary$subject_id == current_subject_id]
    }
    
    # Create and save individual diagnostic plot
    p_plot_df <- p_data_valid %>%
      mutate(
        plot_choice = choice,
        plot_reward = reward
      )

    p_behavior_plot <- ggplot(p_plot_df, aes(x = trial)) +
      geom_point(aes(y = as.numeric(plot_choice)-1, color = "Choice"), size = 2, show.legend = FALSE) +
      geom_point(aes(y = as.numeric(plot_choice)-1 + ifelse(plot_reward == "Win", 0.2, -0.2), shape = plot_reward), size = 3) +
      scale_shape_manual(values = c("Loss" = 4, "Win" = 16), name = "Reward") +
      scale_y_continuous(breaks = c(0, 1), labels = c("Stimulus 1", "Stimulus 2"), limits = c(-0.5, 1.5)) +
      labs(title = paste("Participant", current_subject_id, "- Choices and Rewards Over Valid Trials"),
           x = "Trial Number (Valid)", y = "Choice") +
      theme_minimal(base_size = 10) +
      theme(plot.title = element_text(size=rel(0.9)))
    
    plot_filename <- file.path(output_figs_dir, paste0("participant_", current_subject_id, "_choice_reward_plot.png"))
    ggsave(filename = plot_filename, plot = p_behavior_plot, width = 10, height = 4, bg = "white", dpi = 150)
  }
  
  all_participant_stats[[current_subject_id]] <- c(
    `Prop. Stim 1` = prop_stim1,
    `Prop. Stim 2` = prop_stim2,
    `Rew. Rate` = overall_reward_rate_p,
    `Accuracy` = current_accuracy,
    `WS Prob` = win_stay_prob_p
  )
}

# --- Create Summary Table --- 
if (length(all_participant_stats) > 0) {
  summary_df <- as.data.frame(do.call(cbind, all_participant_stats))
  summary_df <- tibble::rownames_to_column(summary_df, var = "Metric")
  
  summary_table_gt <- summary_df %>% 
    gt(rowname_col = "Metric") %>% 
    tab_header(
      title = "Participant Behavioral Summary",
      subtitle = "Key metrics from task data. Accuracy based on choosing higher reward probability option."
    ) %>%
    fmt_number(columns = everything(), decimals = 2, use_seps = FALSE) %>% 
    data_color(
      columns = where(is.numeric),
      rows = `Metric` == "Prop. Stim 1",
      colors = scales::col_quantile(
        palette = "RdBu", 
        domain = c(0.2, 0.8),
        n = 25 
      )
    ) %>% 
    data_color(
      columns = where(is.numeric),
      rows = `Metric` == "Prop. Stim 2",
      colors = scales::col_quantile(
        palette = "RdBu", 
        domain = c(0.2, 0.8),
        n = 25,
        reverse = TRUE
      )
    ) %>%
    data_color(
      columns = where(is.numeric),
      rows = `Metric` == "Rew. Rate",
      colors = scales::col_numeric(
        palette = "Greens",
        domain = c(min(summary_df[summary_df$Metric == "Rew. Rate", -1], na.rm=TRUE), 
                   max(summary_df[summary_df$Metric == "Rew. Rate", -1], na.rm=TRUE)),
        na.color = "#FFFFFF00"
      )
    ) %>% 
    data_color(
      columns = where(is.numeric),
      rows = `Metric` == "Accuracy",
      colors = scales::col_numeric(
        palette = "Blues",
        domain = c(min(summary_df[summary_df$Metric == "Accuracy", -1], na.rm=TRUE), 
                   max(summary_df[summary_df$Metric == "Accuracy", -1], na.rm=TRUE)), 
        na.color = "#FFFFFF00"
      )
    ) %>% 
    data_color(
      columns = where(is.numeric),
      rows = `Metric` == "WS Prob",
      colors = scales::col_numeric(
        palette = "Purples",
        domain = c(min(summary_df[summary_df$Metric == "WS Prob", -1], na.rm=TRUE), 
                   max(summary_df[summary_df$Metric == "WS Prob", -1], na.rm=TRUE)),
        na.color = "#FFFFFF00"
      )
    ) %>%
    tab_options(
      table.width = pct(100), 
      column_labels.font.weight = "bold",
      data_row.padding = px(5)
      ) %>%
    tab_source_note(
      source_note = md("**Note**: `Prop. Stim 1/2` refers to the proportion of trials Stimulus 1 or 2 was chosen. `WS Prob` is Win-Stay probability.")
    )
    
  print(summary_table_gt)
  
  # Save the table
  gtsave(summary_table_gt, filename = file.path(output_tables_dir, "participant_behavioral_summary_table.html"))
  gtsave(summary_table_gt, filename = file.path(output_tables_dir, "participant_behavioral_summary_table.png"), vwidth=1200, vheight=800)
}
```

# 6. Questionnaire Data Analysis

## 6.1 Score Distributions
```{r questionnaire_score_distributions, results='asis'}
key_score_cols <- c("bis_total", "ss_total")
present_score_cols <- key_score_cols[key_score_cols %in% names(questionnaire_data)]

if(length(present_score_cols) > 0) {
  questionnaire_scores_long <- questionnaire_data %>% 
    select(subject_id, all_of(present_score_cols)) %>%
    pivot_longer(cols = all_of(present_score_cols), names_to = "scale_name", values_to = "score") %>% 
    filter(!is.na(score))
  
  score_dist_plots <- ggplot(questionnaire_scores_long, aes(x = score)) +
    geom_histogram(aes(y = after_stat(density)), binwidth = function(x) 2 * IQR(x, na.rm=TRUE) / (length(x)^(1/3)), 
                   fill = "skyblue", color = "black", alpha = 0.7) +
    geom_density(alpha = 0.2, fill = "lightblue") +
    facet_wrap(~ scale_name, scales = "free") +
    labs(title = "Distribution of Key Questionnaire Scores", x = "Score", y = "Density") +
    theme_minimal(base_size = 10) +
    theme(plot.title = element_text(face="bold", size=rel(1.2)), strip.text = element_text(face="bold"))
  
  print(score_dist_plots)
  ggsave(file.path(output_figs_dir, "questionnaire_score_distributions.png"), plot = score_dist_plots, width = 10, height = 5)
  
  score_boxplots_filtered <- questionnaire_scores_long %>%
    filter(scale_name %in% c("bis_total", "ss_total")) %>%
    ggplot(aes(x = scale_name, y = score, fill = scale_name)) +
    geom_boxplot(alpha = 0.7, outlier.colour = "red") +
    labs(title = "Boxplots of BIS and SSS Total Scores", y = "Score", x=NULL) +
    theme_minimal(base_size = 10) +
    theme(plot.title = element_text(face="bold", size=rel(1.2)), legend.position="none")
  
  print(score_boxplots_filtered)
  ggsave(file.path(output_figs_dir, "questionnaire_score_boxplots_filtered.png"), plot = score_boxplots_filtered, width = 6, height = 5)

} else {
  cat("\nNo key questionnaire score columns found.\n")
}
```

## 6.2 Score Relationships
```{r questionnaire_score_relationships}
# Relationship between BIS Total and SSS Total Scores plot 
if ("bis_total" %in% names(questionnaire_data) && "ss_total" %in% names(questionnaire_data)) {
  bis_ss_scatter <- ggplot(questionnaire_data, aes(x = bis_total, y = ss_total)) +
    geom_point(alpha = 0.6, color = "purple") +
    geom_smooth(method = "lm", color = "black", se = FALSE, linetype="dashed") +
    labs(title = "Relationship between BIS Total and SSS Total Scores",
         x = "BIS Total Score", y = "SSS Total Score") +
    theme_minimal(base_size = 12)+
    theme(plot.title = element_text(face="bold"))
  print(bis_ss_scatter)
  ggsave(file.path(output_figs_dir, "bis_total_vs_ss_total_scatter.png"), plot = bis_ss_scatter, width = 7, height = 6)
} else {
  cat("\nbis_total or ss_total not found, skipping their specific scatter plot.\n")
}
```

# 7. Concluding Remarks

This EDA has provided a comprehensive overview of the task and questionnaire data. Key findings include:
- Data loading and preparation procedures are established.
- Distributions of key variables (RT, reward rates, questionnaire scores) have been examined.
- Behavioral patterns related to choice, learning, and feedback conditions have been visualized.

The next steps will involve formal hypothesis testing and model fitting as outlined in the analysis plan, using the insights gained from this EDA to inform those processes.

---
End of EDA R Markdown Document
---
