---
title: "Final Data Inspection"
author: "Yannik Poth"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    theme: yeti
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, fig.width = 8, fig.asp = 0.618, out.width = "80%")
# Ensure webshot2 is available for saving gt tables if needed
# if (!requireNamespace("webshot2", quietly = TRUE)) {
#   install.packages("webshot2")
# }
```

# 1. Introduction

This document outlines the Exploratory Data Analysis (EDA) performed on the data collected for the study "Illuminating Decisions: How Salient Reward-Paired Cues Modulate Learning and Choice Behavior." The goal of this EDA is to understand the data structure, identify potential issues, examine distributions, and derive initial insights before formal statistical modeling.

# 2. Prerequisites

## 2.1 Load Necessary Packages
```{r load_packages}
# Core data manipulation and visualization
library(tidyverse)
library(dplyr) # Explicitly load dplyr for clarity, though part of tidyverse
library(ggplot2)
library(here) # For robust file path management
library(fs)   # For file system operations

# Summary statistics and EDA reports
library(skimr)
library(DataExplorer) # For automated EDA reports

# Plotting enhancements
library(patchwork)    # For combining ggplot objects
library(ggbeeswarm)   # For better point distributions in plots
library(ggpubr)       # For arranging plots and adding stats

# Table formatting
library(gt)
library(janitor)      # For cleaning data and table names
```

# 3. Load and Prepare Data

## 3.1 Define Data Directories
```{r define_paths}
# Define data directory path using 'here' package for robustness
base_dir <- here::here()
data_dir <- file.path(base_dir, "bandit_task", "collected_data")

# Define output directory for figures and tables generated by this Rmd
output_figs_dir <- here::here("analysis_scripts", "data_inspection", "figures_final")
output_tables_dir <- here::here("analysis_scripts", "data_inspection", "tables_final")

# Create output directories if they don't exist
if (!dir.exists(output_figs_dir)) {
  dir.create(output_figs_dir, recursive = TRUE)
}
if (!dir.exists(output_tables_dir)) {
  dir.create(output_tables_dir, recursive = TRUE)
}

cat("Base directory:", base_dir, "\n")
cat("Data directory:", data_dir, "\n")
cat("Figures output directory:", output_figs_dir, "\n")
cat("Tables output directory:", output_tables_dir, "\n")
```

## 3.2 Load Task Data
```{r load_task_data}
# List all task data files
task_files <- fs::dir_ls(data_dir, regexp = "_task_data[.]csv$")
cat("Found", length(task_files), "task data files.\n")

# Function to read and preprocess a single task file
read_task_file <- function(file_path) {
  subject_id <- sub("_task_data[.]csv$", "", basename(file_path))
  data <- read_csv(file_path, col_types = cols(
    mode = col_character(),
    trial = col_integer(),
    choice = col_double(), # Read as double initially to handle potential non-integer inputs
    reaction_time = col_double(),
    reward = col_double(), # Read as double
    condition = col_integer(), # 0=non-salient, 1=salient, 2=missed
    reward_prob_1 = col_double(),
    reward_prob_2 = col_double()
  )) %>%
    mutate(
      subject_id = as.character(subject_id),
      # Convert choice to factor (Stimulus 1, Stimulus 2), with an explicit level for "Missed"
      choice = factor(choice, levels = c(0, 1), labels = c("Stimulus 1", "Stimulus 2")) %>%
        forcats::fct_explicit_na(na_level = "Missed"),
      # Reward: convert to factor for more descriptive summaries
      reward = factor(reward, levels = c(0, 1), labels = c("Loss", "Win")),
      # Condition: convert to factor for easier interpretation in plots/summaries
      condition = factor(condition, levels = c(0, 1, 2), labels = c("Non-Salient", "Salient", "Missed"))
    ) %>%
    filter(mode == "main") %>% # Keep only main trials
    select(subject_id, mode, trial, choice, reaction_time, reward, condition, reward_prob_1, reward_prob_2)
  
  return(data)
}

# Read and combine all task data files
task_data <- map_dfr(task_files, read_task_file)

cat("Successfully loaded and combined task data for", length(unique(task_data$subject_id)), "subjects.\n")
cat("Total main trials loaded:", nrow(task_data), "\n")
```

## 3.3 Load Questionnaire Data
```{r load_questionnaire_data}
# List all questionnaire data files
questionnaire_files <- fs::dir_ls(data_dir, regexp = "_questionnaire_data[.]csv$")
cat("Found", length(questionnaire_files), "questionnaire data files.\n")

# Function to read and preprocess a single questionnaire file
read_questionnaire_file <- function(file_path) {
  subject_id_from_filename <- sub("_questionnaire_data[.]csv$", "", basename(file_path))

  data <- read_csv(file_path, col_types = cols(.default = col_character()), show_col_types = FALSE)
  
  data_cleaned <- data %>% janitor::clean_names()
  
  if ("participant_id" %in% names(data_cleaned)) {
    data_with_subject_id <- data_cleaned %>%
      mutate(subject_id = as.character(participant_id))
    
    if ("participant_id" %in% names(data_with_subject_id) && "participant_id" != "subject_id") {
      data_with_subject_id <- data_with_subject_id %>% select(-participant_id)
    }
  } else {
    data_with_subject_id <- data_cleaned %>%
      mutate(subject_id = as.character(subject_id_from_filename))
  }
  
  potential_ordered_factor_colnames <- c(
    grep("^bis_\\d+$", names(data_with_subject_id), value = TRUE)
  )
  cols_to_convert_to_ordered_factor <- intersect(potential_ordered_factor_colnames, names(data_with_subject_id))

  potential_numeric_colnames <- c("ss_percent", "bis_total", "sst", "sse", "ssd", "ssb", "ss_total")
  cols_to_convert_to_numeric <- intersect(potential_numeric_colnames, names(data_with_subject_id))

  potential_sss_colnames <- grep("^sss_\\d+$", names(data_with_subject_id), value = TRUE)
  cols_to_convert_to_sss_factor <- intersect(potential_sss_colnames, names(data_with_subject_id))
  
  potential_other_factor_colnames <- grep("^q_choice_", names(data_with_subject_id), value = TRUE)
  cols_to_convert_to_other_factor <- intersect(potential_other_factor_colnames, names(data_with_subject_id))

  data_typed <- data_with_subject_id

  if (length(cols_to_convert_to_ordered_factor) > 0) {
    data_typed <- data_typed %>%
      mutate(across(all_of(cols_to_convert_to_ordered_factor), ~factor(., levels = c("1", "2", "3", "4"), ordered = TRUE)))
  }
  
  if (length(cols_to_convert_to_numeric) > 0) {
    data_typed <- data_typed %>%
      mutate(across(all_of(cols_to_convert_to_numeric), as.numeric))
  }

  if (length(cols_to_convert_to_sss_factor) > 0) {
    data_typed <- data_typed %>%
      mutate(across(all_of(cols_to_convert_to_sss_factor), ~factor(., levels = c("a", "b"))))
  }
  
  if (length(cols_to_convert_to_other_factor) > 0) {
    data_typed <- data_typed %>%
      mutate(across(all_of(cols_to_convert_to_other_factor), as.factor))
  }
  
  data_final <- data_typed %>%
    mutate(subject_id = as.character(subject_id))
    
  return(data_final)
}

questionnaire_data <- map_dfr(questionnaire_files, read_questionnaire_file)

cat("Successfully loaded and combined questionnaire data for", length(unique(questionnaire_data$subject_id)), "subjects.\n")
```

# 4. Exploratory Data Analysis: General Overview

## 4.1 Basic Summary Statistics
```{r summary_stats_basic}
cat("Basic summary statistics for Task Data:\n")
summary(task_data)

cat("\n\nBasic summary statistics for Questionnaire Data:\n")
summary(questionnaire_data)
```

## 4.2 Distributions of Categorical Variables
```{r discrete_distributions}
cat("\nPlotting distributions of discrete (factor) variables.\n")

# --- Task Data Discrete Variables ---
task_discrete_vars <- task_data %>% 
  select(where(is.factor)) %>%
  names()

task_plots_list <- map(task_discrete_vars, ~{
  ggplot(task_data, aes(x = .data[[.x]])) +
    geom_bar(fill = "steelblue", alpha = 0.8) +
    labs(title = .x, x = NULL, y = "Trial Count") +
    theme_minimal(base_size = 10)
})

# --- Questionnaire Data Discrete Variables ---
# Select factor variables, excluding ordered factors with many levels if desired
quest_discrete_vars <- questionnaire_data %>% 
  select(where(is.factor), -starts_with("bis_")) %>%
  names()

quest_plots_list <- map(quest_discrete_vars, ~{
  n_levels <- nlevels(questionnaire_data[[.x]])
  x_axis_theme <- if (n_levels > 5) theme(axis.text.x = element_text(angle = 45, hjust = 1)) else theme()
  
  ggplot(questionnaire_data, aes(x = .data[[.x]])) +
    geom_bar(fill = "purple", alpha = 0.8) +
    labs(title = .x, x = NULL, y = "Subject Count") +
    theme_minimal(base_size = 10) +
    x_axis_theme
})

# --- Combine and Print Plots ---
all_discrete_plots <- c(task_plots_list, quest_plots_list)

if (length(all_discrete_plots) > 0) {
  ncol_discrete_facet <- 4
  nrow_discrete_facet <- ceiling(length(all_discrete_plots) / ncol_discrete_facet)
  plot_height_discrete_facet <- max(5, 3 * nrow_discrete_facet)
  
  combined_discrete_plot <- patchwork::wrap_plots(.plots = all_discrete_plots, ncol = ncol_discrete_facet) + 
    plot_annotation(title = "Distributions of Discrete Variables", 
                    subtitle = "Blue plots from Task Data (trial counts), Purple plots from Questionnaire Data (subject counts)",
                    theme = theme(plot.title = element_text(face = "bold", size = 16, hjust = 0.5)))
  
  print(combined_discrete_plot)
  ggsave(file.path(output_figs_dir, "discrete_variables_distribution.png"), 
         plot = combined_discrete_plot, width = 12, height = plot_height_discrete_facet, units = "in")
} else {
  cat("No discrete (factor) variables to plot.\n")
}
```

# 5. Exploratory Data Analysis: Task Data

## 5.1 Choice Behavior
```{r choice_behavior_plots}
# Overall Proportion of Choices plot
choice_plot <- ggplot(task_data %>% filter(choice != "Missed"), aes(x = choice, fill = choice)) +
  geom_bar(aes(y = (..count..)/sum(..count..)), alpha = 0.8) +
  scale_y_continuous(labels = scales::percent_format()) +
  scale_fill_manual(values = c("Stimulus 1" = "dodgerblue", "Stimulus 2" = "firebrick")) +
  labs(title = "Overall Proportion of Choices",
       x = "Choice",
       y = "Proportion") +
  theme_minimal() +
  theme(legend.position = "none", plot.title = element_text(face="bold"))
print(choice_plot)
ggsave(file.path(output_figs_dir, "choice_proportion_overall.png"), plot = choice_plot, width = 6, height = 4)
```

## 5.2 Reaction Time
```{r reaction_time_plots}
# Filter out trials not suitable for RT analysis
rt_analysis_data <- task_data %>%
  filter(choice != "Missed" & !is.na(reaction_time))
fast_rt_threshold <- 0.150

# Overall Distribution of reaction times (Valid Trials) plot
rt_overall_dist_plot <- ggplot(rt_analysis_data, aes(x = reaction_time)) +
  geom_histogram(aes(y = after_stat(density)), binwidth = 0.05, fill = "cornflowerblue", color = "black", alpha = 0.7, boundary = 0) +
  geom_density(alpha = 0.2, fill = "lightblue") +
  geom_vline(xintercept = fast_rt_threshold, color = "red", linetype = "dashed", size = 1) +
  annotate("text", x = fast_rt_threshold + 0.05, y = Inf, label = paste0("Fast RT threshold (", fast_rt_threshold * 1000, "ms)"), 
           hjust = 0, vjust = 1.5, color = "red", size = 3.5) +
  scale_x_continuous(limits = c(0, NA), expand = expansion(mult = c(0.01, 0.05))) +
  labs(title = "Overall Distribution of Reaction Times (Valid Trials)",
       subtitle = paste0("N = ", nrow(rt_analysis_data), " trials. Red line at ", fast_rt_threshold * 1000, "ms."),
       x = "Reaction Time (seconds)",
       y = "Density") +
  theme_minimal(base_size = 12) +
  theme(plot.title = element_text(face = "bold"),
        plot.subtitle = element_text(color = "grey30"))
print(rt_overall_dist_plot)
ggsave(file.path(output_figs_dir, "rt_overall_distribution.png"), plot = rt_overall_dist_plot, width = 7, height = 5)

# Median Reaction Time Over Trial Bins plot
rt_analysis_data_binned <- rt_analysis_data %>%
  mutate(trial_bin = cut_number(trial, n = 10, labels = FALSE))

rt_over_bins_summary <- rt_analysis_data_binned %>%
  group_by(trial_bin) %>%
  summarise(
    mean_rt_bin = mean(reaction_time, na.rm = TRUE),
    median_rt_bin = median(reaction_time, na.rm = TRUE),
    sem_rt_bin = sd(reaction_time, na.rm = TRUE) / sqrt(n()),
    .groups = 'drop'
  )

rt_learning_plot <- ggplot(rt_over_bins_summary, aes(x = trial_bin, y = median_rt_bin)) +
  geom_line(color = "blue", size = 1) +
  geom_point(color = "blue", size = 2) +
  geom_errorbar(aes(ymin = median_rt_bin - sem_rt_bin, ymax = median_rt_bin + sem_rt_bin), width = 0.2, color = "blue", alpha = 0.5) +
  labs(title = "Median Reaction Time Over Trial Bins",
       x = "Trial Bin (10 bins of 20 trials)",
       y = "Median Reaction Time (s) +/- SEM") +
  scale_x_continuous(breaks = 1:10) +
  theme_minimal(base_size = 12)+
  theme(plot.title = element_text(face="bold"))
print(rt_learning_plot)
ggsave(file.path(output_figs_dir, "rt_over_trial_bins.png"), plot = rt_learning_plot, width = 7, height = 5)

# Reaction Time by Feedback Condition plot
rt_condition_plot_data <- rt_analysis_data %>%
  filter(condition %in% c("Salient", "Non-Salient"))

rt_condition_boxplot <- ggplot(rt_condition_plot_data, aes(x = condition, y = reaction_time, fill = condition)) +
  geom_boxplot(alpha = 0.7, outlier.shape = NA) +
  geom_jitter(width = 0.1, alpha = 0.05, size=0.5) +
  scale_y_continuous(limits = c(quantile(rt_condition_plot_data$reaction_time, 0.01), quantile(rt_condition_plot_data$reaction_time, 0.99))) +
  labs(title = "Reaction Time by Feedback Condition",
       subtitle = "Excluding missed trials. Boxes show median & IQR. Y-axis trimmed to 1st-99th percentile.",
       x = "Feedback Condition",
       y = "Reaction Time (s)") +
  theme_minimal(base_size = 12) +
  theme(legend.position = "none", plot.title = element_text(face="bold")) +
  scale_fill_manual(values = c("Non-Salient" = "grey70", "Salient" = "gold"))
print(rt_condition_boxplot)
ggsave(file.path(output_figs_dir, "rt_by_condition_boxplot.png"), plot = rt_condition_boxplot, width = 6, height = 5)
```

## 5.3 Reward and Feedback
```{r reward_feedback_plots}
reward_analysis_data <- task_data %>% filter(choice != "Missed")

# Overall Reward Rate by Chosen Stimulus plot
reward_rate_by_choice <- reward_analysis_data %>%
  group_by(choice) %>%
  summarise(
    n_rewards = sum(reward == "Win", na.rm = TRUE),
    n_trials_for_choice = n(),
    reward_rate = n_rewards / n_trials_for_choice,
    .groups = 'drop'
  ) %>%
  mutate(choice_label = factor(choice, levels = c("Stimulus 1", "Stimulus 2")))

reward_rate_by_choice_plot <- ggplot(reward_rate_by_choice, aes(x = choice, y = reward_rate, fill = choice)) +
    geom_bar(stat = "identity", alpha = 0.8) +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
    scale_fill_manual(values = c("Stimulus 1" = "dodgerblue", "Stimulus 2" = "firebrick")) +
    labs(title = "Overall Reward Rate by Chosen Stimulus",
         x = "Stimulus Choice",
         y = "Reward Rate") +
    theme_minimal(base_size = 12) +
    theme(legend.position = "none", plot.title = element_text(face="bold"))
print(reward_rate_by_choice_plot)
ggsave(file.path(output_figs_dir, "reward_rate_by_choice.png"), plot = reward_rate_by_choice_plot, width = 6, height = 5)

# Mean Reward Rate Over Trial Bins plot
reward_analysis_data_binned <- reward_analysis_data %>%
  mutate(trial_bin = cut_number(trial, n = 10, labels = FALSE))

reward_over_bins_summary <- reward_analysis_data_binned %>%
  group_by(trial_bin) %>%
  summarise(
    mean_reward_rate_bin = mean(reward == "Win", na.rm = TRUE),
    sem_reward_rate_bin = sd(reward == "Win", na.rm = TRUE) / sqrt(n()),
    .groups = 'drop'
  )

reward_learning_plot <- ggplot(reward_over_bins_summary, aes(x = trial_bin, y = mean_reward_rate_bin)) +
  geom_line(color = "darkgreen", size = 1) +
  geom_point(color = "darkgreen", size = 2) +
  geom_errorbar(aes(ymin = mean_reward_rate_bin - sem_reward_rate_bin, 
                    ymax = mean_reward_rate_bin + sem_reward_rate_bin), 
                width = 0.2, color = "darkgreen", alpha = 0.5) +
  scale_y_continuous(labels = scales::percent_format(accuracy=1), limits = c(0, NA)) +
  labs(title = "Mean Reward Rate Over Trial Bins",
       x = "Trial Bin (10 bins of 20 trials)",
       y = "Mean Reward Rate +/- SEM") +
  scale_x_continuous(breaks = 1:10) +
  theme_minimal(base_size = 12)+
  theme(plot.title = element_text(face="bold"))
print(reward_learning_plot)
ggsave(file.path(output_figs_dir, "reward_rate_over_trial_bins.png"), plot = reward_learning_plot, width = 7, height = 5)

# Proportion of Feedback Conditions plot
condition_plot <- ggplot(task_data %>% filter(choice != "Missed"), aes(x = condition, fill = condition)) +
  geom_bar(aes(y = (..count..)/sum(..count..)), alpha = 0.8) +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(title = "Proportion of Feedback Conditions (Valid Trials)",
       x = "Feedback Condition",
       y = "Proportion") +
  theme_minimal(base_size = 12) +
  theme(legend.position = "none", plot.title = element_text(face="bold")) +
  scale_fill_manual(values = c("Non-Salient" = "grey70", "Salient" = "gold", "Missed" = "grey85"))
print(condition_plot)
ggsave(file.path(output_figs_dir, "condition_proportion_valid_trials.png"), plot = condition_plot, width = 6, height = 4)

# Proportion of Feedback Conditions by Subject plot
condition_per_subject_summary <- task_data %>%
  filter(choice != "Missed") %>%
  group_by(subject_id, condition) %>%
  summarise(n = n(), .groups = 'drop') %>%
  group_by(subject_id) %>%
  mutate(prop = n / sum(n))

condition_subject_plot <- ggplot(condition_per_subject_summary, aes(x = subject_id, y = prop, fill = condition)) +
  geom_bar(stat = "identity", position = "stack") +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(title = "Proportion of Feedback Conditions by Subject (Valid Trials)",
       x = "Subject ID",
       y = "Proportion of Trials",
       fill = "Condition") +
  theme_minimal(base_size = 10) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5),
        plot.title = element_text(face="bold")) +
  scale_fill_manual(values = c("Non-Salient" = "grey70", "Salient" = "gold", "Missed" = "grey85"))
print(condition_subject_plot)
ggsave(file.path(output_figs_dir, "condition_proportion_per_subject.png"), plot = condition_subject_plot, width = 10, height = 6)
```

## 5.4 Choice Strategies
```{r choice_strategies_plots}
# Win-Stay Probability by Feedback Condition plot
wsls_data <- task_data %>%
  filter(choice != "Missed" & !is.na(reward)) %>%
  arrange(subject_id, trial) %>% 
  group_by(subject_id) %>% 
  mutate(
    prev_choice = lag(choice, 1),
    prev_reward = lag(reward, 1),
    prev_condition = lag(condition, 1)
  ) %>% 
  filter(!is.na(prev_choice) & !is.na(prev_reward) & !is.na(prev_condition))

wsls_summary_calc <- wsls_data %>% 
  mutate(stayed = (choice == prev_choice)) %>% 
  group_by(subject_id, prev_reward, prev_condition) %>%
  summarise(
    n_opportunities = n(),
    n_stay = sum(stayed, na.rm = TRUE),
    prob_stay = ifelse(n_opportunities > 0, n_stay / n_opportunities, NA_real_),
    .groups = "drop"
  ) %>% 
  mutate(
    outcome_type = case_when(
      prev_reward == "Win" & prev_condition == "Salient" ~ "Salient Win",
      prev_reward == "Win" & prev_condition == "Non-Salient" ~ "Non-Salient Win",
      prev_reward == "Loss" ~ "Loss",
      TRUE ~ as.character(NA)
    )
  ) %>% 
  filter(!is.na(outcome_type))

win_stay_comparison_data <- wsls_summary_calc %>% 
  filter(outcome_type %in% c("Salient Win", "Non-Salient Win")) %>% 
  select(subject_id, outcome_type, prob_stay)

if(nrow(win_stay_comparison_data) > 0 && n_distinct(win_stay_comparison_data$subject_id) > 1) {
  win_stay_plot <- ggplot(win_stay_comparison_data, aes(x = outcome_type, y = prob_stay, fill = outcome_type)) +
    geom_boxplot(alpha = 0.7, outlier.shape = NA, width = 0.5) +
    geom_point(aes(group = subject_id), position = position_jitterdodge(jitter.width = 0.1, dodge.width = 0.5), alpha = 0.3, size=1) + 
    geom_line(aes(group = subject_id), color = "grey", alpha = 0.3, position = position_jitterdodge(jitter.width = 0.1, dodge.width = 0.5)) + 
    scale_y_continuous(labels = scales::percent_format(accuracy = 1), limits = c(0,1)) +
    labs(title = "Win-Stay Probability by Feedback Condition on Previous Trial",
         subtitle = "P(Stay | Rewarded on t-1). Points are individual subjects.",
         x = "Outcome of Previous Trial (t-1)",
         y = "Probability of Staying with Previous Choice") +
    theme_minimal(base_size = 12) +
    theme(legend.position = "none", plot.title = element_text(face="bold")) +
    scale_fill_manual(values = c("Non-Salient Win" = "grey70", "Salient Win" = "gold"))
  print(win_stay_plot)
  ggsave(file.path(output_figs_dir, "win_stay_prob_by_condition.png"), plot = win_stay_plot, width = 7, height = 6)
}

# Post-Outcome Pauses (PRP) plot
prp_data <- rt_analysis_data %>%
  arrange(subject_id, trial) %>% 
  group_by(subject_id) %>% 
  mutate(
    prev_reward_for_prp = lag(reward, 1),
    prev_condition_for_prp = lag(condition, 1)
  ) %>% 
  filter(!is.na(prev_reward_for_prp) & !is.na(prev_condition_for_prp)) %>%
  mutate(
    outcome_type_prp = case_when(
      prev_reward_for_prp == "Win" & prev_condition_for_prp == "Salient" ~ "Post-Salient Win",
      prev_reward_for_prp == "Win" & prev_condition_for_prp == "Non-Salient" ~ "Post-Non-Salient Win",
      prev_reward_for_prp == "Loss" ~ "Post-Loss",
      TRUE ~ as.character(NA)
    )
  ) %>% 
  filter(!is.na(outcome_type_prp))

subject_median_prps <- prp_data %>% 
  group_by(subject_id, outcome_type_prp) %>% 
  summarise(
    median_prp = median(reaction_time, na.rm = TRUE),
    n_trials_for_prp = n(),
    .groups = "drop"
  )

if(nrow(subject_median_prps) > 0 && n_distinct(subject_median_prps$subject_id) > 1) {
  prp_plot <- ggplot(subject_median_prps, aes(x = outcome_type_prp, y = median_prp, fill = outcome_type_prp)) +
    geom_boxplot(alpha = 0.7, outlier.shape = NA, width = 0.5) +
    geom_point(aes(group=subject_id), position = position_jitterdodge(jitter.width = 0.1, dodge.width = 0.5), alpha=0.3, size=1) +
    geom_line(aes(group = subject_id), color = "grey", alpha = 0.3, position = position_jitterdodge(jitter.width = 0.1, dodge.width = 0.5)) +
    labs(title = "Post-Outcome Pauses (Median RT on Next Trial)",
         subtitle = "Each point is a subject's median RT following the specified outcome on the previous trial.",
         x = "Outcome on Previous Trial (t-1)",
         y = "Median Reaction Time on Current Trial (t) (seconds)") +
    theme_minimal(base_size = 12) +
    theme(legend.position = "none", 
          plot.title = element_text(face="bold"),
          axis.text.x = element_text(angle = 10, hjust = 0.65)) +
    scale_fill_manual(values = c("Post-Non-Salient Win" = "grey70", "Post-Salient Win" = "gold", "Post-Loss" = "salmon"))
  print(prp_plot)
  ggsave(file.path(output_figs_dir, "prp_by_outcome_type.png"), plot = prp_plot, width = 8, height = 6)
}
```

# 6. Exploratory Data Analysis: Questionnaire Data

## 6.1 Score Distributions
```{r questionnaire_score_distributions, fig.width=10, fig.asp=0.7}
key_score_cols <- c("bis_total", "ss_total", "sst", "sse", "ssd", "ssb")
present_score_cols <- key_score_cols[key_score_cols %in% names(questionnaire_data)]

if(length(present_score_cols) > 0) {
  questionnaire_scores_long <- questionnaire_data %>% 
    select(subject_id, all_of(present_score_cols)) %>%
    pivot_longer(cols = all_of(present_score_cols), names_to = "scale_name", values_to = "score") %>% 
    filter(!is.na(score))
  
  # Distribution of Key Questionnaire Scores
  score_dist_plots <- ggplot(questionnaire_scores_long, aes(x = score)) +
    geom_histogram(aes(y = after_stat(density)), binwidth = function(x) 2 * IQR(x, na.rm=TRUE) / (length(x)^(1/3)), 
                   fill = "skyblue", color = "black", alpha = 0.7) +
    geom_density(alpha = 0.2, fill = "lightblue") +
    facet_wrap(~ scale_name, scales = "free") +
    labs(title = "Distribution of Key Questionnaire Scores", x = "Score", y = "Density") +
    theme_minimal(base_size = 10) +
    theme(plot.title = element_text(face="bold", size=rel(1.2)), strip.text = element_text(face="bold"))
  
  print(score_dist_plots)
  ggsave(file.path(output_figs_dir, "questionnaire_score_distributions.png"), plot = score_dist_plots, width = 10, height = max(6, 2*ceiling(length(present_score_cols)/3)))
  
  # Boxplots of BIS Total and SSS Total Scores
  score_boxplots_filtered <- questionnaire_scores_long %>%
    filter(scale_name %in% c("bis_total", "ss_total")) %>%
    ggplot(aes(x = scale_name, y = score, fill = scale_name)) +
    geom_boxplot(alpha = 0.7, outlier.colour = "red") +
    labs(title = "Boxplots of BIS and SSS Total Scores", y = "Score", x=NULL) +
    theme_minimal(base_size = 10) +
    theme(plot.title = element_text(face="bold", size=rel(1.2)), legend.position="none")
  
  print(score_boxplots_filtered)
  ggsave(file.path(output_figs_dir, "questionnaire_score_boxplots_filtered.png"), plot = score_boxplots_filtered, width = 6, height = 5)

} else {
  cat("\nNo key questionnaire score columns found.\n")
}
```

## 6.2 Score Relationships
```{r questionnaire_score_relationships}
# Relationship between BIS Total and SSS Total Scores plot 
if ("bis_total" %in% names(questionnaire_data) && "ss_total" %in% names(questionnaire_data)) {
  bis_ss_scatter <- ggplot(questionnaire_data, aes(x = bis_total, y = ss_total)) +
    geom_point(alpha = 0.6, color = "purple") +
    geom_smooth(method = "lm", color = "black", se = FALSE, linetype="dashed") +
    labs(title = "Relationship between BIS Total and SSS Total Scores",
         x = "BIS Total Score",
         y = "SSS Total Score") +
    theme_minimal(base_size = 12)+
    theme(plot.title = element_text(face="bold"))
  print(bis_ss_scatter)
  ggsave(file.path(output_figs_dir, "bis_total_vs_ss_total_scatter.png"), plot = bis_ss_scatter, width = 7, height = 6)
} else {
  cat("\nbis_total or ss_total not found, skipping their specific scatter plot.\n")
}
```

# 7. Concluding Remarks

This EDA has provided a comprehensive overview of the task and questionnaire data. Key findings include:
- Data loading and preparation procedures are established.
- Distributions of key variables (RT, reward rates, questionnaire scores) have been examined.
- Behavioral patterns related to choice, learning, and feedback conditions have been visualized.

The next steps will involve formal hypothesis testing and model fitting as outlined in the analysis plan, using the insights gained from this EDA to inform those processes.

---
End of EDA R Markdown Document
---
